### 2018-10-29 00_abstract.tex
Initial ShareLaTeX Import

Rearranging objects on a planar surface arises in a variety of
robotic applications, such as product packaging.  Using two arms can improve
efficiency but introduces new computational challenges. This paper
studies the structure of dual-arm rearrangement for synchronous,
monotone tabletop setups and develops an optimal mixed integer model. It then
describes an efficient and scalable algorithm, which first minimizes
the cost of object transfers and then of moves between objects.
This is motivated by the fact that, asymptotically, object transfers
dominate the cost of solutions. Moreover, a lazy strategy minimizes
the number of motion planning calls and results in significant
speedups.  Theoretical arguments support the benefits of using two
arms and indicate that synchronous execution, in which the two arms perform together either transfers or moves, introduces only a small
overhead.  Experiments support these points and show that the
scalable method can quickly compute solutions close to the optimal for
the considered setup.

### 2018-10-29 01_introduction.tex
Initial ShareLaTeX Import

%Advances in robotics have been pushing the boundaries of the
%application of robots to automation. There has been a lot of interest
%in robotic picking in this context\cite{correll2016analysis} and
%significant recent efforts have been made for facing the challenges of
%manipulation and grasping.

Automation tasks in industrial and service robotics, such as product packing or sorting, often require sets of objects to be arranged in
specific poses on a planar surface. Efficient and high-quality
single-arm solutions have been proposed for such
setups \cite{193}. The proliferation of robot arms, however, including dual-arm setups, implies that industrial settings can utilize multiple robots in the same workspace (Fig \ref{fig:two_arms}). This work explores a) the benefits of coordinated dual-arm rearrangement versus single-arm, b) the combinatorial challenges involved and c) computationally efficient, high-quality and scalable methods.

%While the benefits seem obvious, even for two arms, the challenge
%lies in examining the combinatorial sub-structure of this integrated
%task and motion planning problem.

%The current work focuses on rearrangement problems involving two
%arms.  Compared to the sort of solutions that yield high quality
%single arm solutions to these problems, it will be demonstrated that
%significant solution quality improvements can be made, which
%motivates the need to find effective algorithms that can solve the
%dual-arm rearrangement problem.  We seek to bound the cost of $k$-arm
%manipulation.  Note that $c_t$ may be used to capture distance
%(energy) cost or time cost.

%Due to lying at the confluence of various challenging problem
%domains, namely multi-robot motion planning, object rearrangement
%task planning, and combinatorial search, the problem at hand demands
%closer inspection through these lenses. It is desirable to obtain
%some guarantees about the benefits of using more than one arm, before
%endeavoring to study the problem.

A motivating point is that the coordinated use of multiple arms can
result in significant improvements in efficiency. This arises from the following argument.

\vspace{-.1in}
\begin{lemma}\label{l:k-arm-lower-bound}
There are classes of tabletop rearrangement problems, where a $k$-arm
($k \ge 2$) solution can be arbitrarily better than the optimal
single-arm one.
\vspace{-.3in}
\end{lemma}

For instance, assume two arms that have full (overhand) access to a 
unit square planar tabletop. There are $n$ objects on the table, 
divided into two groups of $\frac{n}{2}$ each. Objects in each group 
are $\varepsilon$-close to each other and to their goals. Let the 
distance between the two groups be on the order of $1$, i.e., the two 
groups are at opposite ends of the table. The initial position of each 
end-effector is $\varepsilon$-close to a group of objects. Let the cost 
of each pick and drop action be $c_{pd}$, while moving the 
end-effector costs $c_t$ per unit distance. Then, the $2$-arm 
cost is no more than $2nc_{pd} + 2n\varepsilon c_t $.  A single arm 
solution costs at least $2nc_{pd} + (2n-1)\varepsilon c_t + 
c_t$. If $c_{pd}$ and $\varepsilon$ are sufficiently small, the $2$-arm 
cost can be arbitrarily better than the single-arm one. The argument 
also extends to $k$-arms relative to $(k-1)$-arms.

In most practical setups, the expectation is that a $2$-arm solution
will be close to half the cost (e.g., time-wise) of the single-arm 
case, which is a desirable improvement. While there 
is coordination overhead, the best $2$-arm solution cannot do worse; simply 
let one of the arms carry out the best single arm solution while the 
other remains outside the workspace. More generally:

\vspace{-.1in}
\begin{lemma}\label{l:2-arm-no-worse}
For any rearrangement problem, the best $k$-arm ($k \ge 2$) solution
cannot be worse than an optimal single arm solution.
\vspace{-.1in}
\end{lemma}

The above points motivate the development of scalable algorithmic
tools for such dual-arm rearrangement instances. This work considers
certain relaxations to achieve this objective. In particular,
monotone tabletop instances are considered, where the start and goal
object poses do not overlap.  Furthermore, the focus is on
synchronized execution of pick-and-place actions by the two arms. i.e., where the two arms simultaneously transfer (different) objects, or simultaneously move towards picking the next objects.
Theoretical arguments and experimental evaluation indicate that the
synchronization assumption does not significantly degrade solution
quality.

\begin{figure}[t]\vspace{-0.15in}
	\centering
	\includegraphics[width=3in]{figures/two_arms}\vspace{-0.1in}
	\caption{Example of dual-arm setups that can utilize
	algorithms proposed in this work.}
	\label{fig:two_arms}\vspace{-0.25in}
\end{figure}

The first contribution is the study of the combinatorial structure of
synchronous, monotone dual-arm rearrangement. Then, a mixed integer linear programming (\milp) model is
proposed that achieves optimal coordinated solutions in this domain.
An efficient algorithm {\tt Tour\_Over\_Matching} (\algo) is proposed
that significantly improves in scalability. \algo\ first optimizes the
cost of object transfers and assigns objects to the two arms by
solving an optimal matching problem. It minimizes the cost of
moves from an object's goal to another object's start pose per
arm as a secondary objective by employing a {\tt TSP} solution. Most
of the computation time is spent on the many calls to a
lower-level motion planner that coordinates the two arms. A lazy
evaluation strategy is proposed, where candidate solution sequences
are developed first and then motion plans are evaluated for them. The
strategy results in significant computational improvement and
minimizes the calls to the coordination motion planner.  An analysis
is also performed on the expected improvement in solution quality
versus the single arm case, as well as the expected cost overhead from a
synchronous solution.

Finally, experiments for i) a simple planar picker setting, and ii) a
model of two 7-DOF Kuka arms, demonstrate a nearly two-fold
improvement against the single arm case for the proposed approach in practice. The
solutions are close to optimal for the dual-arm case and the algorithm
exhibits good scalability. The computational costs of both the optimal
and the proposed method are significantly improved from the lazy
evaluation strategy. 
% When the synchronous solutions are smoothed to
% asynchronous ones, there is not significance difference in overall
% path quality. \kiril{This statement is unclear. What is the benefit from performing this step?}

### 2018-10-29 02_background.tex
Initial ShareLaTeX Import

%Related efforts:
%
%\begin{itemize}
%\item multi-robot planning and coordination
%\item manipulation task planning in general
%\item rearrangement 
%\item combinatorial literature
%\end{itemize}
The current work dealing with dual-arm object rearrangement touches upon the challenging intersection of a variety of rich bodies of prior work. It is closely related to multi-robot planning and coordination. The challenge with multi-body planning is the high dimensionality of the configuration space. %Early work has suggested to slightly reduce the~\cite{aronov1999motion} tried dimensionality reduction strategies. 
Optimal strategies were developed for simpler instances of the problem \cite{solovey2015motion}, although in general the problem is known to be computationally hard~\cite{solovey2016hardness}. Decentralized approaches~\cite{van2005prioritized} also used velocity tuning~\cite{leroy1999multiple} to deal with these difficult instances. General multi-robot planning tries to plan for multiple high-dimensional platforms \cite{wagner2012probabilistic,Gharbi:2009fu} using sampling-based techniques. 
Recent advances provide scalable~\cite{SoloveySH16:ijrr} and asymptotically optimal~\cite{Dobson:2017aa} sampling based frameworks. 
%Assembly planning \cite{halperin2000general,sundaram2001disassembly} is another related problem dealing with multi-body planning.

%The discrete version of the multi-body problem, also known as the "pebble motion problem" has seen a lot of work \cite{kornhauser1984coordinating,auletta1999linear,goraly2010multi}. For such discrete problems on a pebble graph, feasibility times are linear and solution times are polynomial. Optimality is still challenging even in these setups. Heuristics have been used to provide high quality solutions \cite{wagner2012probabilistic,sharon2015conflict}.

In some cases, by restricting the input of the problem to a certain type, it is possible to cast known hard instances of a problem as related algorithmic problems which have efficient solvers. For instance, unlabeled multi-robot motion planning can be reduced to pebble motion on graphs~\cite{abhs-unlabeled14}; pebble motion can be reduced to network flow~\cite{yu2016optimal}; and single-arm object rearrangement can be cast as a traveling salesman problem~\cite{193}. These provide the inspiration to closely inspect the structure of the problem to derive efficient solutions.

%\subsection{Combinatorial Literature}
%Our problem can be formulated in a variety of related classes of problems in combinatorial literature. Most of the approaches assume that all the edge weights are known, ie. the motion planning for all the edges has to be performed before any operation on the graph that uses the weights.

%\textbf{The Traveling Salesman Problem}:
In this work we leverage a connection between dual-arm rearrangement and two combinatorial problems: (1) optimal matching~\cite{edmonds1965maximum} and (2) TSP. On the surface the problem seems closely related to multi-agent TSP.
%This can itself be tweaked with assumptions on same or different start and goal positions, symmetric or asymmetric metrics, directed or undirected graphs or posing the problem as an optimization
A seminal paper~\cite{frederickson1976approximation} provides the formulation for k-TSP, with solutions that split a single tour.
Prior work \cite{rathinam2006matroid} has formulated the problem of multi-start to multi-goal k-TSP as an optimization task. Some work~\cite{friggstad2013multiple} deals with asymmetric edge weights which are more relevant to the problems of our interest.

%\textbf{Errand Scheduling}:
%If the object transfer is seen as an errand \cite{slavik1997errand} then a graph constructed with nodes being object-arm assignments and edges implying the order of coordinated execution. 
%There has been prior work \cite{garg2000polylogarithmic} that operates over the assignment graph(where pairwise assignments are nodes), an object's group consists of sets of nodes that include an object

The multi-arm rearrangement can also be posed as an instance of multi vehicle pickup and delivery (PDP)~\cite{parragh2008survey}. 
%Most of the work has been motivated by ride-sharing applications and timed task scheduling, so there are a lot of variations that deal with time windows but this line of research provides some ILP formulations for the problem.
Prior work~\cite{coltin2014multi} has applied the PDP problem to robots, taking into account time windows and robot-robot transfers.
Some seminal work~\cite{lenstra1981complexity,savelsbergh1995general} has also explored its complexity, and concedes to the hardness of the problem, while others have studied cost bounds~\cite{TrePavFra13}. ILP formulations~\cite{savelsbergh1995general} have also been proposed. 
%The existing work that delves into the combinatorial challenges of the problem, do not account for the costs incurred due to coordination of the agents during task execution. 
%Pickup and Delivery problems under track contention \cite{caricato2003parallel}, makes an attempt to reason about the coordination of the robots over solutions obtained with Tabu Search.
Typically this line of work ignores coordination costs, though some methods~\cite{caricato2003parallel} reason about it once candidate solutions are obtained.

% There has been a a lot of work in motion planning for manipulators and movable objects. 
Navigation among movable objects deals with the combinatorial challenges of multiple objects~\cite{wilfong1991motion,van2009path} and has been shown to be a hard problem, and extended to manipulation applications~\cite{stilman2007manipulation}. Despite a lot of interesting work on challenges of manipulation and grasp planning, the current work shall make assumptions that avoid complexities arising from them. Manipulators opened the applications of rearrangement planning~\cite{ben1998practical,ota2004rearrangement}, including instances where objects can be grasped only once or monotone~\cite{stilman2007manipulation}, as well as non-monotone instances~\cite{havur2014geometric,srivastava2014combined}. Efficient solutions to assembly planning problems~\cite{Wilson:1994fk,Halperin:2000uq} typically assumes monotonicity, as without it the problem becomes much more difficult. Recent work has dealt with the hard instances of task planning~\cite{berenson2011task,cohen2014single} and rearrangement planning~\cite{krontiris2015dealing,krontiris2016efficiently,193}. Sampling-based task planning has made a recent push towards guarantees of optimality~\cite{vega2016asymptotically,schmitt2017optimal}. These are broader approaches that are invariant to the combinatorial structure of the application domain. The current work draws inspiration from these varied lines of research.

\commentadd{
General task planning methods are unaware of the underlying structure studied in this work. Single-arm rearrangement solutions will also not effective in this setting. The current work tries to bridge this gap and provide insights regarding the structure of dual-arm rearrangement. Under assumptions that enable this study, an efficient solution emerges for this problem.
}

### 2018-10-29 03_problem.tex
Initial ShareLaTeX Import

Consider a planar surface and a set of $n$ rigid objects $ \objectset=\{ \object_1, \object_2 \cdots \object_n\}$  that can rest on the surface in stable poses $p_i \in \Pspace_i \subset SE(3)$. The arrangement space $ \Aspace = \Pspace_1 \times \Pspace_2 \ldots \times \Pspace_n $ is the Cartesian product of all $\Pspace_i$, where $ \arrangement = (\pose_1, \ldots, \pose_n) \in \Aspace $. In valid arrangements $ \Afree \subset \Aspace$, the objects are pairwise disjoint.

\begin{wrapfigure}{r}{2.4in}
    \vspace{-.3in}
	\centering
	\includegraphics[width=1.115in,trim={10cm 3cm 8cm 12cm},clip]{figures/rearrangement_start}
	\includegraphics[width=1.115in,trim={10cm 3cm 8cm 12cm},clip]{figures/rearrangement_end}
    \vspace{-.15in}
	\caption{An example of object rearrangement involving two robotic arms. Initial (left) and final (right) object configuration.}
	\label{fig:rearrangement}
    \vspace{-.35in}
\end{wrapfigure}
Two robot arms $\arm^1$ and $\arm^2$ can 
% pick, raise above the surface and place the objects. 
pick and place the objects from and to the surface.
% \kiril{The last statement is unclear, particularly the purpose of the word "raise". Can it be rewritten into "...can pick and place objects from and to the surface."?}  
% THE OLD SENTENCE$\cfree^k$ is the set of collision-free configurations for arm $ \arm^k $, where $ q^k \in \cfree^k %\subset \reals^d $ (while ignoring possible collisions with  objects or the other arm).
$\cfree^k$ is the set of collision-free configurations for arm $\arm^k$ (while ignoring possible collisions with  objects or the other arm), and is assumed here to be a subset of $\reals^d $.
A path for $\arm^k$ is denoted as $ \pi^k : [0,1] \rightarrow \cfree^k$ and includes picking and placing actions.  Let $ \cfree^i(\pi^j) $ represent the collision free $\mathbb{C}$-space for $\arm^i$, given that $\arm^j$ moves along $\pi^j $. This is a function of the paths' parametrization. The space of dual-arm paths $\mathcal{D}$ denotes pairs of paths for the two arms: $D = (\pi^1,\pi^2) \in \mathcal{D}$. Then, $\arrangement(\ainit, D)$ is the resulting arrangement when the objects are at $\ainit$ and moved according to $D$.   Let $ \cost(D) : \mathcal{D} \rightarrow \reals $ be a cost function over dual-arm paths.

\vspace{-.1in}
{\definition [Optimal Dual-arm Rearrangement] Given arms $\arm^1$, $\arm^2$ and objects $\objectset$ to be moved from initial arrangement $ \ainit \in \Afree$ to target arrangement $ \atarget \in \Afree $, the optimal dual-arm rearrangement problem asks for a dual-arm path $D^* \in \mathcal{D}$, which satisfies the following constraint:

\vspace{-.15in} 
\begin{equation}
D^* =  (\pi^{*1}, \pi^{*2}) \ |\ \arrangement(\ainit, D^*) = \atarget \textrm{ and } \pi^{*i} \in \cfree^i(\pi^{*j}) \vspace{-.05in}
\label{eq:dualarm_constraint}
\end{equation}
\noindent and optimizes a cost function: $D^* = \underset{ \forall D \in \mathcal{D}}{ \mathtt{argmin} } \ \cost(D).$}

A set of assumptions are introduced to deal with the problem's combinatorics. The reachable task-space $\taskspace^k \subset SE(3)$ of arm $\arm^k$ is the set of $SE(3)$ poses that objects attached to the arm's end effector can acquire.

% \vspace{-.15in}
\commentdel{
{\textbf{Assumption} [Reachability] All objects are reachable by both arms at $\ainit$ and $\atarget$: $\forall\ \pose_i \in \ainit \textrm{ and } \forall\ \pose_j \in \atarget \textrm{ and } \forall\ k \in [1,2]: \pose_i, \pose_j \subset \taskspace^k $.}
}

Let the ordered set of objects moved during the arm path $ \pi^i $ be denoted as $ \moveset(\pi^k) $. In general, an object can appear many times in $ \moveset(\pi^k) $. The current work, however, focuses on monotone instances, where each object is moved once.

\vspace{-.15in}
{\assumption [Monotonicity] There are dual-arm paths $D = (\pi^1,\pi^2)$ that satisfy Eq. \ref{eq:dualarm_constraint}, where each object $ \object_i \in \objectset $ appears once in $\moveset(\pi^1)$ or $ \moveset(\pi^2)$.}

\commentadd{
For the problem to be solvable, all objects are reachable by at least one arm at both $\ainit$ and $\atarget$: $\forall\ \pose_i \in \ainit \textrm{ and } \forall\ \pose_j \in \atarget \textrm{ and } \exists\ k \in [1,2]: \pose_i, \pose_j \subset \taskspace^k $.
}
The focus will be on simultaneous execution of transfer and move paths.

\noindent\textbf{Transfers:} Dual-arm paths $T(\pi^1_i,\pi^2_i) \in \mathcal{D}$, where $ \moveset(\pi^k_i) =  \object^k_i $ and each $m^k$:
\begin{myitem}
\item[$-$]\ \ starts the path in contact with an object $\object^k_i$ at its initial pose in $\ainit$,
\item[$-$]\ \ and completes it in contact with object $ \object^k_i $ at its final pose in $\atarget$. 
\end{myitem}

\noindent\textbf{Moves or Transits:} Paths $M(\pi^1_{i\rightarrow i^{\prime}},\pi^2_{i\rightarrow i^{\prime}}) \in \mathcal{D}$, $ \moveset(\pi^1_{i\rightarrow i^{\prime}}) = \emptyset $, and each $\arm^k$:
\begin{myitem}
\item[$-$]\ \  starts in contact with object $\object^k_i$ at its final pose in $\atarget$,
\item[$-$]\ \  and completes it in contact with object $\object^k_{i^{\prime}}$ at its initial pose in $\ainit$.
\end{myitem}

\vspace{-.1in}
{\assumption [Synchronicity] Consider dual-arm paths, which can be decomposed into a sequence of simultaneous transfers and moves for both arms:
\vspace{-.1in}
\begin{equation}
D=\left(T(\pi^1_1,\pi^2_1),M(\pi^1_{1\rightarrow 2},\pi^2_{1\rightarrow 2}), \ldots , M(\pi^1_{\ell-1\rightarrow \ell},\pi^2_{\ell-1\rightarrow \ell}), T(\pi^1_\ell,\pi^2_\ell)\right).\vspace{-.05in}
\label{eq:synchronicity}
\end{equation}}
\noindent For simplicity, Eq.~\ref{eq:synchronicity} does not include an initial move from $q^k_{\rm safe} \in \cfree^k$ and a final move back to $q^k_{\rm safe}$. An odd number of objects can also be easily handled. Then, the sequence of object pairs moved during a dual-arm path as in Eq. \ref{eq:synchronicity} is: \vspace{-.1in} 
% $$ \scoma(D) = \left(  \coma_i = (\object_i^1,\object_i^2) \ |\ i,j\in [1,\cdots,\ell], \bigcup_i (\object_i^1 \cup \object_i^2) = \objectset, \object_i^1 \cap \object_j^1 = \object_i^2 \cap \object_j^2 = \emptyset \right). \vspace{-.15in}$$
$$ \scoma(D) = \left(  \coma_i = (\object_i^1,\object_i^2) \ |\ i,j\in [1\cdots \ell], \bigcup_i (\object_i^1 \cup \object_i^2) = \objectset, \forall k,k'\in[1,2], \object_i^k \neq \object_j^{k'} \right). \vspace{-.1in}$$

\noindent Given the pairs of objects $\coma_i$, it is possible to express a transfer as $T(\coma_i)$ and a move as $M(\coma_{i\rightarrow j})$.  Then, $D(\scoma)$ is the synchronous, monotone dual-arm path due to $\scoma = (\coma_1, \ldots, \coma_{\ell})$, i.e., $D(\scoma) = (T(\coma_1),M(\coma_{1\rightarrow 2}),\ldots,M(\coma_{\ell-1\rightarrow \ell}),T(\coma_\ell)).$

\vspace{-.1in}
{\assumption [Object Non-Interactivity] There are collision-free transfers $T(\coma_i)$ and moves $M(\coma_{i\rightarrow i^{\prime}})$ regardless of the object poses in $\ainit$ and $\atarget$.}
\commentadd{This entails that there is no interaction between the $n$ resting objects and the arms during transits. Similarly, there are no interactions between the arm-object system and the $n-2$ resting objects during the transfers. Collisions involving the arms, static obstacles and picked objects are always considered.}
\commentdel{
This assumption is valid in tabletop setups where the arms can raise the picked objects above the resting surface. 
% Furthermore, this assumption implies that transfers and moves involving object poses in $\ainit, \atarget$ are always feasible and the challenge is deciding the appropriate sequence of object-to-arm assignments.
This assumption lets the study focus on the challenge of deciding the appropriate sequence of object-to-arm assignments.
}

The metric this work focuses on relates to makespan and minimizes the sum of the longest distances traveled by the arms in each synchronized operation. Let $ \| \pi^k \| $ denote the Euclidean arc length in $\cfree^k  \subset \reals^d$ of path $ \pi^k $. Then, for transfers $\cost( T(\pi^1_i,\pi^2_i) ) = \max\{ \|\pi^1_i\|, \|\pi^2_i\| \}$. Similarly, $\cost( M(\pi^1_{i\rightarrow i^{\prime}},\pi^2_{i\rightarrow i^{\prime}}) ) = \max\{ \|\pi^1_{i\rightarrow i'}\|, \|\pi^2_{i\rightarrow i'}\| \}$. Then, over the entire dual-arm path $ \D $ define:
\vspace{-.15in}
\begin{equation}
\cost(\D) 
% = \cost_{ T} + \cost_{ M} 
= \sum_{i=1}^{\ell}   \cost(T(\coma_i))   + \sum_{i=1}^{\ell-1}   \cost(M(\coma_{i\rightarrow i+1})). 
\vspace{-.1in}
\label{eq:cost_function}
\end{equation}
Note that the \textit{transfer} costs do not depend on the order with which the objects are moved but only on the assignment of objects to arms. The \textit{transit} costs arise out of the specific ordering in $ \scoma(D)$. 
Then, for the setup of Definition 1 and under Assumptions 1-3, the problem is to compute the optimal sequence of object pairs $\scoma^*$ so that $D(\scoma^*)$ satisfies Eq.~\ref{eq:dualarm_constraint} and minimizes the cost of Eq.~\ref{eq:cost_function}.

\commentdel{Assumptions 2 and 3 will be partly relaxed in Section \ref{sec:integration}. Assumption 1 is also effectively relaxed to cases where at least one arm can transfer every object.}
% , given a smoothing process for achieving an asynchronous solution and a lazy motion planning process for computing transfers and moves that can be informed of object poses.

\commentadd{
\noindent \textbf{Note on Assumptions:} This work restricts the study to a class of monotone problems that relate to a range of industrial packing and stowing applications. The monotonicity assumption is often used in manageable variants of well-studied problems~\cite{Wilson:1994fk,Halperin:2000uq}. A monotone solution also implies that every object's start and target is reachable by at least one arm. To deal with cases where the number of reachable objects is unbalanced between the two arms, a {\tt NO\_ACT} task assignment is introduced and considered in Section 6.

The synchronicity assumption allows to study the combinatorial challenges of the problem, which do not relate to the choice of time synchronization of different picks and placements. Section \ref{sec:integration} describes the use of $\drrtstar$\cite{Dobson:2017aa} as the underlying motion planner that can discover solutions that can synchronize arm motions for simultaneous picks, and simultaneous placements. The synchronicity assumption is relaxed through smoothing (Section \ref{sec:integration}).

The non-interactivity assumption comes up naturally in planar tabletop scenarios with top-down picks or delta robots. Such scenarios are popular in industrial settings. Once the object is raised from the resting surface, transporting it to its target does not introduce interactions with the other resting objects. This assumption is also relaxed in Section \ref{sec:integration}, with a lazy variant of the proposed method. Once a complete candidate solution is obtained, collision checking can be done with everything in the scene.

Overall, under the assumptions, the current work identifies a problem structure, which allows arguments pertaining to the search space, completeness, and optimality. Nevertheless, the smoothed, lazy variant of the proposed method will still return effective solutions in practice, even if these assumptions do not hold.

% The validation of the final candidate solution enforces that the algorithm keeps trying till a collision-free solution is found. The assumptions enable the current work to study in detail the problem, which is otherwise mostly intractable.

}

### 2018-10-29 04_baseline.tex
Initial ShareLaTeX Import

This section highlights two optimal strategies to discover $\D(\scoma^*)$: a) exhaustive search, which reveals the search space of all possible sequences of object pairs $ \scoma $ and b) an MILP model. Both alternatives, however, suffer from scalability issues as for each possible assignment, it is necessary to solve a coordinated motion planning problem for the arms. This motivates minimizing the number of assignments $\coma$ considered, and the number of motion planning queries it requires for discovering $\D(\scoma^*)$, while still aiming for high quality solutions.

\noindent\textbf{Exhaustive Search}: The exhaustive search approach shown in Fig. \ref{fig:backtracking} is a brute force expansion of all possible sequences of object pairs $ \scoma $. Nodes correspond to transfers $T(\coma_i)$ and edges are moves $M(\coma_{i\rightarrow i{^\prime}})$. The approach evaluates the cost for all possible branches to return the best sequence $\scoma$. The total number of nodes is in the order of $O(n!)$, expressed over the levels $L$ of the search tree as: 
% \kiril{It may be beneficial to explain the formula below, or perhaps move it to the appendix to save space and avoid explaining it here.}:

\vspace{-0.25in}
\begin{equation*}
{\permu[n]{2}} + {\permu[n]{2}}\times{\permu[n-2]{2}} + ... + {\permu[n]{2}}\times{\permu[n-2]{2}}\times{\permu[n-4]{2}}...\times{\permu[2]{2}} =\sum_{L=1}^{n/2} {\ \prod_{k=0}^{2L-1}{(n-k)}},
\vspace{-0.15in}
\end{equation*}
where $\permu[n]{k}$ denotes the number of $k$-permutations of $n$.

\begin{wrapfigure}{r}{2.4in}
    \vspace{-.1in}
	\centering
	\includegraphics[width=2.3in]{figures/dual_backtracking.PNG}
    \vspace{-.15in}
	\caption{Search tree for 4 objects. In node $XY$, $m^1$ transfers object $X$, and $m^2$ transfers $Y$. An edge is a transit to the next node. }
	\label{fig:backtracking}
    \vspace{-.3in}
\end{wrapfigure}
Motion plans can be reused, however, and repeated occurrences of $T(\coma_i)$ and $M(\coma_{i\rightarrow i^{\prime}})$ should be counted only once for a total of: 
\begin{myitem}
\item[$-$] $  {\permu[n]{2}} $ \textit{transfers} of objects, and 
\item[$-$] $ {{\permu[n]{2}}\times\permu[n-2]{2}} $ \textit{transits} between all possible valid ordered pairs of $ \coma $.
\end{myitem}
Additional motion plans are needed for the initial move from $q_{\rm safe}^k$ and the return to it at the end of the process, introducing $ 2\times\permu[n]{2} $ transits:

\vspace{-0.35in}
\begin{equation}
\textrm{\# of Transfers} + \textrm{\# of Moves} =  {\permu[n]{2}} +   \Big{(}({{\permu[n]{2}}\times\permu[n-2]{2}}) + (2\times{\permu[n]{2}})\Big{)}
\label{eq:mpcount}
\vspace{-0.2in}
\end{equation}

This returns optimal synchronized solution but performs an exhaustive search and requires exponentially many calls to a motion planner.

\noindent\textbf{MILP Formulation}:
Mixed Integer Linear Programming (\milp) formulations can utilize highly optimized solvers \cite{gurobi}. Prior work has applied these techniques for solving m-TSP \cite{rathinam2006matroid,friggstad2013multiple} and pickup-and-delivery problems \cite{coltin2014multi,savelsbergh1995general}, but viewed these problems in a decoupled manner. This work outlines an \milp formulation for the synchronized dual-arm rearrangement problem that reasons about coordination costs arising from arm interactions in a shared workspace.

\textit{Graph Representation:}
The problem can be represented as a directed graph where each vertex $v = \coma_v = (\object_v^1, \object_v^2)$ corresponds to a transfer $ T(\coma_u) $ and edges $e(u,v)$ are valid moves $M(\coma_{u\rightarrow v})$. A valid edge $e(u,v)$ is one where an object does not appear more than once in the transfers of nodes $u$ and $v$.  The cost of a directed edge $e(u,v)$ encodes both the cost of the transfer  $ T(\coma_v) $ and the cost of the move $M(\coma_{u\rightarrow v})$. There is also a vertex $ \startq $, which connects moves from and to the safe arm configurations $q^k_{\rm safe}$.  The directed graph $ \hat{G} (\hat{V},\hat{E}) $ is defined:

\vspace{-.3in}
\begin{align*}
\hspace{0.5in} \hat{V} = \{ v = \coma_v = (\object_v^1,\object_v^2)\ | \  \forall\ \object_v^1,\object_v^2 \in \objectset, \object_v^1 \neq \object_v^2 \} \cup \{S\}\\
\hat{E} = \{  e(u,v)\ | \ \forall\ u,v\in \hat{V} \textrm{ so that } u\neq v,\ \object_v^k \neq \object_u^{\ell}\ \forall\ k, \ell \in [1,2] \}\\
\cup\ \{e(\startq,v)\ \forall\ v\in\hat{V}\setminus \startq\} \cup \{e(v,\startq)\ \forall\ v\in\hat{V}\setminus \startq\}\\
cost_{e(u,v)} = \cost(u) + \cost(u,v) =\cost(T(\coma_u)) + \cost(M(\coma_{u\rightarrow v}))
\end{align*}

\vspace{-.2in}
Let $\cost(\startq) = 0$. The total number of motion planning queries needed to be answered to define the edge costs is expressed in Eq.~\ref{eq:mpcount}. The formulation proposed in this section tries to ensure the discovery of $ \scoma^* $ on $ \hat{G} $ as a tour that starts and ends at $ \startq $, while traversing each vertex corresponding to $ \scoma^* $. To provide the {\tt MILP} formulation, define $ \delta_{\rm in}(v) $ as the in-edge set $v$, and  $ \delta_{\rm out}(v) $ as the out-edge set. Then, $ \gamma(\object) $ is the object coverage set $ \gamma(\object) = \{ e(u,v) \ |\ e\in\hat{E}, \object\in  \coma_u  \} $, i.e., all the edges that transfer $ \object $.

\textit{Model:} Set the optimization objective as: $\ \ \min \sum_{e \in \hat{E}} cost_e x_e\  $\hspace{.81in} [A]\\ 
Eq. [B] below defines indicator variables. Eqs. [C-E] ensure edge-flow conserved tours. Eqs. [F-G] force $\startq$ to be part of the tour. Eq. [H] transfers every object only once. Eq. [I] lazily enforces the tour to be of length $ \frac{n}{2} + 1 $. While the number of motion-planning queries to be solved is the same as in exhaustive search, efficient {\milp} solvers \cite{gurobi} provide a more scalable search process.

\vspace{-.25in}
\noindent\begin{minipage}{.5\textwidth}
\begin{align*}
x_e \in \{ 0,1 \}& \ \ \forall e \in \hat{E} \tag*{[B]}\\
\sum_{e\in\delta_{\rm in}(v)} x_e \leq 1& \ \ \forall v\in \hat{V} \tag*{[C]}\\
\sum_{e\in\delta_{\rm out}(v)} x_e \leq 1& \ \ \forall v\in \hat{V} \tag*{[D]}\\
\sum_{e\in\delta_{\rm in}(v)}x_e = \sum_{e\in\delta_{\rm out}(v)}x_e& \ \ \forall v\in \hat{V} \tag*{[E]}\\
\end{align*}
\end{minipage}
\noindent\begin{minipage}{.5\textwidth}
\begin{align*}
\sum_{e\in\delta_{\rm in}(\startq)} x_e = 1& \tag*{[F]}\\
\sum_{e\in\delta_{\rm out}(\startq)} x_e = 1& \tag*{[G]}\\
\sum_{e\in\gamma(\object)} x_e = 1& \ \  \forall \object\in\objectset \tag*{[H]}\\
\sum_{e(u,v)\in \mathfrak{T}} x_e < |\mathfrak{T}| & \ \  \forall \mathfrak{T} \subset \hat{V}, |\mathfrak{T}| \leq \frac{n}{2} \tag*{[I]}
\label{model:milp}
\end{align*}
\end{minipage}

### 2018-10-29 05_approximation.tex
Initial ShareLaTeX Import

The optimal baseline methods described above highlight the problem's complexity. Both methods suffer from the large number of motion-planning queries they have to perform to compute the cost measures on the corresponding search structures. For this purpose it needs to be seen whether it is possible to decompose the problem into solvable sub-problems. 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\noindent\textbf{Importance of Transfers}: In order to draw some insight, consider again the tabletop setup with a general cost measure of $c_t$ per unit distance.
Lemma~\ref{l:k-arm-lower-bound} suggests that under certain conditions, there 
may not be a meaningful bound on the performance ratio between a $k$-arm 
solution and a single-arm solution. This motivates the examination of another
often used setting---randomly chosen non-overlapping 
start and goal locations for $n$ objects (within a unit square). In order to derive a 
meaningful bound on the benefit of using a $2$-arm solution 
to a single-arm solution, we first derive a conservative cost of a single-arm solution. 
A single-arm optimal cost has three main parts: 1) the portion of the transfer cost involving the pickup and 
drop-off of the $n$ objects with a cost of $C_{pd} = nc_{pd}$, 2) the remaining transfer cost from 
start to goal for all objects $C_{sg}$, and 3) the transit cost 
going from the goals to starts $C_{gs}$. The single arm cost is  
\vspace{-0.1in}
\begin{equation}
\label{eq:single-cost-exp}
C_{\rm single} = nc_{pd} + C_{sg} + C_{gs}.
\vspace{-0.1in}
\end{equation}
To estimate Eq.~\ref{eq:single-cost-exp}, first note that the randomized setup 
will allow us to obtain the expected $C_{sg}$\cite{santalo2004integral} as
$\frac{2 + \sqrt{2} + 5\ln(1+\sqrt{2})}{15}nc_t \approx 0.52nc_t$.
Approximate $C_{gs}$ by simply computing an optimal assignment of the 
goals to the starts of the objects excluding the matching of the same start 
and goal. Denoting the distance cost of this matching as $C_{gs}^M$, clearly
$C_{gs} > C_{gs}^M$ because the paths produced by the matching may form 
multiple closed loops instead of the desired single loop that connects all 
starts and goals. However, the number of loops produced by the matching 
procedure is on the order of $\ln n$ and therefore, $C_{gs} < C_{gs}^M + 
c_t\ln n$, by~\cite{TrePavFra13}. By \cite{AjtKomTus84}, 
$C_{gs}^M = \Theta(\sqrt{n\ln n})$. Putting these together, we have,

{\centerline
{
$\Theta(c_t\sqrt{n\ln n}) = C_{gs}^M < C_{gs} < C_{gs}^M + c_t\ln n 
= \Theta(c_t\sqrt{n\ln n}) + c_t\ln n$
}
}

\noindent which implies that $C_{gs} \approx C_{gs}^M$ because for large $n$, $\ln n
\ll \sqrt{n\ln n}$. It is estimated in \cite{yu2015target} that $C_{gs}^M 
\approx 0.44\sqrt{n\ln n}c_t$ for large $n$. Therefore,

% \noindent Noting that the $0.44\sqrt{n\ln n}c_t$ term may also be ignored for large $n$,
% we have 
\vspace{-0.1in}
\begin{equation}\label{eq:single-cost-simple}
C_{\rm single} \approx nc_{pd} + (0.52n + 0.44\sqrt{n\ln n})c_t \approx (c_{pd} + 0.52c_t)n
% \vspace{-0.1in}
\end{equation}
noting that the $0.44\sqrt{n\ln n}c_t$ term may also be ignored for large $n$. The cost of dual arm solutions will be analyzed in Section \ref{sec:cost_bounds}.
{
\lemma For large $n$, the transfers dominate the cost of the solution.
\label{lem:transferdomination}
}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

We formulate a strategy to reflect this importance of transfers.
The proposed approach gives up on the optimality of the complete problem, instead focusing on a high-quality solution, which:
\begin{myitem}
\item[$-$] first optimizes transfers and selects an assignment of object pairs to arms, 
\item[$-$] and then considers move costs and optimizes the schedule of assignments.
\end{myitem} 
This ends up scaling better by effectively reducing the size of the search space and performing fewer motion planning queries. It does so by optimizing a related cost objective and taking advantage of efficient polynomial-time algorithms.

\begin{minipage}{0.48\textwidth}
  \begin{align}
  \label{eq:transfergraph}
  \begin{split}
  \graph(\nodes, \edges)\\
  \nodes = \{ \node=\object, \forall \object \in \objectset \}\\
  \edges = \{ \edge(u, v): \coma = (u,v), \forall u,v\in\nodes \}\\
  \cost(\edge(u,v)) = \cost(T(\coma=(u,v)))
  \end{split}
  \end{align}
\end{minipage}
\begin{minipage}{0.48\textwidth}
  \begin{align}
  \label{eq:transitgraph}
  \begin{split}
  \tspgraph(\tspnodes, \tspedges)\\
  \tspnodes = \{ \node=\coma, \forall \coma \in \scomaset^* \} \cup \{\coma_S\} \\
  \tspedges = \{ \edge(u, v): \coma_{u\rightarrow v}, \forall u,v\in\tspnodes \}\\
  \cost(\edge(u,v)) = \cost(M(\coma_{u\rightarrow v}))
  \end{split}
  \end{align}
\end{minipage}
\vspace{0.05in}

% \begin{align*}
% \ainit \rightarrow \atarget \\
% \scomaset^*\ \mathtt{on}\ \graph \\
% \scoma^+ : \tour \ \mathtt{on}\ \tspgraph
% \end{align*}

\begin{wrapfigure}{r}{2.5in}\vspace{-0.5in}
% \begin{figure}[H]
	\begin{center}
% 		\includegraphics[width=2.5in]{figures/mapp}
		\includegraphics[width=2.5in]{figures/mapp_labels}
	\end{center}\vspace{-0.2in}
	\caption{(left) A dual-arm rearrangement problem. (middle) The same problem as minimum weight edge matching on a fully connected directed graph of \textit{transfers}. (right) The ordering of the object-arm assignments from an optimal tour over a \textit{transit} graph.}\vspace{-0.2in}
	\label{fig:edge_matching}
% \end{figure}
\vspace{-0.1in}
\end{wrapfigure}

\noindent\textbf{Foundations:} Consider a complete weighted directed graph $\graph(\nodes,\edges)$ (Eq.~\ref{eq:transfergraph}), where $\node \in \nodes$ corresponds to a single object $ \object $. Each directed edge, $\edge=(\object_i,\object_j) \in \edges$ is an ordered pair of objects $ \object_i $ and $\object_j $, where the order determines the assignment of an object to an arm $ \arm^1 $ or $ \arm^2 $. The cost of an edge $ \cost(\edge) $ is the coordinated motion planning cost of performing the transfer corresponding to $ \coma = (\object_i,\object_j) $. For instance, as shown in Fig \ref{fig:edge_matching}(middle), $\edge(A,B)$ corresponds to $ \arm^1 $ transferring `A', while $ \arm^2 $ transfers `B', and the $\cost( \edge(A,B) ) = \cost(T(\coma=(A,B))$ is the cost of such a concurrent motion. Note that these costs refer to only the transfer costs i.e., starting from the arms picking up the objects $ A $ and $ B $ at the initial poses(as shown in Fig \ref{fig:edge_matching}(left)), and moving them to their target poses. It should also be noted that since the arms are different, in general, $\cost( \edge(A,B) )$ is not necessarily equal to $\cost( \edge(B,A) )$.

Following the observation made in Eq.~\ref{eq:cost_function}, the cost of the transfers can be reasoned about independent of their order. 
Define $\scomaset$ as the unordered set of $\coma\in\scoma$, then unordered transfer cost component corresponds to $\sum_{\coma\in\scomaset}\cost(T(\coma))$.
% We defined $ \scoma $ to be an ordered sequence of object-to-arm assignments. Let $ \scoma $ be a candidate solution to the synchronized dual-arm rearrangement problem. $ \scoma $ is an ordered sequence of $ \coma $, and $ \scomaset $ denote the unordered set of all $ \coma $ that comprise $ \scoma $. 
Since $ \graph $ is a complete graph where every edge corresponds to every possible valid $ \coma $, $ \scomaset $ must also be a part of $ \graph $. 
From the construction of the graph $ \graph $, $ \scomaset \subset \edges$. By definition, a candidate solution of a monotone dual-arm rearrangement problem must transfer every object exactly once. In terms of the graph, this means that in the subset of edges $ \scomaset $ every vertex appears in only one edge. We arrive at the following crucial observation.

{\lemma [Perfect Matching]
Every candidate solution to a monotone dual-arm rearrangement problem comprises of a set of unordered object-to-arm assignments $ \scomaset $ that is also a perfect matching solution on $ \graph $.
}

As per the decomposition of the costs in Eq. \ref{eq:cost_function}, it follows that the $ \cost(\scomaset) $ corresponds to the cost of the transfers in the solution. Given the reduction to edge-matching, the solution to the minimum-weight perfect edge matching problem on such a graph would correspond to a $ \scomaset $ that optimizes the cost of \textit{transfers} of all the objects.

{\lemma [Optimal Matching]
The set of object-to-arm assignments $ \scomaset^* $ that minimizes the cost of object transfers is a solution to the minimum-weight perfect matching problem on $ \graph $.
}
% $$
% \scomaset^* = \underset{ \scomaset \in \mathtt{EM(\graph)}  }{ \mathtt{argmin} } \ \cost(\scomaset)
% $$

Once such an optimal assignment $ \scomaset^* $ is obtained, the missing part of the complete solution is the set of transits between the object transfers and their ordering. Construct another directed graph $ \tspgraph $ (Eqs. \ref{eq:transitgraph}), where the vertices comprise of the $ \coma \in \scomaset^*$. An edge $ e(\coma_{u\rightarrow v}) $ between any two vertices corresponds to the coordinated \textit{transit} motion between them. For instance, as in Fig \ref{fig:edge_matching}(right) for an edge between $ \coma(A,B) $ and $ \coma(C,D) $, $ \arm^1 $ moves from the target pose of object `A' to the starting pose of object `C', and similarly $ \arm^2 $ moves from the target of `B' to the start of `D'. An additional vertex corresponding to the starting(and ending) configuration of the two arms ($ \startq $) is added to the graph. The graph is fully connected again to represent all possible transits or moves.

A complete candidate solution to the problem now requires the sequence of~$ \coma $. By definition of the edges, the complete solution begins at~$ \startq $ and also ends there. This is a complete tour over~$ \tspgraph $, that visits all the vertices i.e., an ordered sequence of vertices $\tour = ( {\startq}, \scoma_\tour, {\startq}  )$.

{
\lemma [Tour]
Any complete tour $ \tour $ over the graph $ \tspgraph $, corresponds to a sequence of object-to-arm assignments $ \scoma_\tour $ and is a candidate solution to the synchronous dual-arm rearrangement problem.
}

% In the problem setup it was assumed that $ \trajset(\scoma) $ contained the start and end transits to $ \startq $. Additionally, the entire trajectory contained both transfers and transits. Since we have considered all the transfers in $ \cost(\scomaset^*) $, what remains is the transits. Then 
% The cost of the tour $ \tour $ can be written as $\cost(\tour) = \sum_{e(u,v)\in\tour}\cost({M}( \coma_{u\rightarrow v} ))$.

Let $ \mathbb{P}^{\scomaset} $ represent the set of all possible ordering of the elements in $ \scomaset $. This means, any candidate tour corresponds to a $ \scoma_\tour\in\mathbb{P}^{\scomaset} $. An optimal tour on $ \tspgraph $ minimizes the transit costs over the all possible candidate solutions in  $ \mathbb{P}^{\scomaset^*} $.
\vspace{-0.1in}
\begin{equation}
\scoma^+ = \underset{ \scoma \in  \mathbb{P}^{\scomaset^*}   }{ \mathtt{argmin} } \ \sum_{e(u,v)\in\tour}\cost({M}( \coma_{u\rightarrow v} ))  )
\vspace{-0.05in}
\end{equation}

This differs from the true optimal $ \scoma^* $, since the second step of finding the optimal transit tour only operates over all possible solutions that include the optimally matched transfers obtained in the first step.
The insight here is that, even though $ \scoma^+ $ reports a solution to a hierarchical optimization objective, the algorithm operates over a much smaller search space, and operates over sub-problems which are more efficient to solve than the baselines.\\

\noindent\textbf{Algorithm}: This section describes the algorithm {\tt {Tour\_Over\_Matching}} (\algo) outlined in the previous section. The steps correspond to Algo \ref{algo:tom}. 
% The algorithm takes as input the set of objects $ \objectset $ and the start(and end) configuration $ \startq $ of the arms.

\noindent $ \mathtt{transfer\_graph} $: This function constructs a directed graph $ \graph $ defined by Eqs.~\ref{eq:transfergraph}. This step creates a graph with $ n $ vertices and $ \permu[n]{2} $ edges.

\begin{wrapfigure}{r}{0.6\textwidth}\vspace{-0.3in}
  \begin{minipage}{0.6\textwidth}
  \vspace{0pt} 
    \begin{algorithm}[H]
    \caption{{\tt \algo}$ (\objectset, \startq, \ainit, \atarget) $}
    \label{algo:tom}
    $ \graph \leftarrow \mathtt{transfer\_graph}(\objectset, \ainit, \atarget) $\;
    $ \scomaset^* \leftarrow \mathtt{optimal\_matching}(\graph) $\;
    $ \tspgraph \leftarrow \mathtt{transit\_graph}(\scomaset^*, \startq) $\;
    $ \scoma^+\leftarrow\mathtt{optimal\_tour}(\tspgraph) $\;
    $ \mathbf{\mathtt{return}}\ \trajset(\scoma^+)$\;
    \end{algorithm}
  \end{minipage}
  \vspace{-0.3in}
\end{wrapfigure}

\noindent $ \mathtt{optimal\_matching} $: This function takes the graph $ \graph $ constructed as an argument and returns the unordered set of edges, corresponding to the set of optimal transfers over $ \graph $. 
\commentdel{The first step is to convert the directed graph $ \graph $ into an equivalent undirected graph $ \graph_U $. Since $ \graph $ is complete, every pair of vertices has two directed edges between them. $\graph_U$ only preserves the minimally weighted connection for every vertex pair. Optimal matching is solved using an Edmond's Blossom Algorithm~\cite{edmonds1965maximum,galil1986ev} implementation~\cite{dezsHo2011lemon}. 
% Since the algorithm performs maximum matching by default, our desired minimally weighted matching can be obtained by subtracting the edge weights from some arbitrarily large number.
}
\commentadd{Optimal matching over an undirected graph can be solved using Edmond's Blossom Algorithm~\cite{edmonds1965maximum,galil1986ev,dezsHo2011lemon}. The directed graph $ \graph $ is converted into an equivalent undirected graph $ \graph_U $. Since $ \graph $ is complete, every pair of vertices shares two directed edges. $\graph_U$ only preserves the minimally weighted connection for every vertex pair. The result of matching}
% The result 
is a subset of edges on $ \graph_U $ which correspond to a set of directed edges on $ \graph $ i.e., $ \scomaset^* $. The runtime complexity of the step is $ O(|\edges||\nodes|\log|\nodes|) = O(\permu[n]{2}n\log n ) = O(n^3\log n)$.

\noindent $ \mathtt{transit\_graph} $: This function constructs the directed transit graph $ \tspgraph $ as per the set of Eqs.~\ref{eq:transitgraph}. This constructs $ \frac{n}{2} + 1 $ vertices and $ \permu[(\frac{n}{2} + 1)]{2} $ edges.

\noindent $\mathtt{optimal\_tour}  $: Standard TSP solvers like Gurobi~\cite{gurobi} can be used to find the  
% It should be noted that a lot of efficient solvers exist for such problems, that provide various degrees of approximation. 
optimal tour over $ \tspgraph $ corresponding to $ \scoma^+ $.

The costs are deduced from coordinated motion plans over edges. The total number of such calls compared to the count from the baseline in Equ. \ref{eq:mpcount}, shows a saving in the order of $ O(n^2)$ queries ($\textrm{\# of Transfers} + \textrm{\# of Moves}$). 
% \kiril{Consider completing the calculation.}
\vspace{-0.1in}
$$
\frac{\textrm{Baseline}\ \#}{{\algo}\ \#} = 
\frac{  {\permu[n]{2}} +   \Big{(}{{\permu[n]{2}}\times\permu[n-2]{2}}\Big{)} + \Big{(}2\times{\permu[n]{2}}\Big{)}   }
{\permu[n]{2} + \permu[(\frac{n}{2} + 1)]{2}} =
\frac{4(n-1)((n-5)n+9)}{5n-2}
$$\vspace{-0.1in}

The evaluation performed here focuses on the maximum of distances (Eq.~\ref{eq:cost_function}) for a fair comparison with the other methods. The prioritization of optimization objective, however, is also amenable to other cost functions, where carrying objects is often more expensive than object-free motions.

### 2018-10-29 06_integration.tex
Initial ShareLaTeX Import

The algorithms described so far are agnostic to the underlying motion planner.
Depending upon the model of the application domain, different motion planning primitives might be appropriate. For planar environments with disk robot pickers~(similar to delta robots), recent work~\cite{kirkpatrick2016characterizing} characterizes the optimal two-disk coordinated motions. The current implementation uses a general multi-robot motion planning framework \drrtstar~\cite{Dobson:2017aa} for dual-arm coordinated planning.

% It should be noted that sometimes such motion plans might not be found either because no such solution exists, or because of a limited time budget. In such cases the edge costs should either be set of some arbitrarily large value, or removed altogether.

In practice the cost of generating and evaluating two-arm motions can dominate the overall running time of the algorithm, when compared to the combinatorial ingredients that discover the high-level plan, i.e., execution order and and arm assignment. Even though \algo reduces this, further improvements can be made with lazy evaluation.

\begin{wrapfigure}{r}{0.6\textwidth}
  \vspace{-0.1in}
  \begin{minipage}{0.6\textwidth}
  \vspace{0pt} 
  \begin{algorithm}[H]
  \caption{{\tt Lazy\_Evaluation}$ (\mathtt{ALGO}, \mathcal{H}, \mathtt{MP}) $}
  \label{algo:lazy}
  $ \edges_{\mathtt{b}}\leftarrow\emptyset $;  $ \D \leftarrow \emptyset $\;
  \While{$ \D=\emptyset \land \mathtt{time\_not\_exceeded} $}
  {
  %	$ \mathtt{planner}\leftarrow\mathcal{H} $\;
      $ \scoma\leftarrow \mathtt{ALGO} ( \mathcal{H},   \edges_{\mathtt{b}}  ) $\;
  %	$ \mathtt{planner}\leftarrow\mathtt{MP} $;
%       $ \D \leftarrow \emptyset $\;
      \For{$ \coma_i, \coma_{i\rightarrow{i+1}} \in \scoma$}
      {
          $ \D_i,\D_{i\rightarrow i+1} \leftarrow \mathtt{MP}(\coma_i), \mathtt{MP}( \coma_{i\rightarrow{i+1}} ) $\;
          $ \D\leftarrow (\D,\D_i,\D_{i\rightarrow i+1} ) $\;
          \If{$ \D_i = \emptyset $}
          {
              $ \edges_{\mathtt{b}} \leftarrow \edges_{\mathtt{b}}\cup \{\coma_i\}$; $ \D \leftarrow \emptyset$\;
          }
          \If{$ \D_{i\rightarrow i+1} = \emptyset $}
          {
              $ \edges_{\mathtt{b}} \leftarrow \edges_{\mathtt{b}}\cup \{\coma_{i\rightarrow{i+1}}\}$; $\D \leftarrow \emptyset $\;
          }
          \lIf{$ \D=\emptyset $}
          {
          $\mathbf{break}$
          }
      }
  }
  $\mathbf{return}\ D$
  \end{algorithm}
  \end{minipage}
  \vspace{-0.35in}
\end{wrapfigure}

% \kiril{Are we referring to the correct paper here? }. 
% This heuristic corresponds to the pre-processed shortest path costs over underlying roadmaps. 
% \kiril{I suggest to replace this sentence with a high-level description omitting the term "underlying roadmaps": "This heuristic corresponds to pre-processed lower estimates of the shortest-path costs for the two arms."}
% The online part of the estimate is tantamount to a simple look-up.

\noindent\textbf{Lazy Evaluation}: Recent work~\cite{shome2017improving} introduces heuristics for $ \drrtstar $, which pre-process estimates of the shortest path costs for the arms. Dual-arm rearrangement can be significantly sped up if the motion planning queries are replaced with look-ups of such heuristics. Once a candidate $ \scoma $ is obtained, motion planning can evaluate the solution $ \trajset(\scoma) $. If this fails, the algorithm tries other sequences. 
% \kiril{In line 8 of the algorithm, the first "$D$" in the curly brackets is redundant, right?}

The algorithm Algo \ref{algo:lazy} takes as input the algorithm $ \mathtt{ALGO} $, a heuristic $ \mathcal{H} $, and a motion planner $ \mathtt{MP} $. $ \edges_{\mathtt{b}}$ keeps track of the blocked edges. The process keeps generating candidate solutions using the $ \mathtt{ALGO} $ (Line 3). Line 5 motion plans over the candidate solution, and appends to the result (Line 6). Any failures are recorded in  $ \edges_{\mathtt{b}}$ (Lines 8,10), and inform subsequent runs of $ \mathtt{ALGO} $.

\noindent\textbf{Completeness}: 
% The heuristic versions would be an approximation of the original optimization guarantees of the algorithms. It should be noted that this framework can be used with all the dual-arm approaches ie., exhaustive search, MILP and \algo. 
The lazy variants give up on optimality for the sake of efficiency but given enough retries the algorithms will eventually solve every problem that {\tt ALGO} can. Since the motion planning happens in the order of execution, the object non-interactivity assumption is relaxed.

\noindent\textbf{Smoothing}: 
% The solutions obtained out of the methods adhere to the defined synchronization assumptions of the problem. 
Applying velocity tuning over the solution trajectories for the individual arms relaxes the synchronization assumption
by minimizing any waits that might be a by-product of the synchronization. 
Smoothing does not change the maximum of distances, only improves execution time. Indications that the smoothed variants of the synchronous solutions do not provide significant savings in execution time are included in the Appendix for the interested reader.

It should be noted that in an iterative version of \algo, in order to explore variations in $ \scomaset^* $ if failures occur in finding $\tour$, some edges need to be temporarily blocked on $ \scomaset^* $. The search structures can also be augmented with {\tt NO\_ACT} tasks, for possible $\coma$ where one of the arms do not move. 
% This effectively includes single arm solutions in the search as well.

### 2018-10-29 07_cost_bounds.tex
Initial ShareLaTeX Import

Following from Lemma \ref{lem:transferdomination}, the current analysis studies the dual arm costs in the randomized unit tabletop setting, with $c_t$ as the cost measure per unit distance. 
For the $2$-arm setting, assume for simplicity that each arm's volume is represented as a disc of some radius 
$r$. For obtaining a $2$-arm solution, we partition the $n$ objects randomly 
into two piles of $\frac{n}{2}$ objects each; then obtain two initial solutions 
similar to the single arm case. It is expected (Eq.~\ref{eq:single-cost-simple}) that these two halves 
should add up to approximately $(c_{pd} + 0.52c_t)n$.

From the initial $2$-arm solution, we construct an {\em asynchronous} $2$-arm 
solution that is collision-free. Assume that pickups 
and drop-offs can be achieved without collisions between the two arms, which 
can be achieved with properly designed end-effectors. The main overhead 
is then the potential collision between the two (disc) arms during transfer 
and move operations. Because there are $\frac{n}{2}$ objects for each arm to work 
with, an arm may travel a path formed by $n + 1$ straight line 
segments. Therefore, there are up to $(n + 1)^2$ intersections between the 
two end-effector trajectories where potential collision may happen. However,
because for the transfers and transits associated with one pair of objects (one 
for each arm) can have at most four intersections, there are at most 
$2n$ potential collisions to handle. For each intersection, let one 
arm wait while letting the other circling around it, which incurs a cost that is bounded by $2\pi \cdot
r \cdot c_t$.

Adding up all the potential extra cost,  
% that a $2$-arm solution has 
a cumulative cost is obtained as 
% \begin{align}\label{eq:dual-cost-distance} 
% C_{dual} = C_{single} + 2n(2\pi rc_t) \approx (c_{pd} + 0.52c_t + 4\pi rc_t)n.
% \end{align}

{\centerline
{
$C_{\rm dual} = C_{\rm single} + 2n(2\pi rc_t) \approx (c_{pd} + 0.52c_t + 4\pi rc_t)n\;.$
}
}

\noindent For small $r$, $C_{\rm dual}$ is almost the same as $C_{\rm single}$ 
$c_t$ is a distance (e.g., energy) cost. Upon considering the maximum of the two arc lengths or makespan (Eq.~\ref{eq:cost_function}),
the $2$-arm cost becomes $C_{\rm dual}^t \approx (c_{pd} + 0.52c_t)\frac{n}{2} + 4n\pi rc_t$.
% \vspace{-0.1in}
% \begin{equation}\label{eq:dual-cost-time}
% C_{dual}^t \approx (c_{pd} + 0.52c_t)\frac{n}{2} + 4n\pi rc_t
% \vspace{-0.1in}
% \end{equation}
% {\centerline
% {
% $C_{dual}^t \approx (c_{pd} + 0.52c_t)\frac{n}{2} + 4n\pi rc_t$
% }
% }
The cost ratio is
\vspace{-0.1in}
\begin{equation}\label{eq:makespan-ratio}
\frac{C_{\rm dual}^t}{C_{\rm single}} \approx 
\frac{(c_{pd} + 0.52c_t)\frac{n}{2} + 4n\pi rc_t}{(c_{pd} + 0.52c_t)n}
= \frac{1}{2} + \frac{4\pi rc_t}{c_{pd} + 0.52c_t}\;.
% \vspace{-0.1in}
\end{equation}

\commentdel{
 \begin{wrapfigure}{r}{1.4in}
  \vspace{-.45in}
	\centering
    \includegraphics[width=1.4in]{figures/monte_carlo}
    \vspace{-.4in}
	\caption{Empirical cost ratio versus the estimate}
  	\label{fig:bounds}
    \vspace{-.4in}
\end{wrapfigure}
}

When $r$ is small or when $\frac{c_t}{c_{pd}}$ is small, the $2$-arm 
solution is roughly half as costly as the single arm solution. On 
the other hand, in this model a $2$-arm solution does not do better than $\frac{1}{2}$ of 
the single arm 
solution. This argument can be extended to $k$-arms as well.
\vspace{-0.08in}
\commentadd{
\begin{theorem}
For rearranging objects with non-overlapping starts and goals that are
uniformly distributed in a unit square,  a $2$-arm solution can have an 
asymptotic improvement of $\frac{1}{2}$ over the single arm solution. 
\label{thm:karm}
\end{theorem}
}
The synchronization assumption changes the expected cost of the solution. The random partitioning of the $n$ objects into two sets of $\frac{n}{2}$ object with a random ordering of the objects yields $\frac{n}{2}$ pairs of objects transfers, which dominate the total cost for large $n$. The cost~(Eq.~\ref{eq:cost_function}) of $\frac{n}{2}$ synchronized transfers ($\coma_i$) includes $\frac{n}{2}c_{pd}$ and $C^{\rm sync}_{sg} \approx (\mathtt{E}(max(l_1,l_2))c_t)\frac{n}{2}$, where $\mathtt{E}(max(l_1,l_2))$ is the expected measure of the max of lengths $l_1$,$l_2$ of two randomly paired transfers. Using the \textit{pdf}\cite{ghosh1951random} of lengths of random lines in an unit square and integrating over the setup, results in the value of $\mathtt{E}(max(l_1,l_2))$ to be $0.66$. 
% (Section \ref{sec:appendix}). 
This means $C_{\rm dual}^{\rm sync} \approx (c_{pd} + 0.66c_t)\frac{n}{2} + 4n\pi rc_t$.
% \vspace{-0.1in}
% \begin{equation}\label{eq:synchronized-cost}
% C_{dual}^{sync} \approx (c_{pd} + 0.66c_t)\frac{n}{2} + 4n\pi rc_t
% \vspace{-0.1in}
% \end{equation}
% {\centerline
% {
% $C_{dual}^{sync} \approx (c_{pd} + 0.66c_t)\frac{n}{2} + 4n\pi rc_t$
% }
% }
The synchronized cost ratio is
\vspace{-0.1in}
\begin{equation}\label{eq:synchronized-ratio}
\frac{C_{\rm dual}^{\rm sync}}{C_{\rm single}} \approx 
\frac{(c_{pd} + 0.66c_t)\frac{n}{2} + 4n\pi rc_t}{(c_{pd} + 0.52c_t)n}
= \frac{1}{2} + \frac{ (0.07 + 4\pi r)c_t}{c_{pd} + 0.52c_t}\;.
\vspace{-0.1in}
\end{equation}

When $\frac{c_t}{c_{pd}}$ is small, even the synchronized $2$-arm solution provides an improvement of $\frac{1}{2}$. For the case when both $r$ and $c_{pd}$ are small, we observe that the ratio approaches $0.636$. 
\commentdel{Fig \ref{fig:bounds} confirms empirically that in randomized trials on an unit square, the ratio of $\frac{C_{dual}^{sync}}{C_{single}}$ when $c_{pd}=0,r=0$, converges to the calculated estimate (red line).}
\vspace{-0.08in}
\begin{theorem}
For rearranging objects with non-overlapping starts and goals that are 
uniformly distributed in a unit square,  a randomized $2$-arm synchronized solution can have an 
asymptotic improvement of $\frac{1}{2}$ over the single arm solution if $\frac{c_t}{c_{pd}}$ is small, and a improvement $\approx 0.64$ when both $c_{pd}$ and $r$ are small. 
\end{theorem}

\commentadd{
\noindent \textbf{Note on bounds:} The proposed simplified model does not apply immediately to general configuration spaces, where the costs and collision volumes do not have the same nice properties of a planar disk setup. The experimental section, however, indicates that the benefits and speedups exist in these spaces as well.
}
% \rahul{this paragraph is phrased contradictorily. It makes sense if the first sentence is for asynchronous cases.}
% We note that the same can be said for a {\em synchronous} $2$-arm solution if
% when $c_t/c_{pd}$ is small. 
% Under the synchronization assumption, $C_{dual}^t$
% is no longer necessarily expected to be $\frac{C_{single}}{2}$ for large $n$. 
% Experiments in the next section indicate that improvements over single arm solutions in practical settings.

%\textcolor{red}{NOTE: We can also generate plots illustrating how the ratio 
%change as $n$, $r$, $c_{pd}:c_t$ changes. We may also further generalize the 
%$r$ based collision term to a more general collision term.}

%\begin{figure}[h]
%%  \begin{center}
%\centering
%    \includegraphics[width=2in]{figures/bounds}
%%  \end{center}
%  \caption{Bounds}
%  	\label{fig:bounds}
%\end{figure}

### 2018-10-29 08_evaluation.tex
Initial ShareLaTeX Import

%\textit{Describe experiments: we will design benchmarks per model
%Describe alternative algorithms }
%a) \textit{single-arm solution per model,}
%b) \textit{exhaustive search integrated with the corresponding path planner for each model,}
%c) \textit{approximate solution we propose [unless we come up with something
%  better for the easier models].}
%d) \textit{1-TSP broken into 2 and coordinated}
%
%\textit{What do we measure: a) solution quality in terms of the cost metrics
%identified and b) computation time.}

\begin{wrapfigure}{r}{2.2in}
    \vspace{-.3in}
	\centering
		\includegraphics[width=1.1in,trim={1cm 9cm 1cm 5cm},clip]{figures/simple_picker_benchmark}
		\includegraphics[width=1.05in]{figures/kuka_benchmark2}
		\vspace{-.3in}
		\caption{\textit{Picker} and \textit{Manipulator} trials.}
		\label{fig:benchmarks}
    \vspace{-.25in}
\end{wrapfigure}
This section describes the experiments performed to evaluate the algorithms in two  domains shown in Fig \ref{fig:benchmarks}: a) simple picker and b) general manipulators.
%\begin{figure}[ht]
%	\centering
%	\includegraphics[width=1.9in]{figures/simple_picker_benchmark}
%	\includegraphics[width=1.8in]{figures/kuka_benchmark2}
%	\caption{The benchmarks: \textit{Simple Picker} and the \textit{General Manipulators} }
%	\label{fig:benchmarks}
%\end{figure}
In order to ensure monotonicity, the object starts and goals do not overlap. Uniform cuboidal objects simplify the grasping problem, though this is not a limitation of the methods. $ 50 $ random experiments were limited to $300s$ of computation time. The underlying $ \drrtstar $ motion planner is restricted to a max of $ 3s $ per plan.
A comparison point includes a random split method, which splits $ \objectset $ at random into two subsets and chooses an arbitrary ordering. Maximum of distances cost is compared to the single arm solution~\cite{193}. Computation times and success rates are reported. The trends in both experiments show that in the single-shot versions, exhaustive and \milp tend to time-out for larger $n$. Lazy variants scale much better for all the algorithms, and in some cases increase the success ratio due to retries. \algo has much better running time than exhaustive and \milp, and producing better and more solutions than random split. Overall, the results show a) our \milp succeeds more within the time limit than exhaustive, b) \algo scales the best among all the methods, and c) the cost of solutions from \algo is close to the optimal baseline, which is around half of the single arm cost.
% to demonstrate the gains from using multiple arms.  Overall, MILP scales better than exhaustive search, while finding optimal solutions. \algo scales better than the other methods, and finds high quality solutions. The lazy variants improve all the dual-arm methods.

%\subsection{Simple Picker}
%The results are shown in Figure~\ref{fig:disk}.
\textbf{Simple Picker}: This benchmark evaluates two disk robots hovering over a planar surface scattered with objects. The robots are only free to move around in a plane parallel to the resting plane of the objects, and the robots can pick up objects when they are directly above them. Fig~\ref{fig:disk}(\textit{top}) all runs up to $ 24 $ objects succeeded for \algo. \milp scales better than exhaustive. Lazy random split succeeds in all cases~(\textit{bottom}). In terms of solution costs~(\textit{middle}) exhaustive finds the true optimal. \milp matches exhaustive and \algo is competitive. In all experiments, \algo enjoys a success rate of 100\%.
% \kiril{What is the reason for low success rate of exhaustive and milp? Is it due to exceeding the time budget?} \kiril{This paragraph misses a statement that demonstrates the benefits of our approach: "In all experiments, \algo enjoys a success rate of \%100, while having much better running time than exhaustive and milp, and producing a higher cost solution than random split. Furthermore, \algo produces a plan whose cost is around half of the single arm plan cost." Similar statements should be added to the other experiments.}

%\subsection{General Manipulator}
%The results are shown in Figure~\ref{fig:kuka}.

\textbf{General Dexterous Manipulator}: The second benchmark sets up two \kuka arms across a table with objects on it. The objects are placed in the common reachable part of both arms' workspace, and only one top-down grasping configuration is allowed for each object pose. Here (Fig~\ref{fig:kuka}) a larger number of motion plans tend to fail, so the single shot variants show artifacts of the randomness of \drrtstar in their success rates. 
% The lazy iterative variants show the robust scalability. 
Random split performs the worst since it is unlikely to chance upon valid motion plans. Single shot exhaustive and \milp scale poorly because of expensive motion planning.
Interestingly, motion planning infeasibility reduces the size of the exhaustive search tree.
The solution costs \textit{(middle)} substantiate benefits of the use of two arms. The computation times \textit{(bottom)} again show the scalability of \algo, even compared to random split.
% In terms of cost. MILP scales to more objects but the computational overhead is more than \algo. Dual-arm solutions are significantly better than single arm.

\begin{figure}[h]
\vspace{-0.2in}
	\centering
%	\includegraphics[width=2.1in]{figures/disk_solution}
%	\includegraphics[width=2.1in]{figures/disk_timing}
%	\includegraphics[width=2.1in]{figures/disk_more_solution}
%	\includegraphics[width=2.1in]{figures/disk_more_timing}
	\includegraphics[width=3.5in]{figures/results/labels}
	\includegraphics[width=2.25in]{figures/results/4_sp_ms_success}
	\includegraphics[width=2.25in]{figures/results/3_sp_lazy_ms_success}
	\includegraphics[width=2.25in]{figures/results/4_sp_ms_cost}
	\includegraphics[width=2.25in]{figures/results/3_sp_lazy_ms_cost}
	\includegraphics[width=2.25in]{figures/results/4_sp_ms_time}
	\includegraphics[width=2.25in]{figures/results/3_sp_lazy_ms_time}
	\vspace{-0.15in}
	\caption{\textit{Simple Picker} results with success\textit{(top)}, solution costs\textit{(middle)}, and computation\textit{(bottom)} reported for single-shot\textit{(left)} and lazy\textit{(right)} versions of the methods}
    \vspace{-0.3in}
	\label{fig:disk}
\end{figure}

\begin{figure}[h]
\vspace{-0.2in}
	\centering
	\includegraphics[width=3.5in]{figures/results/labels}
	\includegraphics[width=2.25in]{figures/results/2_kuka_ms_success}
	\includegraphics[width=2.25in]{figures/results/1_kuka_lazy_ms_success}
	\includegraphics[width=2.25in]{figures/results/2_kuka_ms_cost}
	\includegraphics[width=2.25in]{figures/results/1_kuka_lazy_ms_cost}
	\includegraphics[width=2.25in]{figures/results/2_kuka_ms_time}
	\includegraphics[width=2.25in]{figures/results/1_kuka_lazy_ms_time}
	\vspace{-0.15in}
    \caption{\textit{\kuka}results with success\textit{(top)}, solution costs\textit{(middle)}, and computation\textit{(bottom)} reported for single-shot\textit{(left)} and lazy\textit{(right)} versions of the methods}
    \vspace{-0.3in}
	\label{fig:kuka}
\end{figure}

### 2018-10-29 09_discussion.tex
Initial ShareLaTeX Import

The current work demonstrates the underlying structure of synchronized dual-arm rearrangement and proposes an \milp formulation, as well as a scalable algorithm \algo that provides fast, high quality solutions. Existing efficient solvers for reductions of the dual-arm problem made \algo effective. Future work will attempt to explore the $k-$arm case and instances of non-monotone rearrangement. The incorporation of manipulation and regrasp reasoning can extend these methods to more cluttered domains.

% It can be shown however that efficient approximate solvers for more than 2 arms would be hard to design.
% Let us assume a $ \rho $-Approx algorithm, $\mathbb{A}$ exists for the problem of rearrangement with 3 arms. Assume a hypothetical manipulator that incurs a constant transit cost on a bounded plane. The problem of an optimal set of object assignments reduce to 3D-Matching. $ \rho $-Approx $\mathbb{A}$ should return a solution to 3DM. Since 3DM is hard to approximate, $\mathbb{A}$ does not exist.\kiril{The connection with 3DM is not immediate, and I don't think that there's enough information provided here in order to make sense of it. I suggest to omit this description, especially if space is limited.}

### 2018-10-29 10_appendix.tex
Initial ShareLaTeX Import

% \usepackage{amsmath,amsfonts,amssymb,mathrsfs}
% \usepackage{graphicx}
% \usepackage{psfrag,graphicx,epsfig,epsf}
% \usepackage[ruled,linesnumbered, noend]{algorithm2e}
% \usepackage{fancyhdr}
% \usepackage{wrapfig}
% \usepackage{subfigure}
% \usepackage{mathtools}
% \usepackage{url}
% \usepackage{color}
% \usepackage{verbatim}
% \usepackage{xspace}

% \DeclareMathOperator*{\argmin}{arg\,min}

% \newcommand\permu[2][^n]{\prescript{#1\mkern-2.5mu}{}P_{#2}}
% \newcommand\combi[2][^n]{\prescript{#1\mkern-0.5mu}{}C_{#2}}

% \begin{document}

% \title{Fast High-Quality Dual-Arm Rearrangement in Synchronous, Monotone Tabletop Setups: Appendix}
% %\titlerunning{Fast Methods for Synchronized Tabletop Dual-Arm Rearragement}
% \author{Rahul Shome$^1$ \and Kiril Solovey$^2$ \and Jingjin Yu$^1$ \and Kostas Bekris$^1$ \and Dan Halperin$^2$}
% %\authorrunning{Shome et al.}
% \institute{$^1$Rutgers University, NJ, USA and $^2$Tel Aviv University, Israel}

% \maketitle
% \input{notation}
% \documentclass{llncs}

%####################################################################################
%####################################################################################
%####################################################################################
%####################################################################################
%####################################################################################

\subsection{Expected k-arm cost bounds in a planar disk manipulator model}
\commentadd{
The arguments made in Theorem \ref{thm:karm} can be extended to $k$ disc arms.
In the planar unit-square setting, with $k$ arms, there are $\frac{n}{k}$ objects 
for each arm to work with. Consider the transfers and transits of a set of $k$ 
objects, one for each arm. By \cite{ChiHanYu2018WAFR}, the arbitrary rearrangement of $k$ discs 
can be achieved in a bounded region with a perimeter of $O(kr)$. 
Clearly, the per robot additional (makespan or distance) cost is bounded by some 
function $f(k, r)c_t$, which goes to zero as $r$ goes to zero. Adding up all the potential 
extra cost,  a $k$-arm solution has a cumulative cost

{\centerline
{
$C_{\rm k{\text-}arm} = C_{\rm single} + nf(k,r)c_t \approx (c_{pd} + 0.52c_t + f(k,r)c_t)n\;.$
}
}

\noindent For fixed $k$ and small $r$, $C_{\rm k{\text-}arm}$ is almost the same as $C_{\rm single}$.
%, $c_t$ is a distance (e.g., energy) cost. 
Upon considering the maximum of the two arc lengths or makespan,
the $k$-arm cost becomes $C_{\rm k{\text-}arm}^t \approx (c_{pd} + 0.52c_t)\frac{n}{k} + nf(k,r)c_t$.

The cost ratio is
\vspace{-0.1in}
\begin{equation}\label{eq:kmakespan-ratio}
\frac{C_{\rm k{\text-}arm}^t}{C_{\rm single}} \approx 
\frac{(c_{pd} + 0.52c_t)\frac{n}{k} + nf(k,r)c_t}{(c_{pd} + 0.52c_t)n}
= \frac{1}{k} + \frac{f(k,r)c_t}{c_{pd} + 0.52c_t}\;.
% \vspace{-0.1in}
\end{equation}

When $r$ is small or when $\frac{c_t}{c_{pd}}$ is small, the $k$-arm 
solution is roughly $\frac{1}{k}$ as costly as the single arm solution. On 
the other hand, in this model a $k$-arm solution does not do better than $\frac{1}{k}$ of 
the single arm.

\begin{theorem}
For rearranging objects with non-overlapping starts and goals that are
uniformly distributed in a unit square,  a $k$-arm solution can have an 
asymptotic improvement of $\frac{1}{k}$ over the single arm solution. 
\end{theorem}
}
% \rahul{Need to verify this line of reasoning}

\subsection{Expected measure of the maximum of lengths of two random lines on an unit square}
Prior work \cite{ghosh1951random} defines the \textit{pdf} of lengths($l$) of randomly sampled lines in a rectangle of sides $a,b, \ \ a\geq b$ as 
\begin{align*}
p(l) &= (\frac{4l}{a^2b^2})\phi(l)\\
\phi(l)&= \frac{1}{2}\pi a b - a l - b l + \frac{1}{2} l^2, \ \ l\in[0,b]\\
\phi(l)&= ab \sininv(\frac{b}{l}) + a. \sqrt[]{(l^2-b^2)} - al - \frac{1}{2}b^2, \ \ l\in[b,a]\\
\phi(l)&= ab\{\sininv(\frac{b}{l})-\cosinv(\frac{a}{l})\} + a\sqrt[]{(l^2-b^2)} + b\sqrt[]{(l^2-a^2)} \\
&- \frac{1}{2}(l^2+a^2+b^2),\ \ l\in[a,\sqrt[]{(a^2+b^2)}]
\end{align*}

In the unit square model, $a=b=1$. Substituting the values, the \textit{pdf} becomes
\begin{align}
p(l)&= 2\pi l - 8\pi l^2 + 2l^3, \ \ l\in[0,1]\\
p(l)&= 4l\sininv(\frac{1}{l}) - 4l\cosinv(\frac{1}{l}) + 8l\sqrt[]{(l^2-1)} -2l^3 -4l, \ \ l\in[1,\sqrt[]{2}]
\end{align}

Assuming two random sets of lines, representing transfers in a random split of objects between two arms, we need the expected value of the maximum of these pairwise lengths ie., $\mathtt{E}(max(l_1,l_2)), \ \ l_1,l_2\ i.i.d, \ \ l_1 \sim p, l_2 \sim p$.
This is estimated using the \textit{pdf} obtained. 
\begin{equation}
\mathtt{E}(max(l_1,l_2)) = \int_0^{\sqrt[]{2}} \int_0^{\sqrt[]{2}} max(l_1,l_2)p(l_1)p(l_2) dl_2 dl_1 \approx 0.663
\end{equation}
The result is calculated by taking into account the combination of different ranges of $p(l)$ and $max(l_1,l_2)$.
\commentadd{
\begin{wrapfigure}{r}{1.4in}
	\centering
	\vspace{-0.3in}
    \includegraphics[width=1.4in]{figures/monte_carlo}
	\caption{Empirical cost ratio versus the estimate}
  	\label{fig:bounds}
\end{wrapfigure}

Prior work~\cite{santalo2004integral} offered an estimate for the expected length of a transit path $C_{sg}$ in terms of the expected length of a line segment, $0.52$, in a randomized setting in an unit square. With the current estimate of $0.663$ for the maximum of two such randomly sampled line segments, it follows that, the expected makespan or maximum of distances cost will use this estimate.

Using this result, the synchronized cost ratio is stated in Equation~\ref{eq:synchronized-ratio} as
$$
\frac{C_{\rm dual}^{\rm sync}}{C_{\rm single}} \approx 
\frac{(c_{pd} + 0.66c_t)\frac{n}{2} + 4n\pi rc_t}{(c_{pd} + 0.52c_t)n}
$$
As a way to validate our asymptotic estimate, randomized trials were run with different number randomly sampled object transfer coordinates on an unit square.
% Fig \ref{fig:bounds} verifies empirically that the ratio of $\frac{C_{dual}^{sync}}{C_{single}}$ when $c_{pd}=0,r=0$, asymptotically converges to the calculated expected value of $0.636$. 
When $c_{pd}=0$ and $r=0$, the ratio of $\frac{C_{dual}^{sync}}{C_{single}}$ evaluates to $0.636$. Fig \ref{fig:bounds} verifies empirically that the ratio converges to the expected value as the number of transfers increases.
This indicates the asymptotic speedup of a synchronized dual arm solution for a makespan or maximum of distances cost metric.
}

\subsection{Smoothing}
The result of the velocity tuning over the solution trajectories for the individual arms as a post-processing step is shown in Fig \ref{fig:smoothing}. The objective is to minimize any waits that might be a by-product of the synchronization. 
% The small improvements indicate that synchronization does not adversely affect the solution executions. 
The small \% improvements indicate that the asynchronous variants of the solutions discovered from the methods do not yield a big enough saving in execution time. 
Most of the improvement as a percentage of the original solution duration is not too high. On top of that, the time taken to smooth the solutions for \algo (overlaid on Fig \ref{fig:smoothing}) shows that it is often not beneficial.
In their largest problem instances the \kuka spent $ 0.44s $ of smoothing time to save $ 3.23s $ off the solution duration, while the picker spent $  9.84s $ to save $ 0.54s $.
This indicates that among the class of synchronized solutions discovered by the proposed algorithms, the analogous asynchronous variants do not seem to be drastically better. Moreover, smoothing does not improve the maximum of distances cost measure, but only reduces the solution duration. The theoretical bounds in the simple planar setups agree with the results in that the synchronization does not degrade the benefits of using 2 arms too much. It should be pointed out though that it needs to be studied further, whether these trends would hold for a class of algorithms that can solve the asynchronous dual-arm rearrangement problem in general setups. This is out of the scope of the current work.

% \kiril{What is the bottom line here? Is smoothing worthwhile? The y-axis in the plots is labeled as \% whereas the bars are labeled with seconds.}

% \vspace{-0.2in}
\begin{figure}
	\centering
	\includegraphics[width=2.3in]{figures/results/sp_smoothing}
	\includegraphics[width=2.3in]{figures/results/kuka_smoothing}
	\caption{Smoothed solution improvement as a percentage of the original synchronized solution duration, and the time taken to smooth solutions obtained from \algo in seconds.}
	\label{fig:smoothing}
%     \vspace{-.3in}
\end{figure}

%####################################################################################
%####################################################################################
%####################################################################################
%####################################################################################
%####################################################################################
% {\small
% \bibliographystyle{spmpsci}
% \bibliography{bib/manip}}

% \end{document}

### 2018-10-29 01_introduction.tex
Bringing it down to the page limit

@@
 synchronized execution of pick-and-place actions by the two arms. i.e., where the two arms simultaneously transfer (different) objects, or simultaneously move towards picking the next objects.
-Theoretical arguments and experimental evaluation indicate that the
-synchronization assumption does not significantly degrade solution
+Theoretical arguments and experimental evaluation indicate that this does not significantly degrade solution
 quality.
@@
 proposed that achieves optimal coordinated solutions in this domain.
-An efficient algorithm {\tt Tour\_Over\_Matching} (\algo) is proposed
-that significantly improves in scalability. \algo\ first optimizes the
+The proposed efficient algorithm {\tt Tour\_Over\_Matching} (\algo) significantly improves in scalability. \algo\ first optimizes the
 cost of object transfers and assigns objects to the two arms by
@@
 lower-level motion planner that coordinates the two arms. A lazy
-evaluation strategy is proposed, where candidate solution sequences
-are developed first and then motion plans are evaluated for them. The
-strategy results in significant computational improvement and
-minimizes the calls to the coordination motion planner.  An analysis
-is also performed on the expected improvement in solution quality
+evaluation strategy is proposed, where motion plans are evaluated for candidate solution sequences. This results in significant computational improvement and
+reduces the calls to the motion planner.  An analysis
+studies the expected improvement in solution quality
 versus the single arm case, as well as the expected cost overhead from a
@@
 
-Finally, experiments for i) a simple planar picker setting, and ii) a
-model of two 7-DOF Kuka arms, demonstrate a nearly two-fold
-improvement against the single arm case for the proposed approach in practice. The
-solutions are close to optimal for the dual-arm case and the algorithm
-exhibits good scalability. The computational costs of both the optimal
-and the proposed method are significantly improved from the lazy
-evaluation strategy. 
+Finally, experiments for i) a simple planar picker setting, and ii) two 7-DOF Kuka arms, demonstrate a nearly two-fold
+improvement against the single arm case for the proposed approach in practice. The algorithm exhibits close to optimal solutions and good scalability. 
+The lazy evaluation strategy significantly improves computation costs for both the optimal and proposed methods.
+%The computational costs of both the optimal
+%and the proposed method are significantly improved from the lazy
+%evaluation strategy. 
 % When the synchronous solutions are smoothed to

### 2018-10-29 04_baseline.tex
Bringing it down to the page limit

@@
 \end{equation*}
-where $\permu[n]{k}$ denotes the number of $k$-permutations of $n$.
+where $\permu[n]{k}$ is the $k$-permutations of $n$.
 
 \begin{wrapfigure}{r}{2.4in}
-    \vspace{-.1in}
+    \vspace{-.5in}
 	\centering
-	\includegraphics[width=2.3in]{figures/dual_backtracking.PNG}
+	\includegraphics[width=1.8in]{figures/dual_backtracking.PNG}
     \vspace{-.15in}
-	\caption{Search tree for 4 objects. In node $XY$, $m^1$ transfers object $X$, and $m^2$ transfers $Y$. An edge is a transit to the next node. }
+	\caption{Search tree for 4 objects. 
+%	In node $XY$, $m^1$ transfers object $X$, and $m^2$ transfers $Y$. An edge is a transit to the next node. 
+	}
 	\label{fig:backtracking}

### 2018-10-29 05_approximation.tex
Bringing it down to the page limit

@@
 
+\vspace{-0.13in}
 {\lemma [Perfect Matching]
@@
 As per the decomposition of the costs in Eq.
-\ref{eq:cost_function}, it follows that the $ \cost(\scomaset) $ corresponds to the cost of the transfers in the solution.
-Given the reduction to edge-matching, the solution to the minimum-weight perfect edge matching problem on such a graph would correspond to a $ \scomaset $ that optimizes the cost of \textit{transfers} of all the objects.
+\ref{eq:cost_function}, it follows that the $ \cost(\scomaset) $ is the cost of the transfers in the solution.
+The solution to the minimum-weight perfect edge matching problem on such a graph would correspond to a $ \scomaset $ that optimizes the cost of \textit{transfers} of all the objects.
 
@@
 This is a complete tour over~$ \tspgraph $, that visits all the vertices i.e., an ordered sequence of vertices $\tour = ( {\startq}, \scoma_\tour, {\startq}  )$.
-
+\vspace{-0.1in}
 {
@@
 The insight here is that, even though $ \scoma^+ $ reports a solution to a hierarchical optimization objective, the algorithm operates over a much smaller search space, and operates over sub-problems which are more efficient to solve than the baselines.\\
+
+\vspace{-0.1in}
 

### 2018-10-29 07_cost_bounds.tex
Bringing it down to the page limit

@@
 \commentadd{
-\noindent \textbf{Note on bounds:} The proposed simplified model does not apply immediately to general configuration spaces, where the costs and collision volumes do not have the same nice properties of a planar disk setup.
-The experimental section, however, indicates that the benefits and speedups exist in these spaces as well.
+\noindent \textbf{Note on bounds:} Even though the proposed simplified model does not apply immediately costs and collision volumes in general configuration spaces, experiments indicate that the speedups exist in these spaces as well.
 }

### 2018-10-29 08_evaluation.tex
Bringing it down to the page limit

@@
 \begin{wrapfigure}{r}{2.2in}
-    \vspace{-.3in}
+    \vspace{-.6in}
 	\centering
@@
 		\label{fig:benchmarks}
-    \vspace{-.25in}
+    \vspace{-.3in}
 \end{wrapfigure}
@@
 	\includegraphics[width=3.5in]{figures/results/labels}
-	\includegraphics[width=2.25in]{figures/results/4_sp_ms_success}
-	\includegraphics[width=2.25in]{figures/results/3_sp_lazy_ms_success}
-	\includegraphics[width=2.25in]{figures/results/4_sp_ms_cost}
-	\includegraphics[width=2.25in]{figures/results/3_sp_lazy_ms_cost}
-	\includegraphics[width=2.25in]{figures/results/4_sp_ms_time}
-	\includegraphics[width=2.25in]{figures/results/3_sp_lazy_ms_time}
+	\includegraphics[width=2in]{figures/results/4_sp_ms_success}
+	\includegraphics[width=2in]{figures/results/3_sp_lazy_ms_success}
+	\includegraphics[width=2in]{figures/results/4_sp_ms_cost}
+	\includegraphics[width=2in]{figures/results/3_sp_lazy_ms_cost}
+	\includegraphics[width=2in]{figures/results/4_sp_ms_time}
+	\includegraphics[width=2in]{figures/results/3_sp_lazy_ms_time}
 	\vspace{-0.15in}
@@
 	\includegraphics[width=3.5in]{figures/results/labels}
-	\includegraphics[width=2.25in]{figures/results/2_kuka_ms_success}
-	\includegraphics[width=2.25in]{figures/results/1_kuka_lazy_ms_success}
-	\includegraphics[width=2.25in]{figures/results/2_kuka_ms_cost}
-	\includegraphics[width=2.25in]{figures/results/1_kuka_lazy_ms_cost}
-	\includegraphics[width=2.25in]{figures/results/2_kuka_ms_time}
-	\includegraphics[width=2.25in]{figures/results/1_kuka_lazy_ms_time}
+	\includegraphics[width=2in]{figures/results/2_kuka_ms_success}
+	\includegraphics[width=2in]{figures/results/1_kuka_lazy_ms_success}
+	\includegraphics[width=2in]{figures/results/2_kuka_ms_cost}
+	\includegraphics[width=2in]{figures/results/1_kuka_lazy_ms_cost}
+	\includegraphics[width=2in]{figures/results/2_kuka_ms_time}
+	\includegraphics[width=2in]{figures/results/1_kuka_lazy_ms_time}
 	\vspace{-0.15in}

### 2018-10-29 02_background.tex
Bringing it down to the page limit

@@
 The current work dealing with dual-arm object rearrangement touches upon the challenging intersection of a variety of rich bodies of prior work.
-It is closely related to multi-robot planning and coordination.
-The challenge with multi-body planning is the high dimensionality of the configuration space.
+It is closely related to multi-robot planning and coordination where a challenge is the high dimensionality of the configuration space.
 %Early work has suggested to slightly reduce the~\cite{aronov1999motion} tried dimensionality reduction strategies.
 Optimal strategies were developed for simpler instances of the problem \cite{solovey2015motion}, although in general the problem is known to be computationally hard~\cite{solovey2016hardness}.
-Decentralized approaches~\cite{van2005prioritized} also used velocity tuning~\cite{leroy1999multiple} to deal with these difficult instances.
+Decentralized approaches~\cite{van2005prioritized} also used velocity tuning~\cite{leroy1999multiple}.
 General multi-robot planning tries to plan for multiple high-dimensional platforms \cite{wagner2012probabilistic,Gharbi:2009fu} using sampling-based techniques.
@@
 %This can itself be tweaked with assumptions on same or different start and goal positions, symmetric or asymmetric metrics, directed or undirected graphs or posing the problem as an optimization
-A seminal paper~\cite{frederickson1976approximation} provides the formulation for k-TSP, with solutions that split a single tour.
-Prior work \cite{rathinam2006matroid} has formulated the problem of multi-start to multi-goal k-TSP as an optimization task.
+%A seminal paper~\cite{frederickson1976approximation} provides the formulation for k-TSP, with solutions that split a single tour.
+%Prior work \cite{rathinam2006matroid} has formulated the problem of multi-start to multi-goal k-TSP as an optimization task. 
+Prior work has formulated the k-TSP solution in terms of splitting a single tour~\cite{frederickson1976approximation} or as an optimization task~\cite{rathinam2006matroid}.
 Some work~\cite{friggstad2013multiple} deals with asymmetric edge weights which are more relevant to the problems of our interest. 
-
 %\textbf{Errand Scheduling}:
@@
 %There has been prior work \cite{garg2000polylogarithmic} that operates over the assignment graph(where pairwise assignments are nodes), an object's group consists of sets of nodes that include an object
-
-The multi-arm rearrangement can also be posed as an instance of multi vehicle pickup and delivery (PDP)~\cite{parragh2008survey}. 
+The problem can be posed as an instance of multi vehicle pickup and delivery (PDP)~\cite{parragh2008survey}. 
 %Most of the work has been motivated by ride-sharing applications and timed task scheduling, so there are a lot of variations that deal with time windows but this line of research provides some ILP formulations for the problem.
 Prior work~\cite{coltin2014multi} has applied the PDP problem to robots, taking into account time windows and robot-robot transfers.
-Some seminal work~\cite{lenstra1981complexity,savelsbergh1995general} has also explored its complexity, and concedes to the hardness of the problem, while others have studied cost bounds~\cite{TrePavFra13}.
-ILP formulations~\cite{savelsbergh1995general} have also been proposed.
+Some seminal work~\cite{lenstra1981complexity,savelsbergh1995general} has explored its complexity, and concedes to the hardness of the problem, while others studied cost bounds~\cite{TrePavFra13}, and proposed ILP formulations~\cite{savelsbergh1995general}.
 %The existing work that delves into the combinatorial challenges of the problem, do not account for the costs incurred due to coordination of the agents during task execution. 
 %Pickup and Delivery problems under track contention \cite{caricato2003parallel}, makes an attempt to reason about the coordination of the robots over solutions obtained with Tabu Search.
-Typically this line of work ignores coordination costs, though some methods~\cite{caricato2003parallel} reason about it once candidate solutions are obtained.
+Typically this line of work ignores coordination costs, though some methods~\cite{caricato2003parallel} reason about it on candidate solutions.
 
@@
 General task planning methods are unaware of the underlying structure studied in this work.
-Single-arm rearrangement solutions will also not effective in this setting.
+Single-arm rearrangement solutions will also not be effective in this setting.
 The current work tries to bridge this gap and provide insights regarding the structure of dual-arm rearrangement.

### 2018-10-29 05_approximation.tex
Bringing it down to the page limit

@@
 
-\begin{wrapfigure}{r}{2.5in}\vspace{-0.5in}
+\begin{wrapfigure}{r}{2.5in}
+\vspace{-0.15in}
 % \begin{figure}[H]
@@
 For instance, as shown in Fig \ref{fig:edge_matching}(middle), $\edge(A,B)$ corresponds to $ \arm^1 $ transferring `A', while $ \arm^2 $ transfers `B', and the $\cost( \edge(A,B) ) = \cost(T(\coma=(A,B))$ is the cost of such a concurrent motion.
-Note that these costs refer to only the transfer costs i.e., starting from the arms picking up the objects $ A $ and $ B $ at the initial poses(as shown in Fig \ref{fig:edge_matching}(left)), and moving them to their target poses.
-It should also be noted that since the arms are different, in general, $\cost( \edge(A,B) )$ is not necessarily equal to $\cost( \edge(B,A) )$.
+%Note that these costs refer to only the transfer costs i.e., starting from the arms picking up the objects $ A $ and $ B $ at the initial poses(as shown in Fig \ref{fig:edge_matching}(left)), and moving them to their target poses.
+It should also be noted that since the arms are different, in general, $\cost( \edge(A,B) ) \neq \cost( \edge(B,A) )$.
 
@@
 $ \scoma $ is an ordered sequence of $ \coma $, and $ \scomaset $ denote the unordered set of all $ \coma $ that comprise $ \scoma $.
-Since $ \graph $ is a complete graph where every edge corresponds to every possible valid $ \coma $, $ \scomaset $ must also be a part of $ \graph $. 
-From the construction of the graph $ \graph $, $ \scomaset \subset \edges$.
-By definition, a candidate solution of a monotone dual-arm rearrangement problem must transfer every object exactly once.
+Since $ \graph $ is a complete graph where every edge corresponds to every possible valid $ \coma $, by construction $ \scomaset \subset \edges$.
+A candidate solution of a monotone dual-arm rearrangement problem must transfer every object exactly once.
 In terms of the graph, this means that in the subset of edges $ \scomaset $ every vertex appears in only one edge.
@@
 
+\vspace{-0.13in}
 {\lemma [Optimal Matching]
@@
 \ref{eq:transitgraph}), where the vertices comprise of the $ \coma \in \scomaset^*$.
-An edge $ e(\coma_{u\rightarrow v}) $ between any two vertices corresponds to the coordinated \textit{transit} motion between them.
+An edge $ e(\coma_{u\rightarrow v}) $ corresponds to the coordinated \textit{transit} motion between them.
 For instance, as in Fig \ref{fig:edge_matching}(right) for an edge between $ \coma(A,B) $ and $ \coma(C,D) $, $ \arm^1 $ moves from the target pose of object `A' to the starting pose of object `C', and similarly $ \arm^2 $ moves from the target of `B' to the start of `D'.
@@
 The graph is fully connected again to represent all possible transits or moves.
-
-A complete candidate solution to the problem now requires the sequence of~$ \coma $.
-By definition of the edges, the complete solution begins at~$ \startq $ and also ends there.
-This is a complete tour over~$ \tspgraph $, that visits all the vertices i.e., an ordered sequence of vertices $\tour = ( {\startq}, \scoma_\tour, {\startq}  )$.
+A complete candidate solution to the problem now requires the sequence of~$ \coma $, 
+%By definition of the edges, the complete solution begins at~$ \startq $ and also ends there. 
+which is a complete tour over~$ \tspgraph $, that visits all the vertices i.e., an ordered sequence of vertices $\tour = ( {\startq}, \scoma_\tour, {\startq}  )$.
 \vspace{-0.1in}
@@
 This differs from the true optimal $ \scoma^* $, since the second step of finding the optimal transit tour only operates over all possible solutions that include the optimally matched transfers obtained in the first step.
-The insight here is that, even though $ \scoma^+ $ reports a solution to a hierarchical optimization objective, the algorithm operates over a much smaller search space, and operates over sub-problems which are more efficient to solve than the baselines.\\
+The insight here is that, even though $ \scoma^+ $ reports a solution to a hierarchical optimization objective, 
+%the algorithm operates over a much smaller search space, and operates over sub-problems which are more efficient to solve than the baselines.\\
+the search space is much smaller, and the sub-problems more efficient to solve.\\
 

### 2018-10-30 06_integration.tex
Bringing it down to the page limit
Referencing arxiv

@@
 \begin{wrapfigure}{r}{0.6\textwidth}
-  \vspace{-0.1in}
+  \vspace{-0.5 in}
   \begin{minipage}{0.6\textwidth}
@@
 Smoothing does not change the maximum of distances, only improves execution time.
-Indications that the smoothed variants of the synchronous solutions do not provide significant savings in execution time are included in the Appendix for the interested reader.
+Indications that the smoothed variants of the synchronous solutions do not provide significant savings in execution time are included in the Appendix \cite{Shome2018WAFR} for the interested reader.
 

### 2018-10-30 07_cost_bounds.tex
Referencing arxiv

@@
 the single arm 
-solution. This argument can be extended to $k$-arms as well.
+solution. This argument can be extended to $k$-arms as well \cite{Shome2018WAFR}.
 \vspace{-0.08in}
@@
 The cost~(Eq.~\ref{eq:cost_function}) of $\frac{n}{2}$ synchronized transfers ($\coma_i$) includes $\frac{n}{2}c_{pd}$ and $C^{\rm sync}_{sg} \approx (\mathtt{E}(max(l_1,l_2))c_t)\frac{n}{2}$, where $\mathtt{E}(max(l_1,l_2))$ is the expected measure of the max of lengths $l_1$,$l_2$ of two randomly paired transfers.
-Using the \textit{pdf}\cite{ghosh1951random} of lengths of random lines in an unit square and integrating over the setup, results in the value of $\mathtt{E}(max(l_1,l_2))$ to be $0.66$.
+Using the \textit{pdf}\cite{ghosh1951random} of lengths of random lines in an unit square and integrating over the setup\cite{Shome2018WAFR}, results in the value of $\mathtt{E}(max(l_1,l_2))$ to be $0.66$ .
 % (Section \ref{sec:appendix}). 

### 2019-06-03 03_problem.tex
tase initial update

@@
 \begin{wrapfigure}{r}{2.4in}
-    \vspace{-.3in}
+    % \vspace{-.3in}
 	\centering
@@
 	\includegraphics[width=1.115in,trim={10cm 3cm 8cm 12cm},clip]{figures/rearrangement_end}
-    \vspace{-.15in}
+    % \vspace{-.15in}
 	\caption{An example of object rearrangement involving two robotic arms. Initial (left) and final (right) object configuration.}
 	\label{fig:rearrangement}
-    \vspace{-.35in}
+    % \vspace{-.35in}
 \end{wrapfigure}
@@
 
-\vspace{-.1in}
+% \vspace{-.1in}
 {\definition [Optimal Dual-arm Rearrangement] Given arms $\arm^1$, $\arm^2$ and objects $\objectset$ to be moved from initial arrangement $ \ainit \in \Afree$ to target arrangement $ \atarget \in \Afree $, the optimal dual-arm rearrangement problem asks for a dual-arm path $D^* \in \mathcal{D}$, which satisfies the following constraint:
 
-\vspace{-.15in} 
+% \vspace{-.15in} 
 \begin{equation}
-D^* =  (\pi^{*1}, \pi^{*2}) \ |\ \arrangement(\ainit, D^*) = \atarget \textrm{ and } \pi^{*i} \in \cfree^i(\pi^{*j}) \vspace{-.05in}
+% D^* =  (\pi^{*1}, \pi^{*2}) \ |\ \arrangement(\ainit, D^*) = \atarget \textrm{ and } \pi^{*i} \in \cfree^i(\pi^{*j}) \vspace{-.05in}
 \label{eq:dualarm_constraint}
@@
 
-\vspace{-.15in}
+% \vspace{-.15in}
 {\assumption [Monotonicity] There are dual-arm paths $D = (\pi^1,\pi^2)$ that satisfy Eq.
@@
 
-\vspace{-.1in}
+% \vspace{-.1in}
 {\assumption [Synchronicity] Consider dual-arm paths, which can be decomposed into a sequence of simultaneous transfers and moves for both arms:
-\vspace{-.1in}
+% \vspace{-.1in}
 \begin{equation}
-D=\left(T(\pi^1_1,\pi^2_1),M(\pi^1_{1\rightarrow 2},\pi^2_{1\rightarrow 2}), \ldots , M(\pi^1_{\ell-1\rightarrow \ell},\pi^2_{\ell-1\rightarrow \ell}), T(\pi^1_\ell,\pi^2_\ell)\right).\vspace{-.05in}
+D=\left(T(\pi^1_1,\pi^2_1),M(\pi^1_{1\rightarrow 2},\pi^2_{1\rightarrow 2}), \ldots , M(\pi^1_{\ell-1\rightarrow \ell},\pi^2_{\ell-1\rightarrow \ell}), T(\pi^1_\ell,\pi^2_\ell)\right).
+% \vspace{-.05in}
 \label{eq:synchronicity}
@@
 Then, the sequence of object pairs moved during a dual-arm path as in Eq.
-\ref{eq:synchronicity} is: \vspace{-.1in}
+\ref{eq:synchronicity} is:
+% \vspace{-.1in} 
 % $$ \scoma(D) = \left(  \coma_i = (\object_i^1,\object_i^2) \ |\ i,j\in [1,\cdots,\ell], \bigcup_i (\object_i^1 \cup \object_i^2) = \objectset, \object_i^1 \cap \object_j^1 = \object_i^2 \cap \object_j^2 = \emptyset \right).
@@
 $$ \scoma(D) = \left(  \coma_i = (\object_i^1,\object_i^2) \ |\ i,j\in [1\cdots \ell], \bigcup_i (\object_i^1 \cup \object_i^2) = \objectset, \forall k,k'\in[1,2], \object_i^k \neq \object_j^{k'} \right).
-\vspace{-.1in}$$
+$$
 
@@
 
-\vspace{-.1in}
+% \vspace{-.1in}
 {\assumption [Object Non-Interactivity] There are collision-free transfers $T(\coma_i)$ and moves $M(\coma_{i\rightarrow i^{\prime}})$ regardless of the object poses in $\ainit$ and $\atarget$.}
@@
 Then, over the entire dual-arm path $ \D $ define:
-\vspace{-.15in}
+% \vspace{-.15in}
 \begin{equation}
@@
 = \sum_{i=1}^{\ell}   \cost(T(\coma_i))   + \sum_{i=1}^{\ell-1}   \cost(M(\coma_{i\rightarrow i+1})). 
-\vspace{-.1in}
+% \vspace{-.1in}
 \label{eq:cost_function}
@@
 A monotone solution also implies that every object's start and target is reachable by at least one arm.
-To deal with cases where the number of reachable objects is unbalanced between the two arms, a {\tt NO\_ACT} task assignment is introduced and considered in Section 6.
+\cameraready{
+Objects do not need to be in the commonly reachable workspace as long as the problem is monotone and solvable.
+Section~\ref{sec:integration} discusses a {\tt NO\_ACT} task that can deal with unbalanced object assignments between two arms.
+}
 

### 2019-06-03 09_discussion.tex
tase initial update

@@
 Existing efficient solvers for reductions of the dual-arm problem made \algo effective.
-Future work will attempt to explore the $k-$arm case and instances of non-monotone rearrangement.
-The incorporation of manipulation and regrasp reasoning can extend these methods to more cluttered domains.
+\cameraready
+{
+Future work will attempt to explore the $k-$arm case.
+The matching sub-problem ceases to have effective solvers for $k>2$, and heuristics might need to be considered for feasible solutions.
+Regrasp reasoning can extend this work to non-monotone problem instances.
+The incorporation of manipulation and grasp reasoning can apply such solvers to more cluttered environments.
+}
 

### 2019-06-03 10_appendix.tex
tase initial update

@@
 
+\subsection{Discrete Reachability Benchmark}
+In this benchmark, two Kuka arms are placed opposite a target arrangement table.
+The initial poses of the objects are set to be on opposite ends of the arms, as demonstrated in the image.
+The purpose of this study is to see the effects of general divided workspaces where both the initial and target poses are not in the region of common reachability of the arms.
+This is indeed a simpler problem for the coordinated methods, but proves challenging to the naive random split strategy.
+
+\begin{figure}
+	\centering
+	\includegraphics[width=5.3in]{figures/reachability}
+	\includegraphics[width=5.3in]{figures/results/5_kuka_lazy_ms_success.png}
+	\includegraphics[width=5.3in]{figures/results/5_kuka_lazy_ms_cost.png}
+	\includegraphics[width=5.3in]{figures/results/5_kuka_lazy_ms_time.png}
+	\caption{The reachability benchmark}
+	\label{fig:reachability_benchmark}
+%     \vspace{-.3in}
+\end{figure}
+
 %####################################################################################

### 2019-06-03 01_introduction.tex
tase initial update
update

@@
 
-Automation tasks in industrial and service robotics, such as product packing or sorting, often require sets of objects to be arranged in
+\IEEEPARstart{A}{utomation} tasks in industrial and service robotics, such as product packing or sorting, often require sets of objects to be arranged in
 specific poses on a planar surface. Efficient and high-quality
@@
 
-\vspace{-.1in}
+% \vspace{-.1in}
 \begin{lemma}\label{l:k-arm-lower-bound}
@@
 single-arm one.
-\vspace{-.3in}
+% \vspace{-.3in}
 \end{lemma}
@@
 
-\vspace{-.1in}
+% \vspace{-.1in}
 \begin{lemma}\label{l:2-arm-no-worse}
@@
 cannot be worse than an optimal single arm solution.
-\vspace{-.1in}
+% \vspace{-.1in}
 \end{lemma}
@@
 
-\begin{figure}[t]\vspace{-0.15in}
+\begin{figure}[t]
+% \vspace{-0.15in}
 	\centering
-	\includegraphics[width=3in]{figures/two_arms}\vspace{-0.1in}
+	\includegraphics[width=0.48\textwidth]{figures/two_arms}
+% 	\vspace{-0.1in}
 	\caption{Example of dual-arm setups that can utilize
 	algorithms proposed in this work.}
-	\label{fig:two_arms}\vspace{-0.25in}
+	\label{fig:two_arms}
+% 	\vspace{-0.25in}
 \end{figure}

### 2019-06-03 03_problem.tex
update

@@
 
-\begin{wrapfigure}{r}{2.4in}
+\begin{figure}[h]
     % \vspace{-.3in}
 	\centering
-	\includegraphics[width=1.115in,trim={10cm 3cm 8cm 12cm},clip]{figures/rearrangement_start}
-	\includegraphics[width=1.115in,trim={10cm 3cm 8cm 12cm},clip]{figures/rearrangement_end}
+	\includegraphics[width=0.24\textwidth,trim={10cm 3cm 8cm 12cm},clip]{figures/rearrangement_start}
+	\includegraphics[width=0.24\textwidth,trim={10cm 3cm 8cm 12cm},clip]{figures/rearrangement_end}
     % \vspace{-.15in}
@@
     % \vspace{-.35in}
-\end{wrapfigure}
+\end{figure}
 Two robot arms $\arm^1$ and $\arm^2$ can 
@@
 \begin{equation}
-% D^* =  (\pi^{*1}, \pi^{*2}) \ |\ \arrangement(\ainit, D^*) = \atarget \textrm{ and } \pi^{*i} \in \cfree^i(\pi^{*j}) \vspace{-.05in}
+ D^* =  (\pi^{*1}, \pi^{*2}) \ |\ \arrangement(\ainit, D^*) = \atarget \textrm{ and } \pi^{*i} \in \cfree^i(\pi^{*j}) \vspace{-.05in}
 \label{eq:dualarm_constraint}
 \end{equation}
-\noindent and optimizes a cost function: $D^* = \underset{ \forall D \in \mathcal{D}}{ \mathtt{argmin} } \ \cost(D).$}
+ and optimizes a cost function: $D^* = \underset{ \forall D \in \mathcal{D}}{ \mathtt{argmin} } \ \cost(D).$}
 
@@
 % \vspace{-.1in}
-\begin{equation}
-D=\left(T(\pi^1_1,\pi^2_1),M(\pi^1_{1\rightarrow 2},\pi^2_{1\rightarrow 2}), \ldots , M(\pi^1_{\ell-1\rightarrow \ell},\pi^2_{\ell-1\rightarrow \ell}), T(\pi^1_\ell,\pi^2_\ell)\right).
+\begin{align*}
+D=& (T(\pi^1_1,\pi^2_1),M(\pi^1_{1\rightarrow 2},\pi^2_{1\rightarrow 2}), \ldots , M(\pi^1_{\ell-1\rightarrow \ell},\pi^2_{\ell-1\rightarrow \ell}),\\
+& T(\pi^1_\ell,\pi^2_\ell)).\numberthis
 % \vspace{-.05in}
 \label{eq:synchronicity}
-\end{equation}}
+\end{align*}}
 \noindent For simplicity, Eq.~\ref{eq:synchronicity} does not include an initial move from $q^k_{\rm safe} \in \cfree^k$ and a final move back to $q^k_{\rm safe}$.
@@
 \vspace{-.15in}$$
-$$ \scoma(D) = \left(  \coma_i = (\object_i^1,\object_i^2) \ |\ i,j\in [1\cdots \ell], \bigcup_i (\object_i^1 \cup \object_i^2) = \objectset, \forall k,k'\in[1,2], \object_i^k \neq \object_j^{k'} \right).
-$$
+\begin{align*}
+	\scoma(D) = &\Bigg(  \coma_i = (\object_i^1,\object_i^2) \ |\ i,j\in [1\cdots \ell],\\& \bigcup_i (\object_i^1 \cup \object_i^2) = \objectset, \forall k,k'\in[1,2], \object_i^k \neq \object_j^{k'} \Bigg).&\numberthis
+	\label{eq:scomaD}
+\end{align*}
 

### 2019-06-03 04_baseline.tex
Bringing it down to the page limit
tase initial update
update

@@
 
-\vspace{-0.25in}
-\begin{equation*}
-{\permu[n]{2}} + {\permu[n]{2}}\times{\permu[n-2]{2}} + ... + {\permu[n]{2}}\times{\permu[n-2]{2}}\times{\permu[n-4]{2}}...\times{\permu[2]{2}} =\sum_{L=1}^{n/2} {\ \prod_{k=0}^{2L-1}{(n-k)}},
-\vspace{-0.15in}
-\end{equation*}
+% \vspace{-0.25in}
+\begin{align*}
+{\permu[n]{2}} + {\permu[n]{2}}\times{\permu[n-2]{2}} + ...
++ {\permu[n]{2}}\times{\permu[n-2]{2}}\times{\permu[n-4]{2}}...&\times{\permu[2]{2}} =\\\sum_{L=1}^{n/2} {\ \prod_{k=0}^{2L-1}{(n-k)}}&\numberthis
+% \vspace{-0.15in}
+\end{align*}
 where $\permu[n]{k}$ is the $k$-permutations of $n$.
 
-\begin{wrapfigure}{r}{2.4in}
-    \vspace{-.5in}
+\begin{figure}[h]
+    % \vspace{-.5in}
 	\centering
-	\includegraphics[width=1.8in]{figures/dual_backtracking.PNG}
-    \vspace{-.15in}
+	\includegraphics[width=0.48\textwidth]{figures/dual_backtracking.PNG}
+    % \vspace{-.15in}
 	\caption{Search tree for 4 objects. 
@@
 	\label{fig:backtracking}
-    \vspace{-.3in}
-\end{wrapfigure}
+    % \vspace{-.3in}
+\end{figure}
 Motion plans can be reused, however, and repeated occurrences of $T(\coma_i)$ and $M(\coma_{i\rightarrow i^{\prime}})$ should be counted only once for a total of: 
@@
 
-\vspace{-0.35in}
-\begin{equation}
-\textrm{\# of Transfers} + \textrm{\# of Moves} =  {\permu[n]{2}} +   \Big{(}({{\permu[n]{2}}\times\permu[n-2]{2}}) + (2\times{\permu[n]{2}})\Big{)}
+% \vspace{-0.25in}
+\begin{align*}
+\textrm{\# of Transfers} + \textrm{\# of Moves} =&\\  {\permu[n]{2}} +   \Big{(}({{\permu[n]{2}}\times\permu[n-2]{2}}) + (2\times{\permu[n]{2}})&\Big{)}\numberthis
 \label{eq:mpcount}
-\vspace{-0.2in}
-\end{equation}
+% \vspace{-0.15in}
+\end{align*}
 
@@
 
-\vspace{-.3in}
+% \vspace{-.25in}
 \begin{align*}
-\hspace{0.5in} \hat{V} = \{ v = \coma_v = (\object_v^1,\object_v^2)\ | \  \forall\ \object_v^1,\object_v^2 \in \objectset, \object_v^1 \neq \object_v^2 \} \cup \{S\}\\
-\hat{E} = \{  e(u,v)\ | \ \forall\ u,v\in \hat{V} \textrm{ so that } u\neq v,\ \object_v^k \neq \object_u^{\ell}\ \forall\ k, \ell \in [1,2] \}\\
-\cup\ \{e(\startq,v)\ \forall\ v\in\hat{V}\setminus \startq\} \cup \{e(v,\startq)\ \forall\ v\in\hat{V}\setminus \startq\}\\
-cost_{e(u,v)} = \cost(u) + \cost(u,v) =\cost(T(\coma_u)) + \cost(M(\coma_{u\rightarrow v}))
+\hspace{0.5in} \hat{V} =& \{ v = \coma_v = (\object_v^1,\object_v^2)\ |\\& \  \forall\ \object_v^1,\object_v^2 \in \objectset, \object_v^1 \neq \object_v^2 \} \cup \{S\}\\
+\hat{E} =& \{  e(u,v)\ | \ \forall\ u,v\in \hat{V} \textrm{ so that } u\neq v,\ \\& 
+\object_v^k \neq \object_u^{\ell}\ \forall\ k, \ell \in [1,2] \}
+\cup\ \\&
+ \{e(\startq,v)\ \forall\ v\in\hat{V}\setminus \startq\} \cup \\& \{e(v,\startq)\ \forall\ v\in\hat{V}\setminus \startq\}\\
+cost_{e(u,v)} =& \cost(u) + \cost(u,v)\\ =&\cost(T(\coma_u)) + \cost(M(\coma_{u\rightarrow v}))
 \end{align*}
 
-\vspace{-.2in}
+% \vspace{-.15in}
 Let $\cost(\startq) = 0$.
@@
 
-\vspace{-.25in}
-\noindent\begin{minipage}{.5\textwidth}
+% \vspace{-.2in}
+\noindent\begin{minipage}{.48\textwidth}
 \begin{align*}
@@
 \end{minipage}
-\noindent\begin{minipage}{.5\textwidth}
+\noindent\begin{minipage}{.48\textwidth}
 \begin{align*}

### 2019-06-03 05_approximation.tex
update

@@
 going from the goals to starts $C_{gs}$. The single arm cost is  
-\vspace{-0.1in}
+%\vspace{-0.1in}
 \begin{equation}
@@
 C_{\rm single} = nc_{pd} + C_{sg} + C_{gs}.
-\vspace{-0.1in}
+%\vspace{-0.1in}
 \end{equation}
@@
 
-{\centerline
-{
-$\Theta(c_t\sqrt{n\ln n}) = C_{gs}^M < C_{gs} < C_{gs}^M + c_t\ln n 
-= \Theta(c_t\sqrt{n\ln n}) + c_t\ln n$
-}
-}
+\begin{align*}
+\Theta(c_t\sqrt{n\ln n}) = C_{gs}^M < C_{gs} < C_{gs}^M + c_t\ln n 
+=\\ \Theta(c_t\sqrt{n\ln n}) + c_t\ln n
+\end{align*}
 
@@
 % we have 
-\vspace{-0.1in}
-\begin{equation}\label{eq:single-cost-simple}
-C_{\rm single} \approx nc_{pd} + (0.52n + 0.44\sqrt{n\ln n})c_t \approx (c_{pd} + 0.52c_t)n
+%\vspace{-0.1in}
+\begin{align*}\label{eq:single-cost-simple}
+C_{\rm single} &\approx nc_{pd} + (0.52n + 0.44\sqrt{n\ln n})c_t \\&\approx (c_{pd} + 0.52c_t)n \numberthis
 % \vspace{-0.1in}
-\end{equation}
+\end{align*}
 noting that the $0.44\sqrt{n\ln n}c_t$ term may also be ignored for large $n$. The cost of dual arm solutions will be analyzed in Section \ref{sec:cost_bounds}.
@@
 
-\begin{minipage}{0.48\textwidth}
-  \begin{align}
-  \label{eq:transfergraph}
-  \begin{split}
+%\begin{minipage}{0.48\textwidth}
+%  \begin{align}
+%  \label{eq:transfergraph}
+%  \begin{split}
+%  \graph(\nodes, \edges)\\
+%  \nodes = \{ \node=\object, \forall \object \in \objectset \}\\
+%  \edges = \{ \edge(u, v): \coma = (u,v), \forall u,v\in\nodes \}\\
+%  \cost(\edge(u,v)) = \cost(T(\coma=(u,v)))
+%  \end{split}
+%  \end{align}
+%\end{minipage}
+%\begin{minipage}{0.48\textwidth}
+%  \begin{align}
+%  \label{eq:transitgraph}
+%  \begin{split}
+%  \tspgraph(\tspnodes, \tspedges)\\
+%  \tspnodes = \{ \node=\coma, \forall \coma \in \scomaset^* \} \cup \{\coma_S\} \\
+%  \tspedges = \{ \edge(u, v): \coma_{u\rightarrow v}, \forall u,v\in\tspnodes \}\\
+%  \cost(\edge(u,v)) = \cost(M(\coma_{u\rightarrow v}))
+%  \end{split}
+%  \end{align}
+%\end{minipage}
+
+\begin{align*}
 	\graph(\nodes, \edges)\\
@@
 	\edges = \{ \edge(u, v): \coma = (u,v), \forall u,v\in\nodes \}\\
-  \cost(\edge(u,v)) = \cost(T(\coma=(u,v)))
-  \end{split}
-  \end{align}
-\end{minipage}
-\begin{minipage}{0.48\textwidth}
-  \begin{align}
-  \label{eq:transitgraph}
-  \begin{split}
+	\cost(\edge(u,v)) = \cost(T(\coma=(u,v))) \numberthis\label{eq:transfergraph}\\ \\
 	\tspgraph(\tspnodes, \tspedges)\\
@@
 	\tspedges = \{ \edge(u, v): \coma_{u\rightarrow v}, \forall u,v\in\tspnodes \}\\
-  \cost(\edge(u,v)) = \cost(M(\coma_{u\rightarrow v}))
-  \end{split}
-  \end{align}
-\end{minipage}
-\vspace{0.05in}
+	\cost(\edge(u,v)) = \cost(M(\coma_{u\rightarrow v})) \numberthis\label{eq:transitgraph}
+\end{align*}
+%\vspace{0.05in}
 
@@
 
-\begin{wrapfigure}{r}{2.5in}
-\vspace{-0.15in}
+\begin{figure*}
+%\vspace{-0.15in}
 % \begin{figure}[H]
@@
 % 		\includegraphics[width=2.5in]{figures/mapp}
-		\includegraphics[width=2.5in]{figures/mapp_labels}
-	\end{center}\vspace{-0.2in}
+		\includegraphics[width=0.7\textwidth]{figures/mapp_labels}
+	\end{center}
+%\vspace{-0.2in}
 	\caption{(left) A dual-arm rearrangement problem.
 (middle) The same problem as minimum weight edge matching on a fully connected directed graph of \textit{transfers}.
-(right) The ordering of the object-arm assignments from an optimal tour over a \textit{transit} graph.}\vspace{-0.2in}
+(right) The ordering of the object-arm assignments from an optimal tour over a \textit{transit} graph.}
+%	\vspace{-0.2in}
 	\label{fig:edge_matching}
 % \end{figure}
-\vspace{-0.1in}
-\end{wrapfigure}
+%\vspace{-0.1in}
+\end{figure*}
 
@@
 
-\vspace{-0.13in}
+%\vspace{-0.13in}
 {\lemma [Perfect Matching]
@@
 
-\vspace{-0.13in}
+%\vspace{-0.13in}
 {\lemma [Optimal Matching]
@@
 which is a complete tour over~$ \tspgraph $, that visits all the vertices i.e., an ordered sequence of vertices $\tour = ( {\startq}, \scoma_\tour, {\startq}  )$.
-\vspace{-0.1in}
+%\vspace{-0.1in}
 {
@@
 An optimal tour on $ \tspgraph $ minimizes the transit costs over the all possible candidate solutions in  $ \mathbb{P}^{\scomaset^*} $.
-\vspace{-0.1in}
+%\vspace{-0.1in}
 \begin{equation}
 \scoma^+ = \underset{ \scoma \in  \mathbb{P}^{\scomaset^*}   }{ \mathtt{argmin} } \ \sum_{e(u,v)\in\tour}\cost({M}( \coma_{u\rightarrow v} ))  )
-\vspace{-0.05in}
+%\vspace{-0.05in}
 \end{equation}
@@
 
-\vspace{-0.1in}
+%\vspace{-0.1in}
 
@@
 
-\begin{wrapfigure}{r}{0.6\textwidth}\vspace{-0.3in}
-  \begin{minipage}{0.6\textwidth}
-  \vspace{0pt} 
-    \begin{algorithm}[H]
+%\begin{wrapfigure}{r}{0.6\textwidth}\vspace{-0.3in}
+%  \begin{minipage}{0.6\textwidth}
+%  \vspace{0pt} 
+    \begin{algorithm}[t]
     \caption{{\tt \algo}$ (\objectset, \startq, \ainit, \atarget) $}
@@
     \end{algorithm}
-  \end{minipage}
-  \vspace{-0.3in}
-\end{wrapfigure}
+%  \end{minipage}
+%  \vspace{-0.3in}
+%\end{wrapfigure}
 
@@
 % \kiril{Consider completing the calculation.}
-\vspace{-0.1in}
-$$
-\frac{\textrm{Baseline}\ \#}{{\algo}\ \#} = 
+%\vspace{-0.1in}
+
+\begin{align*}
+\frac{\textrm{Baseline}\ \#}{{\algo}\ \#} &= 
 \frac{  {\permu[n]{2}} +   \Big{(}{{\permu[n]{2}}\times\permu[n-2]{2}}\Big{)} + \Big{(}2\times{\permu[n]{2}}\Big{)}   }
-{\permu[n]{2} + \permu[(\frac{n}{2} + 1)]{2}} =
-\frac{4(n-1)((n-5)n+9)}{5n-2}
-$$\vspace{-0.1in}
+{\permu[n]{2} + \permu[(\frac{n}{2} + 1)]{2}}\\ &=
+\frac{4(n-1)((n-5)n+9)}{5n-2}\numberthis
+\end{align*}
+
+%\vspace{-0.1in}
 

### 2019-06-03 08_evaluation.tex
update

@@
 
-\begin{wrapfigure}{r}{2.2in}
-    \vspace{-.6in}
+\begin{figure*}[b]
+%    \vspace{-.6in}
 	\centering
-		\includegraphics[width=1.1in,trim={1cm 9cm 1cm 5cm},clip]{figures/simple_picker_benchmark}
-		\includegraphics[width=1.05in]{figures/kuka_benchmark2}
-		\vspace{-.3in}
+		\includegraphics[width=0.49\textwidth,trim={1cm 9cm 1cm 5cm},clip]{figures/simple_picker_benchmark}
+		\includegraphics[width=0.47\textwidth]{figures/kuka_benchmark2}
+%		\vspace{-.3in}
 		\caption{\textit{Picker} and \textit{Manipulator} trials.}
 		\label{fig:benchmarks}
-    \vspace{-.3in}
-\end{wrapfigure}
+%    \vspace{-.3in}
+\end{figure*}
 This section describes the experiments performed to evaluate the algorithms in two  domains shown in Fig \ref{fig:benchmarks}: a) simple picker and b) general manipulators.
@@
 
-\begin{figure}[h]
-\vspace{-0.2in}
+\begin{figure*}[h!]
+%\vspace{-0.2in}
 	\centering
@@
 %	\includegraphics[width=2.1in]{figures/disk_more_timing}
-	\includegraphics[width=3.5in]{figures/results/labels}
-	\includegraphics[width=2in]{figures/results/4_sp_ms_success}
-	\includegraphics[width=2in]{figures/results/3_sp_lazy_ms_success}
-	\includegraphics[width=2in]{figures/results/4_sp_ms_cost}
-	\includegraphics[width=2in]{figures/results/3_sp_lazy_ms_cost}
-	\includegraphics[width=2in]{figures/results/4_sp_ms_time}
-	\includegraphics[width=2in]{figures/results/3_sp_lazy_ms_time}
-	\vspace{-0.15in}
+
+%\includegraphics[width=0.48\textwidth,trim={1cm 9cm 1cm 5cm},clip]{figures/simple_picker_benchmark}\\
+	\includegraphics[width=0.6\textwidth]{figures/results/labels}
+	\includegraphics[width=0.48\textwidth]{figures/results/4_sp_ms_success}
+	\includegraphics[width=0.48\textwidth]{figures/results/3_sp_lazy_ms_success}
+	\includegraphics[width=0.48\textwidth]{figures/results/4_sp_ms_cost}
+	\includegraphics[width=0.48\textwidth]{figures/results/3_sp_lazy_ms_cost}
+	\includegraphics[width=0.48\textwidth]{figures/results/4_sp_ms_time}
+	\includegraphics[width=0.48\textwidth]{figures/results/3_sp_lazy_ms_time}
+%	\vspace{-0.15in}
 	\caption{\textit{Simple Picker} results with success\textit{(top)}, solution costs\textit{(middle)}, and computation\textit{(bottom)} reported for single-shot\textit{(left)} and lazy\textit{(right)} versions of the methods}
-    \vspace{-0.3in}
+%    \vspace{-0.3in}
 	\label{fig:disk}
-\end{figure}
+\end{figure*}
 
-\begin{figure}[h]
-\vspace{-0.2in}
+\begin{figure*}[h!]
+%\vspace{-0.2in}
 	\centering
-	\includegraphics[width=3.5in]{figures/results/labels}
-	\includegraphics[width=2in]{figures/results/2_kuka_ms_success}
-	\includegraphics[width=2in]{figures/results/1_kuka_lazy_ms_success}
-	\includegraphics[width=2in]{figures/results/2_kuka_ms_cost}
-	\includegraphics[width=2in]{figures/results/1_kuka_lazy_ms_cost}
-	\includegraphics[width=2in]{figures/results/2_kuka_ms_time}
-	\includegraphics[width=2in]{figures/results/1_kuka_lazy_ms_time}
-	\vspace{-0.15in}
+%	\includegraphics[width=0.48\textwidth]{figures/kuka_benchmark2}
+	\includegraphics[width=0.6\textwidth]{figures/results/labels}
+	\includegraphics[width=0.48\textwidth]{figures/results/2_kuka_ms_success}
+	\includegraphics[width=0.48\textwidth]{figures/results/1_kuka_lazy_ms_success}
+	\includegraphics[width=0.48\textwidth]{figures/results/2_kuka_ms_cost}
+	\includegraphics[width=0.48\textwidth]{figures/results/1_kuka_lazy_ms_cost}
+	\includegraphics[width=0.48\textwidth]{figures/results/2_kuka_ms_time}
+	\includegraphics[width=0.48\textwidth]{figures/results/1_kuka_lazy_ms_time}
+%	\vspace{-0.15in}
     \caption{\textit{\kuka}results with success\textit{(top)}, solution costs\textit{(middle)}, and computation\textit{(bottom)} reported for single-shot\textit{(left)} and lazy\textit{(right)} versions of the methods}
-    \vspace{-0.3in}
+%    \vspace{-0.3in}
 	\label{fig:kuka}
-\end{figure}
+\end{figure*}

### 2019-06-03 10_appendix.tex
update

@@
 \vspace{-0.1in}
-\begin{equation}\label{eq:kmakespan-ratio}
-\frac{C_{\rm k{\text-}arm}^t}{C_{\rm single}} \approx 
+\begin{align*}\label{eq:kmakespan-ratio}
+\frac{C_{\rm k{\text-}arm}^t}{C_{\rm single}} &\approx 
 \frac{(c_{pd} + 0.52c_t)\frac{n}{k} + nf(k,r)c_t}{(c_{pd} + 0.52c_t)n}
-= \frac{1}{k} + \frac{f(k,r)c_t}{c_{pd} + 0.52c_t}\;.
+\\&= \frac{1}{k} + \frac{f(k,r)c_t}{c_{pd} + 0.52c_t}\;.\numberthis
 % \vspace{-0.1in}
-\end{equation}
+\end{align*}
 
@@
 In the unit square model, $a=b=1$. Substituting the values, the \textit{pdf} becomes
-\begin{align}
+\begin{align*}
 p(l)&= 2\pi l - 8\pi l^2 + 2l^3, \ \ l\in[0,1]\\
-p(l)&= 4l\sininv(\frac{1}{l}) - 4l\cosinv(\frac{1}{l}) + 8l\sqrt[]{(l^2-1)} -2l^3 -4l, \ \ l\in[1,\sqrt[]{2}]
-\end{align}
+p(l)&= 4l\sininv(\frac{1}{l}) - 4l\cosinv(\frac{1}{l}) + 8l\sqrt[]{(l^2-1)} -2l^3 -4l,\\ &\ l\in[1,\sqrt[]{2}]
+\end{align*}
 
@@
 This is estimated using the \textit{pdf} obtained. 
-\begin{equation}
-\mathtt{E}(max(l_1,l_2)) = \int_0^{\sqrt[]{2}} \int_0^{\sqrt[]{2}} max(l_1,l_2)p(l_1)p(l_2) dl_2 dl_1 \approx 0.663
-\end{equation}
+\begin{align*}
+\mathtt{E}(max(l_1,l_2)) &= \int_0^{\sqrt[]{2}} \int_0^{\sqrt[]{2}} max(l_1,l_2)p(l_1)p(l_2) dl_2 dl_1\\&\approx 0.663
+\end{align*}
 The result is calculated by taking into account the combination of different ranges of $p(l)$ and $max(l_1,l_2)$.
 \commentadd{
-\begin{wrapfigure}{r}{1.4in}
+\begin{figure}[h]
 	\centering
-	\vspace{-0.3in}
-    \includegraphics[width=1.4in]{figures/monte_carlo}
+%	\vspace{-0.3in}
+    \includegraphics[width=0.35\textwidth]{figures/monte_carlo}
 	\caption{Empirical cost ratio versus the estimate}
-  	\label{fig:bounds}
-\end{wrapfigure}
+  	\label{fig:mcbounds}
+\end{figure}
 
@@
 When $c_{pd}=0$ and $r=0$, the ratio of $\frac{C_{dual}^{sync}}{C_{single}}$ evaluates to $0.636$.
-Fig \ref{fig:bounds} verifies empirically that the ratio converges to the expected value as the number of transfers increases.
+Fig \ref{fig:mcbounds} verifies empirically that the ratio converges to the expected value as the number of transfers increases.
 This indicates the asymptotic speedup of a synchronized dual arm solution for a makespan or maximum of distances cost metric.
@@
 % \vspace{-0.2in}
-\begin{figure}
+\begin{figure}[h]
 	\centering	
-	\includegraphics[width=2.3in]{figures/results/sp_smoothing}
-	\includegraphics[width=2.3in]{figures/results/kuka_smoothing}
+	\includegraphics[width=0.48\textwidth]{figures/results/labels}
+	\includegraphics[width=0.48\textwidth]{figures/results/sp_smoothing}
+	\includegraphics[width=0.48\textwidth]{figures/results/kuka_smoothing}
 	\caption{Smoothed solution improvement as a percentage of the original synchronized solution duration, and the time taken to smooth solutions obtained from \algo in seconds.}
@@
 
-\begin{figure}
+\begin{figure}[h]
 	\centering
-	\includegraphics[width=5.3in]{figures/reachability}
-	\includegraphics[width=5.3in]{figures/results/5_kuka_lazy_ms_success.png}
-	\includegraphics[width=5.3in]{figures/results/5_kuka_lazy_ms_cost.png}
-	\includegraphics[width=5.3in]{figures/results/5_kuka_lazy_ms_time.png}
+	\includegraphics[width=0.48\textwidth]{figures/reachability}
+	\includegraphics[width=0.48\textwidth]{figures/results/labels}
+	\includegraphics[width=0.48\textwidth]{figures/results/5_kuka_lazy_ms_success.png}
+	\includegraphics[width=0.48\textwidth]{figures/results/5_kuka_lazy_ms_cost.png}
+	\includegraphics[width=0.48\textwidth]{figures/results/5_kuka_lazy_ms_time.png}
 	\caption{The reachability benchmark}

### 2019-06-03 01_introduction.tex
updates

@@
 The lazy evaluation strategy significantly improves computation costs for both the optimal and proposed methods.
+
+\tase{
+The current archival version is an extension of previous work and several additions have been made to the draft to provide a more holistic inspection of the problem, chiefly:
+\begin{enumerate}
+	\item An additional benchmark has been added to demonstrate the efficacy of the proposed approach in problem domains where all the object positions do not lie in the shared workspace.
+	\item It has been argued that smoothing can be used to alleviate the sychronization assumption.
+Data from the effects of smoothing the solutions in the experiments have been reported and show that the minor improvements highlight that in practice the synchronization assumption is not tragic.
+	\item A k-arm extension of the asymptotic cost bound in the asynchronous case has been included.
+	\item The proof for the asymptotic cost bound estimate for 2-arms under the synchronization assumption has been expanded, and Monte-Carlo trials have been reported in a simplified setup to validate the analysis model.
+\end{enumerate}
+}
 %The computational costs of both the optimal

### 2019-06-03 04_baseline.tex
updates

@@
 
-\noindent\textbf{Exhaustive Search}: The exhaustive search approach shown in Fig.
+\subsection{Exhaustive Search} The exhaustive search approach shown in Fig.
 \ref{fig:backtracking} is a brute force expansion of all possible sequences of object pairs $ \scoma $.
@@
 
-\noindent\textbf{MILP Formulation}:
+\subsection{MILP Formulation}
+
 Mixed Integer Linear Programming (\milp) formulations can utilize highly optimized solvers \cite{gurobi}.
@@
 \sum_{e\in\delta_{\rm out}(v)} x_e \leq 1& \ \ \forall v\in \hat{V} \tag*{[D]}\\
-\sum_{e\in\delta_{\rm in}(v)}x_e = \sum_{e\in\delta_{\rm out}(v)}x_e& \ \ \forall v\in \hat{V} \tag*{[E]}\\
 \end{align*}
@@
 \begin{align*}
+\sum_{e\in\delta_{\rm in}(v)}x_e = \sum_{e\in\delta_{\rm out}(v)}x_e& \ \ \forall v\in \hat{V} \tag*{[E]}\\
 \sum_{e\in\delta_{\rm in}(\startq)} x_e = 1& \tag*{[F]}\\

### 2019-06-03 05_approximation.tex
updates

@@
 
-\noindent\textbf{Importance of Transfers}: In order to draw some insight, consider again the tabletop setup with a general cost measure of $c_t$ per unit distance.
+\subsection{Importance of Transfers} In order to draw some insight, consider again the tabletop setup with a general cost measure of $c_t$ per unit distance.
 Lemma~\ref{l:k-arm-lower-bound} suggests that under certain conditions, there 
@@
 
-\noindent\textbf{Foundations:} Consider a complete weighted directed graph $\graph(\nodes,\edges)$ (Eq.~\ref{eq:transfergraph}), where $\node \in \nodes$ corresponds to a single object $ \object $.
+\subsection{Foundations} Consider a complete weighted directed graph $\graph(\nodes,\edges)$ (Eq.~\ref{eq:transfergraph}), where $\node \in \nodes$ corresponds to a single object $ \object $.
 Each directed edge, $\edge=(\object_i,\object_j) \in \edges$ is an ordered pair of objects $ \object_i $ and $\object_j $, where the order determines the assignment of an object to an arm $ \arm^1 $ or $ \arm^2 $.
@@
 
-\noindent\textbf{Algorithm}: This section describes the algorithm {\tt {Tour\_Over\_Matching}} (\algo) outlined in the previous section. The steps correspond to Algo \ref{algo:tom}. 
+\subsection{Algorithm : Tour-Over-Matching} 
+This section describes the algorithm  (\algo) outlined in the previous section. The steps correspond to Algo \ref{algo:tom}. 
 % The algorithm takes as input the set of objects $ \objectset $ and the start(and end) configuration $ \startq $ of the arms.

### 2019-06-03 07_cost_bounds.tex
update
updates

@@
 
+\begin{theorem}
+	\textit{For rearranging objects with non-overlapping starts and goals that are
+	uniformly distributed in a unit square,  a $2$-arm solution can have an 
+	asymptotic improvement of $\frac{1}{2}$ over the single arm solution. }
+	\label{thm:karm}
+\end{theorem}
+
+\textit{Proof: }
 From the initial $2$-arm solution, we construct an {\em asynchronous} $2$-arm 
@@
 The cost ratio is
-\vspace{-0.1in}
-\begin{equation}\label{eq:makespan-ratio}
-\frac{C_{\rm dual}^t}{C_{\rm single}} \approx 
+%\vspace{-0.1in}
+\begin{align*}\label{eq:makespan-ratio}
+\frac{C_{\rm dual}^t}{C_{\rm single}} &\approx 
 \frac{(c_{pd} + 0.52c_t)\frac{n}{2} + 4n\pi rc_t}{(c_{pd} + 0.52c_t)n}
-= \frac{1}{2} + \frac{4\pi rc_t}{c_{pd} + 0.52c_t}\;.
+\\&= \frac{1}{2} + \frac{4\pi rc_t}{c_{pd} + 0.52c_t}\;.\numberthis
 % \vspace{-0.1in}
-\end{equation}
+\end{align*}
 
@@
  \begin{wrapfigure}{r}{1.4in}
-  \vspace{-.45in}
+%  \vspace{-.45in}
 	\centering
     \includegraphics[width=1.4in]{figures/monte_carlo}
-    \vspace{-.4in}
+%    \vspace{-.4in}
 	\caption{Empirical cost ratio versus the estimate}
   	\label{fig:bounds}
-    \vspace{-.4in}
+%    \vspace{-.4in}
 \end{wrapfigure}
@@
 the single arm 
-solution. This argument can be extended to $k$-arms as well \cite{Shome2018WAFR}.
-\vspace{-0.08in}
+solution. $ \qed $
+
+%This argument can be extended to $k$-arms as well \cite{Shome2018WAFR}.
+
+%\vspace{-0.08in}
 \commentadd{
+%\begin{theorem}
+%For rearranging objects with non-overlapping starts and goals that are
+%uniformly distributed in a unit square,  a $2$-arm solution can have an 
+%asymptotic improvement of $\frac{1}{2}$ over the single arm solution. 
+%\label{thm:karm}
+%\end{theorem}
+}
+
+\tase{
 \begin{theorem}
-For rearranging objects with non-overlapping starts and goals that are
-uniformly distributed in a unit square,  a $2$-arm solution can have an 
-asymptotic improvement of $\frac{1}{2}$ over the single arm solution. 
-\label{thm:karm}
+	\textit{For rearranging objects with non-overlapping starts and goals that are
+	uniformly distributed in a unit square,  a $k$-arm solution can have an 
+	asymptotic improvement of $\frac{1}{k}$ over the single arm solution. }
 \end{theorem}
+
+\textit{Proof:}	
+%\subsection{Expected k-arm cost bounds in a planar disk manipulator model}
+\commentadd{The arguments made in Theorem \ref{thm:karm} can be extended to $k$ disc arms.
+	In the planar unit-square setting, with $k$ arms, there are $\frac{n}{k}$ objects 
+	for each arm to work with. Consider the transfers and transits of a set of $k$ 
+	objects, one for each arm. By \cite{ChiHanYu2018WAFR}, the arbitrary rearrangement of $k$ discs 
+	can be achieved in a bounded region with a perimeter of $O(kr)$. 
+	Clearly, the per robot additional (makespan or distance) cost is bounded by some 
+	function $f(k, r)c_t$, which goes to zero as $r$ goes to zero. Adding up all the potential 
+	extra cost,  a $k$-arm solution has a cumulative cost
+
+	{\centerline
+		{
+			$C_{\rm k{\text-}arm} = C_{\rm single} + nf(k,r)c_t \approx (c_{pd} + 0.52c_t + f(k,r)c_t)n\;.$
 		}
-The synchronization assumption changes the expected cost of the solution.
+	}
+
+	\noindent For fixed $k$ and small $r$, $C_{\rm k{\text-}arm}$ is almost the same as $C_{\rm single}$.
+	%, $c_t$ is a distance (e.g., energy) cost. 
+	Upon considering the maximum of the two arc lengths or makespan,
+	the $k$-arm cost becomes $C_{\rm k{\text-}arm}^t \approx (c_{pd} + 0.52c_t)\frac{n}{k} + nf(k,r)c_t$.
+
+	The cost ratio is
+	\vspace{-0.1in}
+	\begin{align*}\label{eq:kmakespan-ratio}
+	\frac{C_{\rm k{\text-}arm}^t}{C_{\rm single}} &\approx 
+	\frac{(c_{pd} + 0.52c_t)\frac{n}{k} + nf(k,r)c_t}{(c_{pd} + 0.52c_t)n}
+	\\&= \frac{1}{k} + \frac{f(k,r)c_t}{c_{pd} + 0.52c_t}\;.\numberthis
+	% \vspace{-0.1in}
+	\end{align*}
+
+	When $r$ is small or when $\frac{c_t}{c_{pd}}$ is small, the $k$-arm 
+	solution is roughly $\frac{1}{k}$ as costly as the single arm solution. On 
+	the other hand, in this model a $k$-arm solution does not do better than $\frac{1}{k}$ of 
+	the single arm. \qed
+
+%	\begin{theorem}
+%		For rearranging objects with non-overlapping starts and goals that are
+%		uniformly distributed in a unit square,  a $k$-arm solution can have an 
+%		asymptotic improvement of $\frac{1}{k}$ over the single arm solution. 
+%	\end{theorem}
+}
+% \rahul{Need to verify this line of reasoning}
+
+}
+
+\begin{theorem}
+	\textit{For rearranging objects with non-overlapping starts and goals that are 
+	uniformly distributed in a unit square,  a randomized $2$-arm \textit{synchronized} solution can have an 
+	asymptotic improvement of $\frac{1}{2}$ over the single arm solution if $\frac{c_t}{c_{pd}}$ is small, and a improvement $\approx 0.64$ when both $c_{pd}$ and $r$ are small. }
+\end{theorem}
+
+\textit{Proof:} The synchronization assumption changes the expected cost of the solution.
 The random partitioning of the $n$ objects into two sets of $\frac{n}{2}$ object with a random ordering of the objects yields $\frac{n}{2}$ pairs of objects transfers, which dominate the total cost for large $n$.
@@
 % (Section \ref{sec:appendix}).
+
+\tase{
+\begin{lemma}
+	Expected measure of the maximum of lengths of two random lines on an unit square is $ 0.66 $.
+\end{lemma}
+
+\textit{Proof:} Prior work \cite{ghosh1951random} defines the \textit{probability distribution function (pdf)} of lengths($l$) of randomly sampled lines in a rectangle.
+% of sides $a,b, \ \ a\geq b$.
+% as 
+%\begin{align*}
+%p(l) &= (\frac{4l}{a^2b^2})\phi(l)\\
+%\phi(l)&= \frac{1}{2}\pi a b - a l - b l + \frac{1}{2} l^2, \ \ l\in[0,b]\\
+%\phi(l)&= ab \sininv(\frac{b}{l}) + a. \sqrt[]{(l^2-b^2)} - al - \frac{1}{2}b^2, \ \ l\in[b,a]\\
+%\phi(l)&= ab\{\sininv(\frac{b}{l})-\cosinv(\frac{a}{l})\} + a\sqrt[]{(l^2-b^2)} + b\sqrt[]{(l^2-a^2)} \\
+%&- \frac{1}{2}(l^2+a^2+b^2),\ \ l\in[a,\sqrt[]{(a^2+b^2)}]
+%\end{align*}
+
+%In the unit square model, $a=b=1$. Substituting the values, the \textit{pdf} becomes
+In the unit square model, substituting the values for the dimensions of the sides of the rectangle with $1$, the \textit{pdf} can be simplified as follows.
+\begin{align*}
+p(l)&= 2\pi l - 8\pi l^2 + 2l^3, \ \ l\in[0,1]\\
+p(l)&= 4l\sininv(\frac{1}{l}) - 4l\cosinv(\frac{1}{l}) + 8l\sqrt[]{(l^2-1)} -2l^3 -4l,\\ &\ l\in[1,\sqrt[]{2}]
+\end{align*}
+
+Assuming two random sets of lines, representing transfers in a random split of objects between two arms, we need the expected value of the maximum of these pairwise lengths ie., $\mathtt{E}(max(l_1,l_2)), \ \ l_1,l_2\ i.i.d, \ \ l_1 \sim p, l_2 \sim p$.
+This is estimated using the \textit{pdf} obtained. 
+\begin{align*}
+\mathtt{E}(max(l_1,l_2)) &= \int_0^{\sqrt[]{2}} \int_0^{\sqrt[]{2}} max(l_1,l_2)p(l_1)p(l_2) dl_2 dl_1\\&\approx 0.663
+\end{align*}
+The result is calculated by taking into account the combination of different ranges of $p(l)$ and $max(l_1,l_2)$.
+\commentadd{
+%	\begin{figure}[h]
+%		\centering
+%		%	\vspace{-0.3in}
+%		\includegraphics[width=0.35\textwidth]{figures/monte_carlo}
+%		\caption{Empirical cost ratio versus the estimate}
+%		\label{fig:mcbounds}
+%	\end{figure}
+
+	Prior work~\cite{santalo2004integral} offered an estimate for the expected length of a transit path $C_{sg}$ in terms of the expected length of a line segment, $0.52$, in a randomized setting in an unit square.
+With the current estimate of $0.663$ for the maximum of two such randomly sampled line segments, it follows that, the expected makespan or maximum of distances cost will use this estimate.\qed
+
+%	Using this result, the synchronized cost ratio is stated in Equation~\ref{eq:synchronized-ratio} as
+%	$$
+%	\frac{C_{\rm dual}^{\rm sync}}{C_{\rm single}} \approx 
+%	\frac{(c_{pd} + 0.66c_t)\frac{n}{2} + 4n\pi rc_t}{(c_{pd} + 0.52c_t)n}
+%	$$
+%	As a way to validate our asymptotic estimate, randomized trials were run with different number randomly sampled object transfer coordinates on an unit square.
+%	% Fig \ref{fig:bounds} verifies empirically that the ratio of $\frac{C_{dual}^{sync}}{C_{single}}$ when $c_{pd}=0,r=0$, asymptotically converges to the calculated expected value of $0.636$. 
+%	When $c_{pd}=0$ and $r=0$, the ratio of $\frac{C_{dual}^{sync}}{C_{single}}$ evaluates to $0.636$.
+Fig \ref{fig:mcbounds} verifies empirically that the ratio converges to the expected value as the number of transfers increases.
+%	This indicates the asymptotic speedup of a synchronized dual arm solution for a makespan or maximum of distances cost metric.
+}
+
+}
+
 This means $C_{\rm dual}^{\rm sync} \approx (c_{pd} + 0.66c_t)\frac{n}{2} + 4n\pi rc_t$.
@@
 The synchronized cost ratio is
-\vspace{-0.1in}
-\begin{equation}\label{eq:synchronized-ratio}
-\frac{C_{\rm dual}^{\rm sync}}{C_{\rm single}} \approx 
+%\vspace{-0.1in}
+\begin{align*}\label{eq:synchronized-ratio}
+\frac{C_{\rm dual}^{\rm sync}}{C_{\rm single}} &\approx 
 \frac{(c_{pd} + 0.66c_t)\frac{n}{2} + 4n\pi rc_t}{(c_{pd} + 0.52c_t)n}
-= \frac{1}{2} + \frac{ (0.07 + 4\pi r)c_t}{c_{pd} + 0.52c_t}\;.
-\vspace{-0.1in}
-\end{equation}
+\\&= \frac{1}{2} + \frac{ (0.07 + 4\pi r)c_t}{c_{pd} + 0.52c_t}\;.\numberthis
+%\vspace{-0.1in}
+\end{align*}
 
@@
 \commentdel{Fig \ref{fig:bounds} confirms empirically that in randomized trials on an unit square, the ratio of $\frac{C_{dual}^{sync}}{C_{single}}$ when $c_{pd}=0,r=0$, converges to the calculated estimate (red line).}
-\vspace{-0.08in}
-\begin{theorem}
-For rearranging objects with non-overlapping starts and goals that are 
-uniformly distributed in a unit square,  a randomized $2$-arm synchronized solution can have an 
-asymptotic improvement of $\frac{1}{2}$ over the single arm solution if $\frac{c_t}{c_{pd}}$ is small, and a improvement $\approx 0.64$ when both $c_{pd}$ and $r$ are small. 
-\end{theorem}
+
+\tase{
+	\begin{figure}[h]
+		\centering
+		%	\vspace{-0.3in}
+		\includegraphics[width=0.35\textwidth]{figures/monte_carlo}
+		\caption{Empirical cost ratio versus the estimate}
+		\label{fig:mcbounds}
+	\end{figure}
+	As a way to validate our asymptotic estimate, randomized trials were run with different number randomly sampled object transfer coordinates on an unit square.
+% Fig \ref{fig:bounds} verifies empirically that the ratio of $\frac{C_{dual}^{sync}}{C_{single}}$ when $c_{pd}=0,r=0$, asymptotically converges to the calculated expected value of $0.636$. 
+When $c_{pd}=0$ and $r=0$, the ratio of $\frac{C_{dual}^{sync}}{C_{single}}$ evaluates to $0.636$.
+Fig \ref{fig:mcbounds} verifies empirically that the ratio converges to the expected value as the number of transfers increases.
+This indicates the asymptotic speedup of a synchronized dual arm solution for a makespan or maximum of distances cost metric.
+}
+
+\qed
+%\vspace{-0.08in}
+%\begin{theorem}
+%For rearranging objects with non-overlapping starts and goals that are 
+%uniformly distributed in a unit square,  a randomized $2$-arm synchronized solution can have an 
+%asymptotic improvement of $\frac{1}{2}$ over the single arm solution if $\frac{c_t}{c_{pd}}$ is small, and a improvement $\approx 0.64$ when both $c_{pd}$ and $r$ are small. 
+%\end{theorem}
 

### 2019-06-03 08_evaluation.tex
updates

@@
 
-\begin{figure*}[b]
+\begin{figure}[h]
 %    \vspace{-.6in}
 	\centering
-		\includegraphics[width=0.49\textwidth,trim={1cm 9cm 1cm 5cm},clip]{figures/simple_picker_benchmark}
-		\includegraphics[width=0.47\textwidth]{figures/kuka_benchmark2}
+		\includegraphics[width=0.245\textwidth,trim={1cm 9cm 1cm 5cm},clip]{figures/simple_picker_benchmark}
+		\includegraphics[width=0.235\textwidth]{figures/kuka_benchmark2}
 %		\vspace{-.3in}
@@
 %    \vspace{-.3in}
-\end{figure*}
+\end{figure}
 This section describes the experiments performed to evaluate the algorithms in two  domains shown in Fig \ref{fig:benchmarks}: a) simple picker and b) general manipulators.
@@
 
-%\subsection{Simple Picker}
+\subsection{Simple Picker}
 %The results are shown in Figure~\ref{fig:disk}.
-\textbf{Simple Picker}: This benchmark evaluates two disk robots hovering over a planar surface scattered with objects.
+This benchmark evaluates two disk robots hovering over a planar surface scattered with objects.
 The robots are only free to move around in a plane parallel to the resting plane of the objects, and the robots can pick up objects when they are directly above them.
@@
 
-\textbf{General Dexterous Manipulator}: The second benchmark sets up two \kuka arms across a table with objects on it.
+\subsection{General Dexterous Manipulator} The second benchmark sets up two \kuka arms across a table with objects on it.
 The objects are placed in the common reachable part of both arms' workspace, and only one top-down grasping configuration is allowed for each object pose.
@@
 
-\begin{figure*}[h!]
+\begin{figure*}[t]
 %\vspace{-0.2in}
@@
 \end{figure*}
+
+\tase{
+\subsection{Smoothing}
+The result of the velocity tuning over the solution trajectories for the individual arms as a post-processing step is shown in Fig \ref{fig:smoothing}.
+The objective is to minimize any waits that might be a by-product of the synchronization.
+% The small improvements indicate that synchronization does not adversely affect the solution executions. 
+The small \% improvements indicate that the asynchronous variants of the solutions discovered from the methods do not yield a big enough saving in execution time. 
+Most of the improvement as a percentage of the original solution duration is not too high.
+On top of that, the time taken to smooth the solutions for \algo (overlaid on Fig \ref{fig:smoothing}) shows that it is often not beneficial.
+In their largest problem instances the \kuka spent $ 0.44s $ of smoothing time to save $ 3.23s $ off the solution duration, while the picker spent $  9.84s $ to save $ 0.54s $.
+This indicates that among the class of synchronized solutions discovered by the proposed algorithms, the analogous asynchronous variants do not seem to be drastically better.
+Moreover, smoothing does not improve the maximum of distances cost measure, but only reduces the solution duration.
+The theoretical bounds in the simple planar setups agree with the results in that the synchronization does not degrade the benefits of using 2 arms too much.
+It should be pointed out though that it needs to be studied further, whether these trends would hold for a class of algorithms that can solve the asynchronous dual-arm rearrangement problem in general setups.
+This is out of the scope of the current work.
+
+% \kiril{What is the bottom line here? Is smoothing worthwhile? The y-axis in the plots is labeled as \% whereas the bars are labeled with seconds.}
+
+%\clearpage
+
+% \vspace{-0.2in}
+\begin{figure}[h]
+	\centering	
+	\includegraphics[width=0.48\textwidth]{figures/results/labels}
+	\includegraphics[width=0.48\textwidth]{figures/results/sp_smoothing}
+	\includegraphics[width=0.48\textwidth]{figures/results/kuka_smoothing}
+	\caption{Smoothed solution improvement as a percentage of the original synchronized solution duration, and the time taken to smooth solutions obtained from \algo in seconds.}
+	\label{fig:smoothing}
+	%     \vspace{-.3in}
+\end{figure}
+
+\subsection{Discrete Reachability Benchmark}
+In this benchmark, two Kuka arms are placed opposite a target arrangement table.
+The initial poses of the objects are set to be on opposite ends of the arms, as demonstrated in the image.
+The purpose of this study is to see the effects of general divided workspaces where both the initial and target poses are not in the region of common reachability of the arms.
+This is indeed a simpler problem for the coordinated methods, but proves challenging to the naive random split strategy.
+
+\begin{figure}[h]
+	\centering
+	\includegraphics[width=0.48\textwidth]{figures/reachability}
+	\includegraphics[width=0.48\textwidth]{figures/results/labels}
+	\includegraphics[width=0.48\textwidth]{figures/results/5_kuka_lazy_ms_success.png}
+	\includegraphics[width=0.48\textwidth]{figures/results/5_kuka_lazy_ms_cost.png}
+	\includegraphics[width=0.48\textwidth]{figures/results/5_kuka_lazy_ms_time.png}
+	\caption{The reachability benchmark}
+	\label{fig:reachability_benchmark}
+	%     \vspace{-.3in}
+\end{figure}
+}

### 2019-06-03 01_introduction.tex
update

@@
 	\item It has been argued that smoothing can be used to alleviate the sychronization assumption.
-Data from the effects of smoothing the solutions in the experiments have been reported and show that the minor improvements highlight that in practice the synchronization assumption is not tragic.
+Data from the effects of smoothing the solutions in the experiments have been reported and show that the minor improvements highlight that in practice the synchronization assumption does not adversely affect solution quality to a great extent.
 	\item A k-arm extension of the asymptotic cost bound in the asynchronous case has been included.

### 2019-06-03 08_evaluation.tex
update

@@
 \subsection{Discrete Reachability Benchmark}
-In this benchmark, two Kuka arms are placed opposite a target arrangement table.
+In this benchmark, two Kuka arms are placed opposite a target arrangement table, as shown in Fig \ref{fig:reachability_benchmark}.
 The initial poses of the objects are set to be on opposite ends of the arms, as demonstrated in the image.

### 2019-06-04 08_evaluation.tex
update

--- 2019-06-03 08_evaluation.tex
@@
 \subsection{Smoothing}
+
 The result of the velocity tuning over the solution trajectories for the individual arms as a post-processing step is shown in Fig \ref{fig:smoothing}.
@@
 In their largest problem instances the \kuka spent $ 0.44s $ of smoothing time to save $ 3.23s $ off the solution duration, while the picker spent $  9.84s $ to save $ 0.54s $.
+
+\begin{figure}[h]
+	\centering	
+	\includegraphics[width=0.48\textwidth]{figures/results/labels}
+	\includegraphics[width=0.48\textwidth]{figures/results/sp_smoothing}
+	\includegraphics[width=0.48\textwidth]{figures/results/kuka_smoothing}
+	\caption{Smoothed solution improvement as a percentage of the original synchronized solution duration, and the time taken to smooth solutions obtained from \algo in seconds.}
+	\label{fig:smoothing}
+	%     \vspace{-.3in}
+\end{figure}
+
 This indicates that among the class of synchronized solutions discovered by the proposed algorithms, the analogous asynchronous variants do not seem to be drastically better.
@@
 % \vspace{-0.2in}
-\begin{figure}[h]
-	\centering	
-	\includegraphics[width=0.48\textwidth]{figures/results/labels}
-	\includegraphics[width=0.48\textwidth]{figures/results/sp_smoothing}
-	\includegraphics[width=0.48\textwidth]{figures/results/kuka_smoothing}
-	\caption{Smoothed solution improvement as a percentage of the original synchronized solution duration, and the time taken to smooth solutions obtained from \algo in seconds.}
-	\label{fig:smoothing}
-	%     \vspace{-.3in}
-\end{figure}
 
 \subsection{Discrete Reachability Benchmark}
-In this benchmark, two Kuka arms are placed opposite a target arrangement table.
-The initial poses of the objects are set to be on opposite ends of the arms, as demonstrated in the image.
+
+In this benchmark, two Kuka arms are placed opposite a target arrangement table, as shown in Fig \ref{fig:reachability_benchmark}.
+The initial poses of the objects on either side of the arms in a way that the initial poses are reachable by only one of the arms.
 The purpose of this study is to see the effects of general divided workspaces where both the initial and target poses are not in the region of common reachability of the arms.
-This is indeed a simpler problem for the coordinated methods, but proves challenging to the naive random split strategy.
+This somewhat simplifies the problem of coordinating the two arms because interactions are limited to the target poses of the objects.
 
@@
 \end{figure}
+
+The problem of optimizing the assignment of arms to objects will be affected by the reachability.
+Expectedly, the naive random split tends to erroneously assign unreachable objects to arms.
+It should be noted that a single arm solution does not exist for this benchmark.
+The data reported for the lazy variants, shows that our proposed method manages to maintain scalability and robustness even in such scenarios and moreover, shows the benefits of dual-arm rearrangement.
+
 }

### 2019-06-05 05_approximation.tex
update

@@
 % 		\includegraphics[width=2.5in]{figures/mapp}
-		\includegraphics[width=0.7\textwidth]{figures/mapp_labels}
+%		\includegraphics[width=0.7\textwidth]{figures/mapp_labels}
+		\includegraphics[width=0.8\textwidth]{figures/algo_1}
+		\includegraphics[width=0.8\textwidth]{figures/algo_2}
 	\end{center}
 %\vspace{-0.2in}
-	\caption{(left) A dual-arm rearrangement problem.
-(middle) The same problem as minimum weight edge matching on a fully connected directed graph of \textit{transfers}.
-(right) The ordering of the object-arm assignments from an optimal tour over a \textit{transit} graph.}
+	\caption{\textit{(Top-left)} A dual-arm rearrangement problem.
+\textit{(Top)} The problem of optimizing object transfers reduces to a minimum weight edge matching on a fully connected directed graph of \textit{transfers}.
+\textit{(Bottom)} Each transit moves the arms from the target poses of the current objects, to the initial poses of the next objects in the object-arm assignments.
+The ordering of the object-arm assignments form an optimal tour over a \textit{transit} graph.}
 %	\vspace{-0.2in}

### 2020-12-17 001_ntp.tex
Updates from Overleaf

\tase{Monotone tabletop rearrangement challenges arise in a variety of automation scenarios including product sorting or packing.  Performing this task with two robotic manipulators introduces the overhead of coordinating them in the shared workspace, as well as an increase in the size of the underling search space. The objective of this work is to study the feasibility of such dual-arm solutions, providing both theoretical bounds, as well as a fast, and approximate solution. The approach leverages an effective algorithmic decomposition of the problem so as to take advantage of efficient motion planners and mixed-integer linear programming solvers. The proposed solution has been evaluated in settings that include delta-robots as well as \textit{7-dof} manipulators. Interesting extensions of this work correspond to studying the case of additional arms, non-monotone and general manipulation scenarios.}

### 2020-12-17 01_introduction.tex
Updates from Overleaf

--- 2019-06-03 01_introduction.tex
@@
 setups \cite{193}.
-The proliferation of robot arms, however, including dual-arm setups, implies that industrial settings can utilize multiple robots in the same workspace (Fig \ref{fig:two_arms}).
+The proliferation of robot arms, however, including dual-arm setups, implies that industrial settings can utilize multiple robots in the same workspace (Fig~\ref{fig:two_arms}).
 This work explores a) the benefits of coordinated dual-arm rearrangement versus single-arm, b) the combinatorial challenges involved and c) computationally efficient, high-quality and scalable methods.
@@
 
-A motivating point is that the coordinated use of multiple arms can
+A major motivation for this work is that the coordinated use of multiple arms can
 result in significant improvements in efficiency. This arises from the following argument.
@@
 % \vspace{-.1in}
-\begin{lemma}\label{l:k-arm-lower-bound}
+\begin{observation}\label{l:k-arm-lower-bound}
 There are classes of tabletop rearrangement problems, where a $k$-arm
@@
 % \vspace{-.3in}
-\end{lemma}
+\end{observation}
 
@@
 
+\begin{figure}[t]
+% \vspace{-0.15in}
+	\centering
+	\includegraphics[width=0.48\textwidth]{figures/two_arms}
+% 	\vspace{-0.1in}
+	\caption{Example of dual-arm setups that can utilize
+	algorithms proposed in this work.}
+	\label{fig:two_arms}
+	\vspace{-0.25in}
+\end{figure}
+
 In most practical setups, the expectation is that a $2$-arm solution
@@
 % \vspace{-.1in}
-\begin{lemma}\label{l:2-arm-no-worse}
+\begin{observation}\label{l:2-arm-no-worse}
 For any rearrangement problem, the best $k$-arm ($k \ge 2$) solution
@@
 % \vspace{-.1in}
-\end{lemma}
+\end{observation}
 
-The above points motivate the development of scalable algorithmic
+The above observations motivate the development of scalable algorithmic
 tools for such dual-arm rearrangement instances. This work considers
@@
 quality.
-
-\begin{figure}[t]
-% \vspace{-0.15in}
-	\centering
-	\includegraphics[width=0.48\textwidth]{figures/two_arms}
-% 	\vspace{-0.1in}
-	\caption{Example of dual-arm setups that can utilize
-	algorithms proposed in this work.}
-	\label{fig:two_arms}
-% 	\vspace{-0.25in}
-\end{figure}
 
@@
 arm as a secondary objective by employing a {\tt TSP} solution. Most
-of the computation time is spent on the many calls to a
-lower-level motion planner that coordinates the two arms. A lazy
-evaluation strategy is proposed, where motion plans are evaluated for candidate solution sequences. This results in significant computational improvement and
+of the computation time is spent on the many calls to an underlying motion planner that coordinates the two arms. A lazy
+evaluation strategy is proposed, where motion plans are evaluated and validated for candidate solution sequences, as opposed to performing this expensive motion plan computation for the entire search space.
+This results in significant computational improvement and
 reduces the calls to the motion planner.  An analysis
@@
 The lazy evaluation strategy significantly improves computation costs for both the optimal and proposed methods.
+
+\tase{
+The current archival version is an extension of previous work \cite{shome2018dualarm}. In particular, several additions have been made to provide a more holistic study of the problem:
+\begin{enumerate}
+    % \item Additional explanation and visual support is provided for understanding the algorithmic steps, especially regarding Section \ref{sec:approximation}.
+    \item A detailed illustration and expository text is provided for describing the algorithmic steps, especially regarding Section \ref{sec:approximation}.
+	\item Further analysis has been performed to study the problem (Section \ref{sec:cost_bounds}).
+Specifically, the result describing the asymptotic cost bound for asynchronous operation has been extended to the $k$-arm case.
+Additionally, a more detailed proof is provided for the asymptotic cost bound estimate in the case of synchronized dual-arm operation.
+% 	\item New data (Section \ref{sec:smoothing}) is provided that study the effect of post-processing solutions so as to minimize delays introduced due to the synchronization assumption. 
+	\item The solutions from the benchmarks were post-processed so as to minimize delays introduced due to the synchronization assumption, and the data from this \textit{smoothing} operation is provided in Section \ref{sec:smoothing}.
+	\item A benchmark (Section \ref{sec:reachability}) has been included to demonstrate the efficacy of the proposed approach in problem domains where initial or target poses of objects do not lie in the shared workspace.
+\end{enumerate}
+}
+
 %The computational costs of both the optimal

### 2020-12-17 02_background.tex
Updates from Overleaf

@@
 %Early work has suggested to slightly reduce the~\cite{aronov1999motion} tried dimensionality reduction strategies.
-Optimal strategies were developed for simpler instances of the problem \cite{solovey2015motion}, although in general the problem is known to be computationally hard~\cite{solovey2016hardness}.
+Optimal strategies were developed for simpler instances of the problem~\cite{SolYuZamHal15}, although in general the problem is known to be computationally hard~\cite{solovey2016hardness}.
 Decentralized approaches~\cite{van2005prioritized} also used velocity tuning~\cite{leroy1999multiple}.
 General multi-robot planning tries to plan for multiple high-dimensional platforms \cite{wagner2012probabilistic,Gharbi:2009fu} using sampling-based techniques.
-Recent advances provide scalable~\cite{SoloveySH16:ijrr} and asymptotically optimal~\cite{Dobson:2017aa} sampling based frameworks. 
+Recent advances provide scalable~\cite{SoloveySH16:ijrr} and asymptotically optimal~\cite{Dobson:2017aa,Shome2019} sampling based frameworks. 
 %Assembly planning \cite{halperin2000general,sundaram2001disassembly} is another related problem dealing with multi-body planning.
@@
 Prior work~\cite{coltin2014multi} has applied the PDP problem to robots, taking into account time windows and robot-robot transfers.
-Some seminal work~\cite{lenstra1981complexity,savelsbergh1995general} has explored its complexity, and concedes to the hardness of the problem, while others studied cost bounds~\cite{TrePavFra13}, and proposed ILP formulations~\cite{savelsbergh1995general}.
+The seminal work~\cite{lenstra1981complexity,savelsbergh1995general} has explored its complexity, and concedes to the hardness of the problem, while others studied cost bounds~\cite{TrePavFra13}, and proposed ILP formulations~\cite{savelsbergh1995general}.
 %The existing work that delves into the combinatorial challenges of the problem, do not account for the costs incurred due to coordination of the agents during task execution. 
@@
 % There has been a a lot of work in motion planning for manipulators and movable objects. 
-Navigation among movable objects deals with the combinatorial challenges of multiple objects~\cite{wilfong1991motion,van2009path} and has been shown to be a hard problem, and extended to manipulation applications~\cite{stilman2007manipulation}.
-Despite a lot of interesting work on challenges of manipulation and grasp planning, the current work shall make assumptions that avoid complexities arising from them.
-Manipulators opened the applications of rearrangement planning~\cite{ben1998practical,ota2004rearrangement}, including instances where objects can be grasped only once or monotone~\cite{stilman2007manipulation}, as well as non-monotone instances~\cite{havur2014geometric,srivastava2014combined}.
-Efficient solutions to assembly planning problems~\cite{Wilson:1994fk,Halperin:2000uq} typically assumes monotonicity, as without it the problem becomes much more difficult.
+Navigation among movable objects deals with the combinatorial challenges of multiple objects~\cite{wilfong1991motion,van2009path}, and has been shown to be a hard problem, and extended to manipulation applications~\cite{stilman2007manipulation}.
+Despite a lot of interesting work on challenges of manipulation and design choices~\cite{littlefield2016evaluating} in grasp planning, the current work shall make assumptions that avoid complexities arising from them.
+The availability of manipulators opened the door to solve rearrangement tasks~\cite{ben1998practical,ota2004rearrangement}, including instances where objects can be grasped only once or monotone~\cite{stilman2007manipulation}, as well as non-monotone instances~\cite{havur2014geometric,srivastava2014combined}.
+Efficient solutions to assembly planning problems~\cite{Wilson:1994fk,Halperin:2000uq} typically assume monotonicity, as without it the problem becomes much more difficult.
 Recent work has dealt with the hard instances of task planning~\cite{berenson2011task,cohen2014single} and rearrangement planning~\cite{krontiris2015dealing,krontiris2016efficiently,193}.

### 2020-12-17 03_problem.tex
Updates from Overleaf

@@
-Consider a planar surface and a set of $n$ rigid objects $ \objectset=\{ \object_1, \object_2 \cdots \object_n\}$  that can rest on the surface in stable poses $p_i \in \Pspace_i \subset SE(3)$.
-The arrangement space $ \Aspace = \Pspace_1 \times \Pspace_2 \ldots \times \Pspace_n $ is the Cartesian product of all $\Pspace_i$, where $ \arrangement = (\pose_1, \ldots, \pose_n) \in \Aspace $.
+Consider a planar surface and a set of $n$ rigid objects $ \objectset=\{ \object_1, \object_2 \cdots \object_n\}$  which can rest on the surface in stable poses $p_i \in \Pspace_i \subset SE(3)$.
+The arrangement space $ \Aspace = \Pspace_1 \times \Pspace_2 \ldots \times \Pspace_n $ is the Cartesian product of all $\Pspace_i$, where Every rearrangement $\arrangement \in \Aspace$ is an $n$-tuple $(\pose_1, \ldots, \pose_n)$.
 In valid arrangements $ \Afree \subset \Aspace$, the objects are pairwise disjoint.
+
+% $ \arrangement = (\pose_1, \ldots, \pose_n) \in \Aspace $.
 
@@
 $\cfree^k$ is the set of collision-free configurations for arm $\arm^k$ (while ignoring possible collisions with  objects or the other arm), and is assumed here to be a subset of $\reals^d $.
-A path for $\arm^k$ is denoted as $ \pi^k : [0,1] \rightarrow \cfree^k$ and includes picking and placing actions.
-Let $ \cfree^i(\pi^j) $ represent the collision free $\mathbb{C}$-space for $\arm^i$, given that $\arm^j$ moves along $\pi^j $.
-This is a function of the paths' parametrization.
-The space of dual-arm paths $\mathcal{D}$ denotes pairs of paths for the two arms: $D = (\pi^1,\pi^2) \in \mathcal{D}$.
+A path for $\arm^k$ is denoted as $ \pi^k : [0,1] \rightarrow \cfree^k$ and includes picking and placing actions throughout the entire rearrangement process.
+Let the set of collisions induced between the geometries of both the arms at two configurations along the path (at $t$) be denoted by the expression $ \pi^1(t) \ominus \pi^2(t) $.
+If there are no collisions then $\pi^1(t) \ominus \pi^2(t) = \emptyset$.
+% Let $ \cfree^i(\pi^j) $ represent the collision free $\mathbb{C}$-space for $\arm^i$, given that $\arm^j$ moves along $\pi^j $. This is a function of the paths' parametrization. 
+The space of dual-arm paths $\mathcal{D}$ is made of pairs of paths for the two arms: $D = (\pi^1,\pi^2) \in \mathcal{D}$.
 Then, $\arrangement(\ainit, D)$ is the resulting arrangement when the objects are at $\ainit$ and moved according to $D$.
@@
 % \vspace{-.1in}
-{\definition [Optimal Dual-arm Rearrangement] Given arms $\arm^1$, $\arm^2$ and objects $\objectset$ to be moved from initial arrangement $ \ainit \in \Afree$ to target arrangement $ \atarget \in \Afree $, the optimal dual-arm rearrangement problem asks for a dual-arm path $D^* \in \mathcal{D}$, which satisfies the following constraint:
+{\definition [Optimal Dual-arm Rearrangement] Given arms $\arm^1$, $\arm^2$ and objects $\objectset$ to be moved from initial arrangement $ \ainit \in \Afree$ to target arrangement $ \atarget \in \Afree $, the optimal dual-arm rearrangement problem asks for a dual-arm path $D^* \in \mathcal{D}$, which optimizes a cost function, and solution paths belong to the valid configuration space.
 
 % \vspace{-.15in} 
-\begin{equation}
- D^* =  (\pi^{*1}, \pi^{*2}) \ |\ \arrangement(\ainit, D^*) = \atarget \textrm{ and } \pi^{*i} \in \cfree^i(\pi^{*j}) \vspace{-.05in}
-\label{eq:dualarm_constraint}
-\end{equation}
- and optimizes a cost function: $D^* = \underset{ \forall D \in \mathcal{D}}{ \mathtt{argmin} } \ \cost(D).$}
+% \begin{equation}
+%  D^* =  (\pi^{*1}, \pi^{*2}) \ |\ \arrangement(\ainit, D^*) = \atarget \textrm{ and } \pi^{*i} \in \cfree^i(\pi^{*j}) \vspace{-.05in}
+% \label{eq:dualarm_constraint}
+% \end{equation}
+%  and optimizes a cost function: $D^* = \underset{ \forall D \in \mathcal{D}}{ \mathtt{argmin} } \ \cost(D).$}
 
-A set of assumptions are introduced to deal with the problem's combinatorics.
+% \begin{align*}
+%  D^* =  (\pi^{*1}, \pi^{*2}) = \underset{ \forall D \in \mathcal{D}}{ \mathtt{argmin} }\ \cost(D) \numberthis\label{eq:dualarm_constraint} \\ 
+%  \ \textrm{such that} \ \arrangement(\ainit, D^*) = \atarget \textrm{ and,}\\ \pi^{*1} \in \cfree^1(\pi^{*2}), \pi^{*2} \in \cfree^2(\pi^{*1})  
+% \end{align*}
+%  and optimizes a cost function: $D^* =  .$}
+\vspace{-0.1in}
+\begin{align*}
+ D^* =  (\pi^{*1}, \pi^{*2}) &= \underset{ \forall D \in \mathcal{D}}{ \mathtt{argmin} }\ \cost(D) \numberthis\label{eq:dualarm_constraint} \\ 
+ \ \textrm{such that} \ \arrangement(\ainit, D^*) &= \atarget \textrm{ ,and }\ \forall t\in[0,1]\\
+ \pi^{*1}(t) \in \cfree^1,\ \pi^{*2}(t) \in \cfree^2,\ & \pi^{*1}(t) \ominus \pi^{*2}(t) = \emptyset
+\end{align*}
+
+Assumptions are introduced to deal with the problem's combinatorics.
 The reachable task-space $\taskspace^k \subset SE(3)$ of arm $\arm^k$ is the set of $SE(3)$ poses that objects attached to the arm's end effector can acquire.
@@
 
-Let the ordered set of objects moved during the arm path $ \pi^i $ be denoted as $ \moveset(\pi^k) $.
+Let the ordered set of objects moved during the arm path $ \pi^k $ be denoted as $ \moveset(\pi^k) $.
 In general, an object can appear many times in $ \moveset(\pi^k) $.
@@
 
-\noindent\textbf{Moves or Transits:} Paths $M(\pi^1_{i\rightarrow i^{\prime}},\pi^2_{i\rightarrow i^{\prime}}) \in \mathcal{D}$, $ \moveset(\pi^1_{i\rightarrow i^{\prime}}) = \emptyset $, and each $\arm^k$:
+\noindent\textbf{Moves or Transits:} Paths $M(\pi^1_{i\rightarrow i^{\prime}},\pi^2_{i\rightarrow i^{\prime}}) \in \mathcal{D}$, $ \moveset(\pi^k_{i\rightarrow i^{\prime}}) = \emptyset $, and each $\arm^k$:
 \begin{myitem}
@@
 \end{align*}}
-\noindent For simplicity, Eq.~\ref{eq:synchronicity} does not include an initial move from $q^k_{\rm safe} \in \cfree^k$ and a final move back to $q^k_{\rm safe}$.
-An odd number of objects can also be easily handled.
+\noindent For simplicity, Eq.~\ref{eq:synchronicity} does not include an initial move from $q^k_{\rm safe} \in \cfree^k$ and a final move back to $q^k_{\rm safe}$ (an odd number of objects can also be easily handled).
 Then, the sequence of object pairs moved during a dual-arm path as in Eq.
@@
 \end{equation}
-Note that the \textit{transfer} costs do not depend on the order with which the objects are moved but only on the assignment of objects to arms.
+Note that the \textit{transfer} costs do not depend on the order in which the objects are moved but only on the assignment of objects to arms.
 The \textit{transit} costs arise out of the specific ordering in $ \scoma(D)$.
@@
 
-The synchronicity assumption allows to study the combinatorial challenges of the problem, which do not relate to the choice of time synchronization of different picks and placements.
-Section \ref{sec:integration} describes the use of $\drrtstar$\cite{Dobson:2017aa} as the underlying motion planner that can discover solutions that can synchronize arm motions for simultaneous picks, and simultaneous placements.
+The synchronicity assumption allows to study the combinatorial challenges of the problem, which do not relate to the choice of time synchronization of different pickups and drop-offs.
+Section \ref{sec:integration} describes the use of $\drrtstar$\cite{Dobson:2017aa,Shome2019} as the underlying motion planner that can discover solutions that can synchronize arm motions for simultaneous picks, and simultaneous placements.
 The synchronicity assumption is relaxed through smoothing (Section \ref{sec:integration}).
@@
 This assumption is also relaxed in Section \ref{sec:integration}, with a lazy variant of the proposed method.
-Once a complete candidate solution is obtained, collision checking can be done with everything in the scene.
+Once a complete candidate solution is obtained, collision checking is performed with the entire scene.
 
-Overall, under the assumptions, the current work identifies a problem structure, which allows arguments pertaining to the search space, completeness, and optimality.
-Nevertheless, the smoothed, lazy variant of the proposed method will still return effective solutions in practice, even if these assumptions do not hold.
+Overall, under Assumptions~{1-3}, the current work identifies a problem structure, which allows arguments pertaining to the search space, completeness, and optimality.
+Nevertheless, the smoothed, lazy variant of the proposed method will still, in the
+experiments that were carried out, often return effective solutions in practice, even if these assumptions do not hold.
 

### 2020-12-17 04_baseline.tex
update
Updates from Overleaf

@@
 
-\subsection{Exhaustive Search} The exhaustive search approach shown in Fig.
+\subsection{Exhaustive Search} The exhaustive search approach, illustrated in Fig.
 \ref{fig:backtracking} is a brute force expansion of all possible sequences of object pairs $ \scoma $.
@@
 The approach evaluates the cost for all possible branches to return the best sequence $\scoma$.
-The total number of nodes is in the order of $O(n!)$, expressed over the levels $L$ of the search tree as:
+% The total number of nodes is in the order of $O(n!)$, expressed over the levels $L$ of the search tree as: 
+The total number of possible distinct plans is $n!$. 
 % \kiril{It may be beneficial to explain the formula below, or perhaps move it to the appendix to save space and avoid explaining it here.}:
 
-% \vspace{-0.25in}
+\vspace{-0.1in}
 \begin{align*}
@@
     % \vspace{-.15in}
-	\caption{Search tree for 4 objects. 
+	\caption{Search tree for 4 objects (A,B,C,D) where each branch orders a sequence of object-arm assignments. 
 %	In node $XY$, $m^1$ transfers object $X$, and $m^2$ transfers $Y$. An edge is a transit to the next node. 
@@
 
-% \vspace{-0.25in}
+\vspace{-0.2in}
 \begin{align*}
@@
 
-This returns optimal synchronized solution but performs an exhaustive search and requires exponentially many calls to a motion planner.
+This returns an optimal synchronized solution but performs an exhaustive search and requires exponentially many calls to a motion planner.
 
@@
 \textit{Graph Representation:}
-The problem can be represented as a directed graph where each vertex $v = \coma_v = (\object_v^1, \object_v^2)$ corresponds to a transfer $ T(\coma_u) $ and edges $e(u,v)$ are valid moves $M(\coma_{u\rightarrow v})$.
+The problem can be represented as a directed graph where:
+\begin{myitem}
+\item vertices $v = \coma_v = (\object_v^1, \object_v^2)$ correspond to a transfer $ T(\coma_v) $;
+\item edges $e(u,v)$ are valid moves $M(\coma_{u\rightarrow v})$.
+\end{myitem} 
 A valid edge $e(u,v)$ is one where an object does not appear more than once in the transfers of nodes $u$ and $v$.
-The cost of a directed edge $e(u,v)$ encodes both the cost of the transfer  $ T(\coma_v) $ and the cost of the move $M(\coma_{u\rightarrow v})$.
+The cost of a directed edge $e(u,v)$ encodes both the cost of the transfer  $ T(\coma_u) $ and the cost of the move $M(\coma_{u\rightarrow v})$.
 There is also a vertex $ \startq $, which connects moves from and to the safe arm configurations $q^k_{\rm safe}$.
@@
 
-% \vspace{-.25in}
+\vspace{-.1in}
 \begin{align*}
-\hspace{0.5in} \hat{V} =& \{ v = \coma_v = (\object_v^1,\object_v^2)\ |\\& \  \forall\ \object_v^1,\object_v^2 \in \objectset, \object_v^1 \neq \object_v^2 \} \cup \{S\}\\
+\hspace{0.5in} \hat{V} =& \{S\} \cup \{ v = \coma_v = (\object_v^1,\object_v^2)\ |\\& \  \forall\ \object_v^1,\object_v^2 \in \objectset, \object_v^1 \neq \object_v^2 \}, \\
 \hat{E} =& \{  e(u,v)\ | \ \forall\ u,v\in \hat{V} \textrm{ so that } u\neq v,\ \\& 
@@
  \{e(\startq,v)\ \forall\ v\in\hat{V}\setminus \startq\} \cup \\& \{e(v,\startq)\ \forall\ v\in\hat{V}\setminus \startq\}\\
-cost_{e(u,v)} =& \cost(u) + \cost(u,v)\\ =&\cost(T(\coma_u)) + \cost(M(\coma_{u\rightarrow v}))
+cost_{e(u,v)} = & \cost(u) + \cost(u,v)\\ = &\cost(T(\coma_u)) + \cost(M(\coma_{u\rightarrow v}))
 \end{align*}
@@
 Let $\cost(\startq) = 0$.
-The total number of motion planning queries needed to be answered to define the edge costs is expressed in Eq.~\ref{eq:mpcount}.
+The total number of motion planning queries needed to be answered to define the edge costs is given in Eq.~\ref{eq:mpcount}.
 The formulation proposed in this section tries to ensure the discovery of $ \scoma^* $ on $ \hat{G} $ as a tour that starts and ends at $ \startq $, while traversing each vertex corresponding to $ \scoma^* $.
 To provide the {\tt MILP} formulation, define $ \delta_{\rm in}(v) $ as the in-edge set $v$, and  $ \delta_{\rm out}(v) $ as the out-edge set.
-Then, $ \gamma(\object) $ is the object coverage set $ \gamma(\object) = \{ e(u,v) \ |\ e\in\hat{E}, \object\in  \coma_u  \} $, i.e., all the edges that transfer $ \object $.
+Then, $ \gamma(\object) $ is the object coverage set $ \gamma(\object) = \{ e(u,v) \ |\ e\in\hat{E}, \object\in  \coma_u  \} $, i.e., all the edges that transfer an object $ \object $.
 
-\textit{Model:} Set the optimization objective as: $\ \ \min \sum_{e \in \hat{E}} cost_e x_e\  $\hspace{.81in} [A]\\ 
+\textit{Model:} Set the optimization objective as:
+%$\ \ \min \sum_{e \in \hat{E}} cost_e x_e\  $\hspace{.81in} [A]\\ 
+\begin{align*}
+	\min \sum_{e \in \hat{E}} cost_e x_e \tag*{[A]}
+\end{align*}
 Eq.
@@
 Eq.
-[I] lazily enforces the tour to be of length $ \frac{n}{2} + 1 $.
+[I] lazily enforces the tour to be of length $ \frac{n}{2} + 1 $~\cite{dantzig1954solution}.
 While the number of motion-planning queries to be solved is the same as in exhaustive search, efficient {\milp} solvers \cite{gurobi} provide a more scalable search process.
 
-% \vspace{-.2in}
+\vspace{-.1in}
 \noindent\begin{minipage}{.48\textwidth}
@@
 \sum_{e\in\delta_{\rm out}(v)} x_e \leq 1& \ \ \forall v\in \hat{V} \tag*{[D]}\\
+\sum_{e\in\delta_{\rm in}(v)}x_e = \sum_{e\in\delta_{\rm out}(v)}x_e& \ \ \forall v\in \hat{V} \tag*{[E]}\\
+\sum_{e\in\delta_{\rm in}(\startq)} x_e = 1& \tag*{[F]}\\
+\sum_{e\in\delta_{\rm out}(\startq)} x_e = 1& \tag*{[G]}\\
 \end{align*}
@@
 \begin{align*}
-\sum_{e\in\delta_{\rm in}(v)}x_e = \sum_{e\in\delta_{\rm out}(v)}x_e& \ \ \forall v\in \hat{V} \tag*{[E]}\\
-\sum_{e\in\delta_{\rm in}(\startq)} x_e = 1& \tag*{[F]}\\
-\sum_{e\in\delta_{\rm out}(\startq)} x_e = 1& \tag*{[G]}\\
 \sum_{e\in\gamma(\object)} x_e = 1& \ \  \forall \object\in\objectset \tag*{[H]}\\

### 2020-12-17 05_approximation.tex
Updates from Overleaf

@@
 \end{align*}
-noting that the $0.44\sqrt{n\ln n}c_t$ term may also be ignored for large $n$. The cost of dual arm solutions will be analyzed in Section \ref{sec:cost_bounds}.
+noting that the $0.44\sqrt{n\ln n}c_t$ term may also be ignored for large $n$.
+The cost of dual arm solutions will be analyzed in Section \ref{sec:cost_bounds}.
+We summarize the discussion above in the following lemma.
 {
@@
 
-\begin{align*}
-	\graph(\nodes, \edges)\\
-	\nodes = \{ \node=\object, \forall \object \in \objectset \}\\
-	\edges = \{ \edge(u, v): \coma = (u,v), \forall u,v\in\nodes \}\\
-	\cost(\edge(u,v)) = \cost(T(\coma=(u,v))) \numberthis\label{eq:transfergraph}\\ \\
-	\tspgraph(\tspnodes, \tspedges)\\
-	\tspnodes = \{ \node=\coma, \forall \coma \in \scomaset^* \} \cup \{\coma_S\} \\
-	\tspedges = \{ \edge(u, v): \coma_{u\rightarrow v}, \forall u,v\in\tspnodes \}\\
-	\cost(\edge(u,v)) = \cost(M(\coma_{u\rightarrow v})) \numberthis\label{eq:transitgraph}
-\end{align*}
+% \begin{align*}
+% 	\graph(\nodes, \edges)\\
+% 	\nodes = \{ \node=\object, \forall \object \in \objectset \}\\
+% 	\edges = \{ \edge(u, v): \coma = (u,v), \forall u,v\in\nodes \}\\
+% 	\cost(\edge(u,v)) = \cost(T(\coma=(u,v))) \numberthis\label{eq:transfergraph}\\ \\
+% 	\tspgraph(\tspnodes, \tspedges)\\
+% 	\tspnodes = \{ \node=\coma, \forall \coma \in \scomaset^* \} \cup \{\coma_S\} \\
+% 	\tspedges = \{ \edge(u, v): \coma_{u\rightarrow v}, \forall u,v\in\tspnodes \}\\
+% 	\cost(\edge(u,v)) = \cost(M(\coma_{u\rightarrow v})) \numberthis\label{eq:transitgraph}
+% \end{align*}
+
 %\vspace{0.05in}
@@
 %\vspace{-0.2in}
-	\caption{\textit{(Top-left)} A dual-arm rearrangement problem.
-\textit{(Top)} The problem of optimizing object transfers reduces to a minimum weight edge matching on a fully connected directed graph of \textit{transfers}.
-\textit{(Bottom)} Each transit moves the arms from the target poses of the current objects, to the initial poses of the next objects in the object-arm assignments.
-The ordering of the object-arm assignments form an optimal tour over a \textit{transit} graph.}
+	\caption{ \tase{ \textit{(Top-left)} A dual-arm rearrangement problem.
+\textit{(Top-middle)} Directed edges between objects represents the assignment of arms to object \textit{transfers}.
+\textit{(Top-right)} The problem of optimizing object transfers reduces to a minimum weight edge matching on a fully connected directed graph of \textit{transfers}.
+\textit{(Bottom-left)} The legends for the different symbols used in the diagrams.
+\textit{(Bottom-middle)} A directed edge between object pairs represents the \textit{transit} between the target poses of the previous objects to the initial poses of the next.
+\textit{(Bottom-right)} Each transit moves the arms from the target poses of the current objects, to the initial poses of the next objects in the object-arm assignments.
+A sequence of object-arm assignments form an optimal tour over a \textit{transit} graph.} }
 %	\vspace{-0.2in}
@@
 % \end{figure}
-%\vspace{-0.1in}
+\vspace{-0.1in}
 \end{figure*}
 
-\subsection{Foundations} Consider a complete weighted directed graph $\graph(\nodes,\edges)$ (Eq.~\ref{eq:transfergraph}), where $\node \in \nodes$ corresponds to a single object $ \object $.
+\subsection{Foundations} Consider a complete weighted directed graph $\graph(\nodes,\edges)$ (Eqs.~\ref{eq:transfergraph}), where $\node \in \nodes$ corresponds to a single object $ \object $.
  Each directed edge, $\edge=(\object_i,\object_j) \in \edges$ is an ordered pair of objects $ \object_i $ and $\object_j $, where the order determines the assignment of an object to an arm $ \arm^1 $ or $ \arm^2 $.
 The cost of an edge $ \cost(\edge) $ is the coordinated motion planning cost of performing the transfer corresponding to $ \coma = (\object_i,\object_j) $.
-For instance, as shown in Fig \ref{fig:edge_matching}(middle), $\edge(A,B)$ corresponds to $ \arm^1 $ transferring `A', while $ \arm^2 $ transfers `B', and the $\cost( \edge(A,B) ) = \cost(T(\coma=(A,B))$ is the cost of such a concurrent motion.
+For instance, as shown in Fig~\ref{fig:edge_matching}(top-middle), $\edge(A,B)$ corresponds to $ \arm^1 $ transferring `A', while $ \arm^2 $ transfers `B', and the $\cost( \edge(A,B) ) = \cost(T(\coma=(A,B))$ is the cost of such a concurrent motion.
 %Note that these costs refer to only the transfer costs i.e., starting from the arms picking up the objects $ A $ and $ B $ at the initial poses(as shown in Fig \ref{fig:edge_matching}(left)), and moving them to their target poses.
 It should also be noted that since the arms are different, in general, $\cost( \edge(A,B) ) \neq \cost( \edge(B,A) )$.
+\vspace{-0.1in}
+\begin{align*}
+	\graph(\nodes, \edges)\\
+	\nodes = \{ \node=\object, \forall \object \in \objectset \}\\
+	\edges = \{ \edge(u, v): \coma = (u,v), \forall u,v\in\nodes \}\\
+	\cost(\edge(u,v)) = \cost(T(\coma=(u,v))) \numberthis\label{eq:transfergraph}
+\end{align*}
 
-Following the observation made in Eq.~\ref{eq:cost_function}, the cost of the transfers can be reasoned about independent of their order. 
+By Eq.~\ref{eq:cost_function}, the cost of the transfers can be reasoned about independent of their order. 
 Define $\scomaset$ as the unordered set of $\coma\in\scoma$, then unordered transfer cost component corresponds to $\sum_{\coma\in\scomaset}\cost(T(\coma))$.
@@
 $ \scoma $ is an ordered sequence of $ \coma $, and $ \scomaset $ denote the unordered set of all $ \coma $ that comprise $ \scoma $.
-Since $ \graph $ is a complete graph where every edge corresponds to every possible valid $ \coma $, by construction $ \scomaset \subset \edges$.
+Since $ \graph $ is a complete graph (shown in Fig~\ref{fig:edge_matching}(top-right)) where every edge corresponds to every possible valid $ \coma $, by construction $ \scomaset \subset \edges$.
 A candidate solution of a monotone dual-arm rearrangement problem must transfer every object exactly once.
@@
 {\lemma [Perfect Matching]
-Every candidate solution to a monotone dual-arm rearrangement problem comprises of a set of unordered object-to-arm assignments $ \scomaset $ that is also a perfect matching solution on $ \graph $.
+Every candidate solution to a monotone dual-arm rearrangement problem comprises a set of unordered object-to-arm assignments $ \scomaset $ that is also a perfect matching solution on $ \graph $.
 }
@@
 Construct another directed graph $ \tspgraph $ (Eqs.
-\ref{eq:transitgraph}), where the vertices comprise of the $ \coma \in \scomaset^*$.
+\ref{eq:transitgraph}), where the vertices comprise of the $ \coma \in \scomaset^*$, i.e., the optimal object-to-arm assignments.
 An edge $ e(\coma_{u\rightarrow v}) $ corresponds to the coordinated \textit{transit} motion between them.
-For instance, as in Fig \ref{fig:edge_matching}(right) for an edge between $ \coma(A,B) $ and $ \coma(C,D) $, $ \arm^1 $ moves from the target pose of object `A' to the starting pose of object `C', and similarly $ \arm^2 $ moves from the target of `B' to the start of `D'.
-An additional vertex corresponding to the starting(and ending) configuration of the two arms ($ \startq $) is added to the graph.
-The graph is fully connected again to represent all possible transits or moves.
+For instance, as in Fig~\ref{fig:edge_matching}(bottom-middle) for an edge between $ \coma(A,B) $ and $ \coma(C,D) $, $ \arm^1 $ moves from the target pose of object `A' to the starting pose of object `C', and similarly $ \arm^2 $ moves from the target of `B' to the start of `D'.
+An additional vertex corresponding to the starting (and ending) configuration of the two arms ($ \startq $) is added to the graph.
+The graph (shown in Fig~\ref{fig:edge_matching}(bottom-right)) is fully connected again to represent all possible transits or moves.
+\vspace{-0.1in}
+\begin{align*}
+	\tspgraph(\tspnodes, \tspedges)\\
+	\tspnodes = \{ \node=\coma, \forall \coma \in \scomaset^* \} \cup \{\coma_S\} \\
+	\tspedges = \{ \edge(u, v): \coma_{u\rightarrow v}, \forall u,v\in\tspnodes \}\\
+	\cost(\edge(u,v)) = \cost(M(\coma_{u\rightarrow v})) \numberthis\label{eq:transitgraph}
+\end{align*}
+
 A complete candidate solution to the problem now requires the sequence of~$ \coma $, 
@@
 This means, any candidate tour corresponds to a $ \scoma_\tour\in\mathbb{P}^{\scomaset} $.
-An optimal tour on $ \tspgraph $ minimizes the transit costs over the all possible candidate solutions in  $ \mathbb{P}^{\scomaset^*} $.
+An optimal tour on $ \tspgraph $ minimizes the transit costs over the all possible candidate solutions in  $ \mathbb{P}^{\scomaset^*} $
 %\vspace{-0.1in}
 \begin{equation}
-\scoma^+ = \underset{ \scoma \in  \mathbb{P}^{\scomaset^*}   }{ \mathtt{argmin} } \ \sum_{e(u,v)\in\tour}\cost({M}( \coma_{u\rightarrow v} ))  )
+\scoma^+ = \underset{ \scoma \in  \mathbb{P}^{\scomaset^*}   }{ \mathtt{argmin} } \ \sum_{e(u,v)\in\tour}\cost({M}( \coma_{u\rightarrow v} ))  ).
 %\vspace{-0.05in}
@@
 
-%\vspace{-0.1in}
-
+\vspace{-0.1in}
 \subsection{Algorithm : Tour-Over-Matching} 
@@
 % The algorithm takes as input the set of objects $ \objectset $ and the start(and end) configuration $ \startq $ of the arms.
-
-\noindent $ \mathtt{transfer\_graph} $: This function constructs a directed graph $ \graph $ defined by Eqs.~\ref{eq:transfergraph}.
-This step creates a graph with $ n $ vertices and $ \permu[n]{2} $ edges.
 
@@
 
-\noindent $ \mathtt{optimal\_matching} $: This function takes the graph $ \graph $ constructed as an argument and returns the unordered set of edges, corresponding to the set of optimal transfers over $ \graph $.
+\begin{itemize}
+\item[-] $ \mathtt{transfer\_graph} $: This function constructs a directed graph $ \graph $ defined by Eqs.~\ref{eq:transfergraph}.
+This step creates a graph with $ n $ vertices and $ \permu[n]{2} $ edges.
+\item[-] $ \mathtt{optimal\_matching} $: This function takes the graph $ \graph $ constructed as an argument and returns the unordered set of edges, corresponding to the set of optimal transfers over $ \graph $.
 \commentdel{The first step is to convert the directed graph $ \graph $ into an equivalent undirected graph $ \graph_U $.
-Since $ \graph $ is complete, every pair of vertices has two directed edges between them.
+Since $ \graph $ is complete, every pair of vertices shares two directed edges between them.
 $\graph_U$ only preserves the minimally weighted connection for every vertex pair.
@@
 The runtime complexity of the step is $ O(|\edges||\nodes|\log|\nodes|) = O(\permu[n]{2}n\log n ) = O(n^3\log n)$.
-
-\noindent $ \mathtt{transit\_graph} $: This function constructs the directed transit graph $ \tspgraph $ as per the set of Eqs.~\ref{eq:transitgraph}.
+\item[-] $ \mathtt{transit\_graph} $: This function constructs the directed transit graph $ \tspgraph $ as per the set of Eqs.~\ref{eq:transitgraph}.
 This constructs $ \frac{n}{2} + 1 $ vertices and $ \permu[(\frac{n}{2} + 1)]{2} $ edges.
-
-\noindent $\mathtt{optimal\_tour}  $: Standard TSP solvers like Gurobi~\cite{gurobi} can be used to find the  
+\item[-]  $\mathtt{optimal\_tour}  $: Standard TSP solvers like Gurobi~\cite{gurobi} can be used to find the  
 % It should be noted that a lot of efficient solvers exist for such problems, that provide various degrees of approximation. 
 optimal tour over $ \tspgraph $ corresponding to $ \scoma^+ $.
+\end{itemize}
 
@@
 The total number of such calls compared to the count from the baseline in Equ.
-\ref{eq:mpcount}, shows a saving in the order of $ O(n^2)$ queries ($\textrm{\# of Transfers} + \textrm{\# of Moves}$).
+\ref{eq:mpcount}, shows a saving of a factor of $ O(n^2)$ queries ($\textrm{\# of Transfers} + \textrm{\# of Moves}$).
 % \kiril{Consider completing the calculation.}
-%\vspace{-0.1in}
-
+\vspace{-0.1in}
 \begin{align*}
@@
 
-The evaluation performed here focuses on the maximum of distances (Eq.~\ref{eq:cost_function}) for a fair comparison with the other methods.
+The evaluation performed here focuses on the maximum of distances (Eq.~\ref{eq:cost_function}) covered by the arms in a solution for a fair comparison with the other methods.
 The prioritization of optimization objective, however, is also amenable to other cost functions, where carrying objects is often more expensive than object-free motions.

### 2020-12-17 06_integration.tex
update
Updates from Overleaf

--- 2018-10-29 06_integration.tex
@@
 For planar environments with disk robot pickers~(similar to delta robots), recent work~\cite{kirkpatrick2016characterizing} characterizes the optimal two-disk coordinated motions.
-The current implementation uses a general multi-robot motion planning framework \drrtstar~\cite{Dobson:2017aa} for dual-arm coordinated planning.
+The current implementation uses a general multi-robot motion planning framework \drrtstar~\cite{Dobson:2017aa,Shome2019} for dual-arm coordinated planning.
 
@@
 
-\begin{wrapfigure}{r}{0.6\textwidth}
-  \vspace{-0.1in}
-  \begin{minipage}{0.6\textwidth}
-  \vspace{0pt} 
-  \begin{algorithm}[H]
+%\begin{wrapfigure}{r}{0.6\textwidth}
+%  \vspace{-0.5 in}
+%  \begin{minipage}{0.6\textwidth}
+%  \vspace{0pt} 
+  \begin{algorithm}[t]
   \caption{{\tt Lazy\_Evaluation}$ (\mathtt{ALGO}, \mathcal{H}, \mathtt{MP}) $}
@@
   \end{algorithm}
-  \end{minipage}
-  \vspace{-0.35in}
-\end{wrapfigure}
+%  \end{minipage}
+%  \vspace{-0.35in}
+%\end{wrapfigure}
 
@@
 Dual-arm rearrangement can be significantly sped up if the motion planning queries are replaced with look-ups of such heuristics.
-Once a candidate $ \scoma $ is obtained, motion planning can evaluate the solution $ \trajset(\scoma) $.
+Once a candidate $ \scoma $ is obtained, motion planning can expand the solution $ \trajset(\scoma) $ to obtain the actual solution paths.
 If this fails, the algorithm tries other sequences.
@@
 The lazy variants give up on optimality for the sake of efficiency but given enough retries the algorithms will eventually solve every problem that {\tt ALGO} can.
-Since the motion planning happens in the order of execution, the object non-interactivity assumption is relaxed.
+The motion planning and evaluation is performed in sequence of the order of execution.
+The object non-interactivity assumption is relaxed since all the object positions are effectively known during the evaluation of a candidate solution.
 
@@
 Smoothing does not change the maximum of distances, only improves execution time.
-Indications that the smoothed variants of the synchronous solutions do not provide significant savings in execution time are included in the Appendix for the interested reader.
+Indications that the smoothed variants of the synchronous solutions do not provide significant savings in execution time are included in the results for the interested reader in Fig~\ref{fig:smoothing}.
 
-It should be noted that in an iterative version of \algo, in order to explore variations in $ \scomaset^* $ if failures occur in finding $\tour$, some edges need to be temporarily blocked on $ \scomaset^* $.
+It should be noted that in an iterative version of \algo, in order to explore variations in optimal object-to-arm assignments $ \scomaset^* $ if failures occur in finding $\tour$, some edges need to be temporarily blocked on $ \scomaset^* $.
 The search structures can also be augmented with {\tt NO\_ACT} tasks, for possible $\coma$ where one of the arms do not move.

### 2020-12-17 07_cost_bounds.tex
Updates from Overleaf

@@
-Following from Lemma \ref{lem:transferdomination}, the current analysis studies the dual arm costs in the randomized unit tabletop setting, with $c_t$ as the cost measure per unit distance. 
-For the $2$-arm setting, assume for simplicity that each arm's volume is represented as a disc of some radius 
-$r$. For obtaining a $2$-arm solution, we partition the $n$ objects randomly 
-into two piles of $\frac{n}{2}$ objects each; then obtain two initial solutions 
-similar to the single arm case. It is expected (Eq.~\ref{eq:single-cost-simple}) that these two halves 
-should add up to approximately $(c_{pd} + 0.52c_t)n$.
+% This section studies the dual arm costs in the randomized unit tabletop setting, where $c_t$ is the cost measure per unit distance.
+For the $2$-arm setting, assume for simplicity that each arm's volume is represented as a disc of some radius $r$.
+For obtaining a $2$-arm solution, first partition the $n$ objects randomly into two sets of $\frac{n}{2}$ objects each.
+Then, obtain the two initial solutions similar to the single arm case.
+It is expected (Eq.~\ref{eq:single-cost-simple}) that these two halves should add up to approximately $(c_{pd} + 0.52c_t)n$.
+The reasoning follows Lemma \ref{lem:transferdomination}, which states that transfers dominate the cost of the solution.
+
+% \begin{theorem}
+% 	\textit{A $2$-arm solution can have an asymptotic improvement of $\frac{1}{2}$ over the single arm solution for rearranging objects with non-overlapping starts and goals that are uniformly distributed in a unit square}
+% 	\label{thm:karm}
+% \end{theorem}
+
+% \textit{Proof: }
+% From the initial $2$-arm solution, we construct an {\em asynchronous} $2$-arm 
+% solution that is collision-free.
+Assume that pickups and drop-offs can be achieved without collisions between the two arms, which can be achieved with properly designed end-effectors.
+The main overhead is then the potential collision between the two (disc) arms during transfer and move operations.
+Because there are $\frac{n}{2}$ objects for each arm to work
+% with, an arm may travel a path formed by $n + 1$ straight line 
+% segments. Therefore, there are up to $(n + 1)^2$ intersections between the 
+% two end-effector trajectories where potential collisions may happen.
+Nevertheless, since we can have at most four intersections for the transfers and transits associated with a pair of objects (one for each arm), there are at most $2n$ potential collisions to handle.
+For each intersection, let one
+% arm wait while the other circles around the first arm, which incurs a cost that is bounded by $2\pi \cdot r \cdot c_t$.
+
+% Adding up all the potential cost that a $2$-arm solution can incur, the following cumulative cost is obtained:
+% % \begin{align}\label{eq:dual-cost-distance} 
+% % C_{dual} = C_{single} + 2n(2\pi rc_t) \approx (c_{pd} + 0.52c_t + 4\pi rc_t)n.
+% % \end{align}
+
+% {\centerline
+% {
+% $C_{\rm dual} = C_{\rm single} + 2n(2\pi rc_t) \approx (c_{pd} + 0.52c_t + 4\pi rc_t)n\;.$
+% }
+% }
+
+% \noindent For small $r$, $C_{\rm dual}$ is almost the same as $C_{\rm single}$, and
+% $c_t$ is a distance (e.g., energy) cost. Upon considering the maximum of the two arc lengths or makespan (Eq.~\ref{eq:cost_function}),
+% the $2$-arm cost becomes $C_{\rm dual}^t \approx (c_{pd} + 0.52c_t)\frac{n}{2} + 4n\pi rc_t$.
+% % \vspace{-0.1in}
+% % \begin{equation}\label{eq:dual-cost-time}
+% % C_{dual}^t \approx (c_{pd} + 0.52c_t)\frac{n}{2} + 4n\pi rc_t
+% % \vspace{-0.1in}
+% % \end{equation}
+% % {\centerline
+% % {
+% % $C_{dual}^t \approx (c_{pd} + 0.52c_t)\frac{n}{2} + 4n\pi rc_t$
+% % }
+% % }
+% The cost ratio is
+% %\vspace{-0.1in}
+% \begin{align*}%\label{eq:makespan-ratio}
+% \frac{C_{\rm dual}^t}{C_{\rm single}} &\approx 
+% \frac{(c_{pd} + 0.52c_t)\frac{n}{2} + 4n\pi rc_t}{(c_{pd} + 0.52c_t)n}
+% \\&= \frac{1}{2} + \frac{4\pi rc_t}{c_{pd} + 0.52c_t}\;\numberthis \label{eq:dualasync}
+% % \vspace{-0.1in}
+% \end{align*}
+
+% \commentdel{
+%  \begin{wrapfigure}{r}{1.4in}
+% %  \vspace{-.45in}
+% 	\centering
+%     \includegraphics[width=1.4in]{figures/monte_carlo}
+% %    \vspace{-.4in}
+% 	\caption{Empirical cost ratio versus the estimate}
+%   	\label{fig:bounds}
+% %    \vspace{-.4in}
+% \end{wrapfigure}
+% }
+
+% When $r$ is small or when $\frac{c_t}{c_{pd}}$ is small, the $2$-arm 
+% solution is roughly half as costly as the single arm solution. On 
+% the other hand, in this model a $2$-arm solution does not do better than $\frac{1}{2}$ of the single arm solution. $ \qed $
+
+% %This argument can be extended to $k$-arms as well \cite{Shome2018WAFR}.
+
+% %\vspace{-0.08in}
+% \commentadd{
+% %\begin{theorem}
+% %For rearranging objects with non-overlapping starts and goals that are
+% %uniformly distributed in a unit square,  a $2$-arm solution can have an 
+% %asymptotic improvement of $\frac{1}{2}$ over the single arm solution. 
+% %\label{thm:karm}
+% %\end{theorem}
+% }
+
+% \tase{
+
+% The following argument generalizes Theorem~\ref{thm:karm} to the case of $k$-arms.
+
+% \begin{theorem}
+% 	\textit{A $k$-arm solution can have an 
+% 	asymptotic improvement of $\frac{1}{k}$ over the single arm solution, when rearranging objects with non-overlapping starts and goals that are uniformly distributed in a unit square.}
+% \end{theorem}
+
+% \textit{Proof:}	
+% %\subsection{Expected k-arm cost bounds in a planar disk manipulator model}
+% \commentadd{The arguments made in Theorem \ref{thm:karm} can be extended to $k$ disc arms.
+% 	In the planar unit-square setting, with $k$ arms, there are $\frac{n}{k}$ objects 
+% 	for each arm to work with. Consider the transfers and transits of a set of $k$ 
+% 	objects, one for each arm. By \cite{ChiHanYu2018WAFR}, the arbitrary rearrangement of $k$ discs 
+% 	can be achieved in a bounded region with a perimeter of $O(kr)$. 
+% 	Clearly, the per robot additional (makespan or distance) cost is bounded by some 
+% 	function $f(k, r)c_t$, which goes to zero as $r$ goes to zero. Adding up all the potential cost that can be incurred,  a $k$-arm solution has a cumulative cost of:
+
+% 	{\centerline
+% 		{
+% 			$C_{\rm k{\text-}arm} = C_{\rm single} + nf(k,r)c_t \approx (c_{pd} + 0.52c_t + f(k,r)c_t)n\;.$
+% 		}
+% 	}
+
+% 	\noindent For fixed $k$ and small $r$, $C_{\rm k{\text-}arm}$ is almost the same as $C_{\rm single}$.
+% 	%, $c_t$ is a distance (e.g., energy) cost. 
+% 	Upon considering the maximum of the two arc lengths or makespan,
+% 	the $k$-arm cost becomes $C_{\rm k{\text-}arm}^t \approx (c_{pd} + 0.52c_t)\frac{n}{k} + nf(k,r)c_t$.
+
+% 	The cost ratio is
+% % 	\vspace{-0.1in}
+% 	\begin{align*}\label{eq:kmakespan-ratio}
+% 	\frac{C_{\rm k{\text-}arm}^t}{C_{\rm single}} &\approx 
+% 	\frac{(c_{pd} + 0.52c_t)\frac{n}{k} + nf(k,r)c_t}{(c_{pd} + 0.52c_t)n}
+% 	\\&= \frac{1}{k} + \frac{f(k,r)c_t}{c_{pd} + 0.52c_t}\;.\numberthis
+% 	% \vspace{-0.1in}
+% 	\end{align*}
+
+% 	When $r$ is small or when $\frac{c_t}{c_{pd}}$ is small, the $k$-arm 
+% 	solution is roughly $\frac{1}{k}$ as costly as the single arm solution. On 
+% 	the other hand, in this model a $k$-arm solution does not do better than $\frac{1}{k}$ of 
+% 	the single arm. \qed
+
+% %	\begin{theorem}
+% %		For rearranging objects with non-overlapping starts and goals that are
+% %		uniformly distributed in a unit square,  a $k$-arm solution can have an 
+% %		asymptotic improvement of $\frac{1}{k}$ over the single arm solution. 
+% %	\end{theorem}
+% }
+% % \rahul{Need to verify this line of reasoning}
+
+% }
+
+This section studies the dual arm costs in the randomized unit tabletop setting, where $c_t$ is the cost measure per unit distance.
+Assume for simplicity that each arm's volume is represented as a disc of some radius $r$.
+Eq.~\ref{eq:single-cost-simple} derives the cost estimate for a single arm solution as approximately $(c_{pd} + 0.52c_t)n$.
+Firstly the following arguments can be made for $k$-arms.
+
+\tase{
 
 \begin{theorem}
-	\textit{For rearranging objects with non-overlapping starts and goals that are
-	uniformly distributed in a unit square,  a $2$-arm solution can have an 
-	asymptotic improvement of $\frac{1}{2}$ over the single arm solution. }
+	\textit{A $k$-arm solution can have an 
+	asymptotic improvement of $\frac{1}{k}$ over the single arm solution, when rearranging objects with non-overlapping starts and goals that are uniformly distributed in a unit square.}
+\end{theorem}
+
+\textit{Proof:}	
+%\subsection{Expected k-arm cost bounds in a planar disk manipulator model}
+\commentadd{%The arguments made in Theorem \ref{thm:karm} can be extended to $k$ disc arms.
+	In the planar unit-square setting, with $k$ arms, there are $\frac{n}{k}$ objects 
+	for each arm to work with. Consider the transfers and transits of a set of $k$ 
+	objects, one for each arm. By \cite{ChiHanYu2018WAFR}, the arbitrary rearrangement of $k$ discs 
+	can be achieved in a bounded region with a perimeter of $O(kr)$. 
+	Clearly, the per robot additional (makespan or distance) cost is bounded by some 
+	function $f(k, r)c_t$, which goes to zero as $r$ goes to zero. Adding up all the potential cost that can be incurred,  a $k$-arm solution has a cumulative cost of:
+
+	{\centerline
+		{
+			$C_{\rm k{\text-}arm} = C_{\rm single} + nf(k,r)c_t \approx (c_{pd} + 0.52c_t + f(k,r)c_t)n\;.$
+		}
+	}
+
+	\noindent For fixed $k$ and small $r$, $C_{\rm k{\text-}arm}$ is almost the same as $C_{\rm single}$.
+	%, $c_t$ is a distance (e.g., energy) cost. 
+	Upon considering the maximum of the two arc lengths or makespan,
+	the $k$-arm cost becomes $C_{\rm k{\text-}arm}^t \approx (c_{pd} + 0.52c_t)\frac{n}{k} + nf(k,r)c_t$.
+
+	The cost ratio is
+% 	\vspace{-0.1in}
+	\begin{align*}\label{eq:kmakespan-ratio}
+	\frac{C_{\rm k{\text-}arm}^t}{C_{\rm single}} &\approx 
+	\frac{(c_{pd} + 0.52c_t)\frac{n}{k} + nf(k,r)c_t}{(c_{pd} + 0.52c_t)n}
+	\\&= \frac{1}{k} + \frac{f(k,r)c_t}{c_{pd} + 0.52c_t}\;.\numberthis
+	% \vspace{-0.1in}
+	\end{align*}
+
+	When $r$ is small or when $\frac{c_t}{c_{pd}}$ is small, the $k$-arm 
+	solution is roughly $\frac{1}{k}$ as costly as the single arm solution. On 
+	the other hand, in this model a $k$-arm solution does not do better than $\frac{1}{k}$ of 
+	the single arm. \qed
+
+    }
+}
+
+For obtaining a $2$-arm solution, first partition the $n$ objects randomly into two sets of $\frac{n}{2}$ objects each. Then, obtain the two initial solutions similar to the single arm case.  
+% It is expected (Eq.~\ref{eq:single-cost-simple}) that these two halves should add up to approximately $(c_{pd} + 0.52c_t)n$. 
+% The reasoning follows Lemma \ref{lem:transferdomination}, which states that transfers dominate the cost of the solution.
+
+\begin{corollary}
+	\textit{A $2$-arm solution can have an asymptotic improvement of $\frac{1}{2}$ over the single arm solution for rearranging objects with non-overlapping starts and goals that are uniformly distributed in a unit square}
 	\label{thm:karm}
-\end{theorem}
+\end{corollary}
 
@@
 From the initial $2$-arm solution, we construct an {\em asynchronous} $2$-arm 
-solution that is collision-free. Assume that pickups 
-and drop-offs can be achieved without collisions between the two arms, which 
-can be achieved with properly designed end-effectors. The main overhead 
-is then the potential collision between the two (disc) arms during transfer 
-and move operations. Because there are $\frac{n}{2}$ objects for each arm to work 
+solution that is collision-free.
+Assume that pickups and drop-offs can be achieved without collisions between the two arms, which can be achieved with properly designed end-effectors.
+The main overhead is then the potential collision between the two (disc) arms during transfer and move operations.
+Because there are $\frac{n}{2}$ objects for each arm to work
 with, an arm may travel a path formed by $n + 1$ straight line 
 segments. Therefore, there are up to $(n + 1)^2$ intersections between the 
-two end-effector trajectories where potential collision may happen. However,
-because for the transfers and transits associated with one pair of objects (one 
-for each arm) can have at most four intersections, there are at most 
-$2n$ potential collisions to handle. For each intersection, let one 
-arm wait while letting the other circling around it, which incurs a cost that is bounded by $2\pi \cdot
-r \cdot c_t$.
+two end-effector trajectories where potential collisions may happen.
+Nevertheless, since we can have at most four intersections for the transfers and transits associated with a pair of objects (one for each arm), there are at most $2n$ potential collisions to handle.
+For each intersection, let one
+arm wait while the other circles around the first arm, which incurs a cost that is bounded by $2\pi \cdot r \cdot c_t$.
 
-Adding up all the potential extra cost,  
-% that a $2$-arm solution has 
-a cumulative cost is obtained as 
-% \begin{align}\label{eq:dual-cost-distance} 
-% C_{dual} = C_{single} + 2n(2\pi rc_t) \approx (c_{pd} + 0.52c_t + 4\pi rc_t)n.
-% \end{align}
+Adding up all the potential cost that a $2$-arm solution can incur, the following cumulative cost is obtained:
 
@@
 
-\noindent For small $r$, $C_{\rm dual}$ is almost the same as $C_{\rm single}$ 
+\noindent For small $r$, $C_{\rm dual}$ is almost the same as $C_{\rm single}$, and
 $c_t$ is a distance (e.g., energy) cost. Upon considering the maximum of the two arc lengths or makespan (Eq.~\ref{eq:cost_function}),
 the $2$-arm cost becomes $C_{\rm dual}^t \approx (c_{pd} + 0.52c_t)\frac{n}{2} + 4n\pi rc_t$.
-% \vspace{-0.1in}
-% \begin{equation}\label{eq:dual-cost-time}
-% C_{dual}^t \approx (c_{pd} + 0.52c_t)\frac{n}{2} + 4n\pi rc_t
-% \vspace{-0.1in}
-% \end{equation}
-% {\centerline
-% {
-% $C_{dual}^t \approx (c_{pd} + 0.52c_t)\frac{n}{2} + 4n\pi rc_t$
-% }
-% }
+
 The cost ratio is
 %\vspace{-0.1in}
-\begin{align*}\label{eq:makespan-ratio}
+\begin{align*}%\label{eq:makespan-ratio}
 \frac{C_{\rm dual}^t}{C_{\rm single}} &\approx 
 \frac{(c_{pd} + 0.52c_t)\frac{n}{2} + 4n\pi rc_t}{(c_{pd} + 0.52c_t)n}
-\\&= \frac{1}{2} + \frac{4\pi rc_t}{c_{pd} + 0.52c_t}\;.\numberthis
+\\&= \frac{1}{2} + \frac{4\pi rc_t}{c_{pd} + 0.52c_t}\;\numberthis \label{eq:dualasync}
 % \vspace{-0.1in}
@@
 solution is roughly half as costly as the single arm solution. On 
-the other hand, in this model a $2$-arm solution does not do better than $\frac{1}{2}$ of 
-the single arm 
-solution. $ \qed $
-
-%This argument can be extended to $k$-arms as well \cite{Shome2018WAFR}.
-
-%\vspace{-0.08in}
-\commentadd{
-%\begin{theorem}
-%For rearranging objects with non-overlapping starts and goals that are
-%uniformly distributed in a unit square,  a $2$-arm solution can have an 
-%asymptotic improvement of $\frac{1}{2}$ over the single arm solution. 
-%\label{thm:karm}
-%\end{theorem}
-}
-
-\tase{
-\begin{theorem}
-	\textit{For rearranging objects with non-overlapping starts and goals that are
-	uniformly distributed in a unit square,  a $k$-arm solution can have an 
-	asymptotic improvement of $\frac{1}{k}$ over the single arm solution. }
-\end{theorem}
-
-\textit{Proof:}	
-%\subsection{Expected k-arm cost bounds in a planar disk manipulator model}
-\commentadd{The arguments made in Theorem \ref{thm:karm} can be extended to $k$ disc arms.
-	In the planar unit-square setting, with $k$ arms, there are $\frac{n}{k}$ objects 
-	for each arm to work with. Consider the transfers and transits of a set of $k$ 
-	objects, one for each arm. By \cite{ChiHanYu2018WAFR}, the arbitrary rearrangement of $k$ discs 
-	can be achieved in a bounded region with a perimeter of $O(kr)$. 
-	Clearly, the per robot additional (makespan or distance) cost is bounded by some 
-	function $f(k, r)c_t$, which goes to zero as $r$ goes to zero. Adding up all the potential 
-	extra cost,  a $k$-arm solution has a cumulative cost
-
-	{\centerline
-		{
-			$C_{\rm k{\text-}arm} = C_{\rm single} + nf(k,r)c_t \approx (c_{pd} + 0.52c_t + f(k,r)c_t)n\;.$
-		}
-	}
-
-	\noindent For fixed $k$ and small $r$, $C_{\rm k{\text-}arm}$ is almost the same as $C_{\rm single}$.
-	%, $c_t$ is a distance (e.g., energy) cost. 
-	Upon considering the maximum of the two arc lengths or makespan,
-	the $k$-arm cost becomes $C_{\rm k{\text-}arm}^t \approx (c_{pd} + 0.52c_t)\frac{n}{k} + nf(k,r)c_t$.
-
-	The cost ratio is
-	\vspace{-0.1in}
-	\begin{align*}\label{eq:kmakespan-ratio}
-	\frac{C_{\rm k{\text-}arm}^t}{C_{\rm single}} &\approx 
-	\frac{(c_{pd} + 0.52c_t)\frac{n}{k} + nf(k,r)c_t}{(c_{pd} + 0.52c_t)n}
-	\\&= \frac{1}{k} + \frac{f(k,r)c_t}{c_{pd} + 0.52c_t}\;.\numberthis
-	% \vspace{-0.1in}
-	\end{align*}
-
-	When $r$ is small or when $\frac{c_t}{c_{pd}}$ is small, the $k$-arm 
-	solution is roughly $\frac{1}{k}$ as costly as the single arm solution. On 
-	the other hand, in this model a $k$-arm solution does not do better than $\frac{1}{k}$ of 
-	the single arm. \qed
-
-%	\begin{theorem}
-%		For rearranging objects with non-overlapping starts and goals that are
-%		uniformly distributed in a unit square,  a $k$-arm solution can have an 
-%		asymptotic improvement of $\frac{1}{k}$ over the single arm solution. 
-%	\end{theorem}
-}
-% \rahul{Need to verify this line of reasoning}
-
-}
+the other hand, in this model a $2$-arm solution does not do better than $\frac{1}{2}$ of the single arm solution. $ \qed $
 
@@
 	uniformly distributed in a unit square,  a randomized $2$-arm \textit{synchronized} solution can have an 
-	asymptotic improvement of $\frac{1}{2}$ over the single arm solution if $\frac{c_t}{c_{pd}}$ is small, and a improvement $\approx 0.64$ when both $c_{pd}$ and $r$ are small. }
+	asymptotic improvement of $\frac{1}{2}$ over the single arm solution if $\frac{c_t}{c_{pd}}$ is small, and an improvement of roughly $0.64$ when both $c_{pd}$ and $r$ are small. }
+\label{thm:syncproof}
 \end{theorem}
 
-\textit{Proof:} The synchronization assumption changes the expected cost of the solution.
-The random partitioning of the $n$ objects into two sets of $\frac{n}{2}$ object with a random ordering of the objects yields $\frac{n}{2}$ pairs of objects transfers, which dominate the total cost for large $n$.
-The cost~(Eq.~\ref{eq:cost_function}) of $\frac{n}{2}$ synchronized transfers ($\coma_i$) includes $\frac{n}{2}c_{pd}$ and $C^{\rm sync}_{sg} \approx (\mathtt{E}(max(l_1,l_2))c_t)\frac{n}{2}$, where $\mathtt{E}(max(l_1,l_2))$ is the expected measure of the max of lengths $l_1$,$l_2$ of two randomly paired transfers.
-Using the \textit{pdf}\cite{ghosh1951random} of lengths of random lines in an unit square and integrating over the setup\cite{Shome2018WAFR}, results in the value of $\mathtt{E}(max(l_1,l_2))$ to be $0.66$ .
-% (Section \ref{sec:appendix}).
-
+\textit{Proof:} 
 \tase{
+In preparation for the proof of Theorem \ref{thm:syncproof}, we develop the following lemma.
 \begin{lemma}
-	Expected measure of the maximum of lengths of two random lines on an unit square is $ 0.66 $.
+	The expected measure of the maximum of lengths of two random lines on a unit square is $ 0.66 $.
 \end{lemma}
 
-\textit{Proof:} Prior work \cite{ghosh1951random} defines the \textit{probability distribution function (pdf)} of lengths($l$) of randomly sampled lines in a rectangle.
+\textit{Proof:} Prior work \cite{ghosh1951random} defines the \textit{probability distribution function (pdf)} of lengths($\ell$) of randomly sampled lines in a rectangle.
 % of sides $a,b, \ \ a\geq b$.
@@
 %In the unit square model, $a=b=1$. Substituting the values, the \textit{pdf} becomes
-In the unit square model, substituting the values for the dimensions of the sides of the rectangle with $1$, the \textit{pdf} can be simplified as follows.
+Substituting the values for the dimensions of the rectangle in the unit square model, the \textit{pdf} can be simplified as follows.
 \begin{align*}
-p(l)&= 2\pi l - 8\pi l^2 + 2l^3, \ \ l\in[0,1]\\
-p(l)&= 4l\sininv(\frac{1}{l}) - 4l\cosinv(\frac{1}{l}) + 8l\sqrt[]{(l^2-1)} -2l^3 -4l,\\ &\ l\in[1,\sqrt[]{2}]
+p(\ell)&= 2\pi \ell - 8\pi \ell^2 + 2\ell^3, \ \ \ell\in[0,1]\\
+p(\ell)&= 4\ell\sininv\!\!\left(\frac{1}{\ell}\right)\!- 4\ell\cosinv\!\!\left(\frac{1}{\ell}\right)\!+ 8\ell\sqrt{\ell^2-1} -2\ell^3 -4\ell,\\ &\ \ell\in[1,\sqrt[]{2}],
 \end{align*}
-
-Assuming two random sets of lines, representing transfers in a random split of objects between two arms, we need the expected value of the maximum of these pairwise lengths ie., $\mathtt{E}(max(l_1,l_2)), \ \ l_1,l_2\ i.i.d, \ \ l_1 \sim p, l_2 \sim p$.
-This is estimated using the \textit{pdf} obtained. 
+where $\ell$ is the length measure, and $p(\ell)$ is the probability measure over different lengths.
+Assuming two random sets of lines, representing transfers in a random split of objects between two arms, the expected value of the maximum of these pairwise lengths i.e., $\mathtt{E}(\max(\ell_1,\ell_2)), \ \ \ell_1,\ell_2\ i.i.d, \ \ \ell_1 \sim p, \ell_2 \sim p$, can be estimated using the \textit{pdf} obtained.
 \begin{align*}
-\mathtt{E}(max(l_1,l_2)) &= \int_0^{\sqrt[]{2}} \int_0^{\sqrt[]{2}} max(l_1,l_2)p(l_1)p(l_2) dl_2 dl_1\\&\approx 0.663
+\mathtt{E}(\max(\ell_1,\ell_2)) &= \int_0^{\sqrt[]{2}} \int_0^{\sqrt[]{2}} \max(\ell_1,\ell_2)p(\ell_1)p(\ell_2) d\ell_2 d\ell_1\\&\approx 0.663
 \end{align*}
-The result is calculated by taking into account the combination of different ranges of $p(l)$ and $max(l_1,l_2)$.
+% \vspace{-0.1in}
+% The result is calculated by taking into account the combination of different ranges of $p(\ell)$ and $\max(\ell_1,\ell_2)$.
 \commentadd{
@@
 %	\end{figure}
+	Prior work~\cite{santalo2004integral} offered an estimate for the expected length of a transit path $C_{sg}$ in terms of the expected length of a line segment, $0.52$, in a randomized setting in a unit square.
+With the current estimate of $0.66$ for the maximum of two such randomly sampled line segments, it follows that, the expected makespan or maximum of distances cost will use this estimate.
 
-	Prior work~\cite{santalo2004integral} offered an estimate for the expected length of a transit path $C_{sg}$ in terms of the expected length of a line segment, $0.52$, in a randomized setting in an unit square.
-With the current estimate of $0.663$ for the maximum of two such randomly sampled line segments, it follows that, the expected makespan or maximum of distances cost will use this estimate.\qed
+	\qed
 
@@
 
-This means $C_{\rm dual}^{\rm sync} \approx (c_{pd} + 0.66c_t)\frac{n}{2} + 4n\pi rc_t$.
+Now all the tools necessary for the proof of Theorem \ref{thm:syncproof} are available.
+
+The synchronization assumption changes the expected cost of the solution.
+The random partitioning of the $n$ objects into two sets of $\frac{n}{2}$ object with a random ordering of the objects yields $\frac{n}{2}$ pairs of objects transfers, which dominate the total cost for large $n$.
+The cost~(Eq.~\ref{eq:cost_function}) of $\frac{n}{2}$ synchronized transfers ($\coma_i$) includes $\frac{n}{2}c_{pd}$ and $C^{\rm sync}_{sg} \approx (\mathtt{E}(\max(\ell_1,\ell_2))c_t)\frac{n}{2}$, where $\mathtt{E}(\max(\ell_1,\ell_2))$ is the expected measure of the maximum of lengths $\ell_1$,$\ell_2$ of two randomly paired transfers.
+% This value is deduced in the next section.
+
+%Using the \textit{pdf}\cite{ghosh1951random} of lengths of random lines in an unit square and integrating over the setup, results in the value of $\mathtt{E}(max(l_1,l_2))$ to be $0.66$ .
+
+% (Section \ref{sec:appendix}).
+
+It follows that $C_{\rm dual}^{\rm sync} \approx (c_{pd} + 0.66c_t)\frac{n}{2} + 4n\pi rc_t$.
 % \vspace{-0.1in}
@@
 When $\frac{c_t}{c_{pd}}$ is small, even the synchronized $2$-arm solution provides an improvement of $\frac{1}{2}$.
-For the case when both $r$ and $c_{pd}$ are small, we observe that the ratio approaches $0.636$.
+For the case when both $r$ and $c_{pd}$ are small, we observe that the ratio approaches $0.636$.\qed
 \commentdel{Fig \ref{fig:bounds} confirms empirically that in randomized trials on an unit square, the ratio of $\frac{C_{dual}^{sync}}{C_{single}}$ when $c_{pd}=0,r=0$, converges to the calculated estimate (red line).}
@@
 		\centering
-		%	\vspace{-0.3in}
+% 		\vspace{-0.1in}
 		\includegraphics[width=0.35\textwidth]{figures/monte_carlo}
-		\caption{Empirical cost ratio versus the estimate}
+		\caption{ \tase{ Empirical cost ratio $\frac{C_{dual}^{sync}}{C_{single}}$ when $c_{pd}=0, r=0$ in the unit square model, versus the estimate (red line).
+As the number of object transfers increases the measured value converges to the estimate.
+} }
 		\label{fig:mcbounds}
+		\vspace{-0.1in}
 	\end{figure}
-	As a way to validate our asymptotic estimate, randomized trials were run with different number randomly sampled object transfer coordinates on an unit square.
+	As a way to validate our asymptotic estimate, randomized trials were run with different number of randomly sampled object transfer coordinates on an unit square.
 % Fig \ref{fig:bounds} verifies empirically that the ratio of $\frac{C_{dual}^{sync}}{C_{single}}$ when $c_{pd}=0,r=0$, asymptotically converges to the calculated expected value of $0.636$. 
@@
 
-\qed
 %\vspace{-0.08in}
@@
 \commentadd{
-\noindent \textbf{Note on bounds:} Even though the proposed simplified model does not apply immediately costs and collision volumes in general configuration spaces, experiments indicate that the speedups exist in these spaces as well.
+\noindent \textbf{Note on bounds:} Even though the proposed simplified model may not be
+immediately suitable for general configuration spaces, experiments indicate that the speedups exist in these spaces as well.
 }

### 2020-12-17 08_evaluation.tex
Updates from Overleaf

@@
 \begin{figure}[h]
-%    \vspace{-.6in}
+\vspace{-0.1in}
 	\centering
@@
 		\label{fig:benchmarks}
-%    \vspace{-.3in}
+\vspace{-0.1in}
 \end{figure}
-This section describes the experiments performed to evaluate the algorithms in two  domains shown in Fig \ref{fig:benchmarks}: a) simple picker and b) general manipulators.
-%\begin{figure}[ht]
-%	\centering
-%	\includegraphics[width=1.9in]{figures/simple_picker_benchmark}
-%	\includegraphics[width=1.8in]{figures/kuka_benchmark2}
-%	\caption{The benchmarks: \textit{Simple Picker} and the \textit{General Manipulators} }
-%	\label{fig:benchmarks}
-%\end{figure}
-In order to ensure monotonicity, the object starts and goals do not overlap.
-Uniform cuboidal objects simplify the grasping problem, though this is not a limitation of the methods.
-$ 50 $ random experiments were limited to $300s$ of computation time.
-The underlying $ \drrtstar $ motion planner is restricted to a max of $ 3s $ per plan.
-A comparison point includes a random split method, which splits $ \objectset $ at random into two subsets and chooses an arbitrary ordering.
-Maximum of distances cost is compared to the single arm solution~\cite{193}.
-Computation times and success rates are reported.
-The trends in both experiments show that in the single-shot versions, exhaustive and \milp tend to time-out for larger $n$.
-Lazy variants scale much better for all the algorithms, and in some cases increase the success ratio due to retries.
-\algo has much better running time than exhaustive and \milp, and producing better and more solutions than random split.
-Overall, the results show a) our \milp succeeds more within the time limit than exhaustive, b) \algo scales the best among all the methods, and c) the cost of solutions from \algo is close to the optimal baseline, which is around half of the single arm cost.
-% to demonstrate the gains from using multiple arms.
-Overall, MILP scales better than exhaustive search, while finding optimal solutions.
-\algo scales better than the other methods, and finds high quality solutions.
-The lazy variants improve all the dual-arm methods.
-
-\subsection{Simple Picker}
-%The results are shown in Figure~\ref{fig:disk}.
-This benchmark evaluates two disk robots hovering over a planar surface scattered with objects.
-The robots are only free to move around in a plane parallel to the resting plane of the objects, and the robots can pick up objects when they are directly above them.
-Fig~\ref{fig:disk}(\textit{top}) all runs up to $ 24 $ objects succeeded for \algo.
-\milp scales better than exhaustive.
-Lazy random split succeeds in all cases~(\textit{bottom}).
-In terms of solution costs~(\textit{middle}) exhaustive finds the true optimal.
-\milp matches exhaustive and \algo is competitive.
-In all experiments, \algo enjoys a success rate of 100\%.
-% \kiril{What is the reason for low success rate of exhaustive and milp?
-Is it due to exceeding the time budget?} \kiril{This paragraph misses a statement that demonstrates the benefits of our approach: "In all experiments, \algo enjoys a success rate of \%100, while having much better running time than exhaustive and milp, and producing a higher cost solution than random split.
-Furthermore, \algo produces a plan whose cost is around half of the single arm plan cost." Similar statements should be added to the other experiments.}
-
-%\subsection{General Manipulator}
-%The results are shown in Figure~\ref{fig:kuka}.
-
-\subsection{General Dexterous Manipulator} The second benchmark sets up two \kuka arms across a table with objects on it.
-The objects are placed in the common reachable part of both arms' workspace, and only one top-down grasping configuration is allowed for each object pose.
-Here (Fig~\ref{fig:kuka}) a larger number of motion plans tend to fail, so the single shot variants show artifacts of the randomness of \drrtstar in their success rates.
-% The lazy iterative variants show the robust scalability. 
-Random split performs the worst since it is unlikely to chance upon valid motion plans. Single shot exhaustive and \milp scale poorly because of expensive motion planning.
-Interestingly, motion planning infeasibility reduces the size of the exhaustive search tree.
-The solution costs \textit{(middle)} substantiate benefits of the use of two arms. The computation times \textit{(bottom)} again show the scalability of \algo, even compared to random split.
-% In terms of cost. MILP scales to more objects but the computational overhead is more than \algo. Dual-arm solutions are significantly better than single arm.
 
@@
 	\includegraphics[width=0.48\textwidth]{figures/results/3_sp_lazy_ms_time}
-%	\vspace{-0.15in}
+	\vspace{-0.1in}
 	\caption{\textit{Simple Picker} results with success\textit{(top)}, solution costs\textit{(middle)}, and computation\textit{(bottom)} reported for single-shot\textit{(left)} and lazy\textit{(right)} versions of the methods}
-%    \vspace{-0.3in}
+    \vspace{-0.1in}
 	\label{fig:disk}
@@
 	\includegraphics[width=0.48\textwidth]{figures/results/1_kuka_lazy_ms_time}
-%	\vspace{-0.15in}
+	\vspace{-0.1in}
     \caption{\textit{\kuka}results with success\textit{(top)}, solution costs\textit{(middle)}, and computation\textit{(bottom)} reported for single-shot\textit{(left)} and lazy\textit{(right)} versions of the methods}
-%    \vspace{-0.3in}
+    \vspace{-0.2in}
 	\label{fig:kuka}
@@
 
+This section describes the experiments performed to evaluate the algorithms in two  domains shown in Fig~\ref{fig:benchmarks}: a) simple picker and b) general manipulators.
+%\begin{figure}[ht]
+%	\centering
+%	\includegraphics[width=1.9in]{figures/simple_picker_benchmark}
+%	\includegraphics[width=1.8in]{figures/kuka_benchmark2}
+%	\caption{The benchmarks: \textit{Simple Picker} and the \textit{General Manipulators} }
+%	\label{fig:benchmarks}
+%\end{figure}
+In order to ensure monotonicity, the object starts and goals do not overlap.
+Uniform cuboidal objects simplify the grasping problem, though this is not a limitation of the methods.
+$ 50 $ random experiments were limited to $300s$ of computation time.
+The underlying $ \drrtstar $ motion planner is restricted to a max of $ 3s $ per plan.
+A comparison point includes a random split method, which splits $ \objectset $ at random into two subsets and chooses an arbitrary ordering.
+Maximum of distances cost is compared to the single arm solution~\cite{193}.
+Computation times and success rates are reported.
+The trends in both experiments show that in the single-shot versions, exhaustive and \milp tend to time-out for larger $n$.
+Lazy variants scale much better for all the algorithms, and in some cases increase the success ratio due to retries.
+\algo has much better running time than exhaustive and \milp, and produces better and more solutions than random split.
+Overall, the results show that a) our \milp succeeds more within the time limit than exhaustive, b) \algo scales the best among all the methods, and c) \textbf{the cost of solutions from \algo is close to the optimal baseline}, which is around half of the single arm cost.
+% to demonstrate the gains from using multiple arms.
+Overall, MILP scales better than exhaustive search, while finding optimal solutions.
+\algo scales better than the other methods, and finds high quality solutions.
+The lazy variants improve all the dual-arm methods.
+
+\subsection{Simple Picker}
+%The results are shown in Figure~\ref{fig:disk}.
+This benchmark evaluates two disk robots hovering over a planar surface scattered with objects.
+The robots are only free to move around in a plane parallel to the resting plane of the objects, and the robots can pick up objects when they are directly above them.
+This benchmark is reminiscent of delta-robots operating over a picking surface.
+Fig~\ref{fig:disk}(\textit{top}) all runs up to $ 24 $ objects succeeded for \algo.
+\milp scales better than exhaustive.
+Lazy random split succeeds in all cases~(\textit{bottom}).
+In terms of solution costs~(\textit{middle}) exhaustive finds the true optimal.
+\milp matches exhaustive and \algo is competitive.
+In all experiments, \algo enjoys a success rate of 100\% while having much better computation time that exhaustive and \milp, as the number of objects increases.
+% \kiril{What is the reason for low success rate of exhaustive and milp?
+Is it due to exceeding the time budget?} \kiril{This paragraph misses a statement that demonstrates the benefits of our approach: "In all experiments, \algo enjoys a success rate of \%100, while having much better running time than exhaustive and milp, and producing a higher cost solution than random split.
+Furthermore, \algo produces a plan whose cost is around half of the single arm plan cost." Similar statements should be added to the other experiments.}
+
+%\subsection{General Manipulator}
+%The results are shown in Figure~\ref{fig:kuka}.
+
+\subsection{General Dexterous Manipulator} The second benchmark sets up two \kuka arms across a table with objects on it.
+The objects are placed in the common reachable part of both arms' workspace, and only one top-down grasping configuration is allowed for each object pose.
+Here (Fig~\ref{fig:kuka}) a larger number of motion plans tend to fail, so the single shot variants show artifacts of the randomness of \drrtstar in their success rates.
+% The lazy iterative variants show the robust scalability. 
+Random split performs the worst since it is unlikely to chance upon valid motion plans. Single shot exhaustive and \milp scale poorly because of expensive motion planning.
+Interestingly, motion planning infeasibility reduces the size of the exhaustive search tree.
+The solution costs \textit{(middle)} substantiate benefits of the use of two arms. The computation times \textit{(bottom)} again show the scalability of \algo, even compared to random split.
+% In terms of cost. MILP scales to more objects but the computational overhead is more than \algo. Dual-arm solutions are significantly better than single arm.
+
 \tase{
 \subsection{Smoothing}
+\label{sec:smoothing}
 
-The result of the velocity tuning over the solution trajectories for the individual arms as a post-processing step is shown in Fig \ref{fig:smoothing}.
+The result of the velocity tuning over the solution trajectories for the individual arms as a post-processing step is shown in Fig~\ref{fig:smoothing}.
 The objective is to minimize any waits that might be a by-product of the synchronization.
@@
 Most of the improvement as a percentage of the original solution duration is not too high.
-On top of that, the time taken to smooth the solutions for \algo (overlaid on Fig \ref{fig:smoothing}) shows that it is often not beneficial.
+On top of that, the time taken to smooth the solutions for \algo (overlaid on Fig~\ref{fig:smoothing}) shows that the trade-off is sometimes not beneficial.
 In their largest problem instances the \kuka spent $ 0.44s $ of smoothing time to save $ 3.23s $ off the solution duration, while the picker spent $  9.84s $ to save $ 0.54s $.
 
-\begin{figure}[h]
+\begin{figure}[t]
 	\centering	
@@
 	\includegraphics[width=0.48\textwidth]{figures/results/kuka_smoothing}
-	\caption{Smoothed solution improvement as a percentage of the original synchronized solution duration, and the time taken to smooth solutions obtained from \algo in seconds.}
+	\caption{ \tase{Smoothed solution improvement as a percentage of the original synchronized solution duration, and the time taken to smooth solutions obtained from \algo in seconds. } }
 	\label{fig:smoothing}
@@
 
-This indicates that among the class of synchronized solutions discovered by the proposed algorithms, the analogous asynchronous variants do not seem to be drastically better.
+This indicates that among the class of synchronized solutions discovered by the proposed algorithms, the asynchronous, smoothed variants do not seem to be drastically better.
 Moreover, smoothing does not improve the maximum of distances cost measure, but only reduces the solution duration.
-The theoretical bounds in the simple planar setups agree with the results in that the synchronization does not degrade the benefits of using 2 arms too much.
+
+% The theoretical bounds in the simple planar setups agree with the results in that the synchronization does not degrade the benefits of using 2 arms too much.
 It should be pointed out though that it needs to be studied further, whether these trends would hold for a class of algorithms that can solve the asynchronous dual-arm rearrangement problem in general setups.
@@
 
-\subsection{Discrete Reachability Benchmark}
+\subsection{Reachability Benchmark}
+\label{sec:reachability}
 
-In this benchmark, two Kuka arms are placed opposite a target arrangement table, as shown in Fig \ref{fig:reachability_benchmark}.
+In this benchmark, two Kuka arms are placed opposite a target arrangement table, as shown in Fig~\ref{fig:reachability_benchmark}.
 The initial poses of the objects on either side of the arms in a way that the initial poses are reachable by only one of the arms.
 The purpose of this study is to see the effects of general divided workspaces where both the initial and target poses are not in the region of common reachability of the arms.
-This somewhat simplifies the problem of coordinating the two arms because interactions are limited to the target poses of the objects.
+It should be noted that a single arm solution does not exist for this benchmark.
 
@@
 	\includegraphics[width=0.48\textwidth]{figures/results/5_kuka_lazy_ms_time.png}
-	\caption{The reachability benchmark}
+	\caption{ \tase{ The reachability benchmark with the initial poses of the objects lying in disjoint parts of the workspace(tables on the right and left) that are only reachable by one of the arms.
+The objective is to transfer the objects to the middle table.
+} }
 	\label{fig:reachability_benchmark}
-	%     \vspace{-.3in}
+	    \vspace{-.2in}
 \end{figure}
@@
 Expectedly, the naive random split tends to erroneously assign unreachable objects to arms.
-It should be noted that a single arm solution does not exist for this benchmark.
-The data reported for the lazy variants, shows that our proposed method manages to maintain scalability and robustness even in such scenarios and moreover, shows the benefits of dual-arm rearrangement.
+The data reported for the lazy variants, shows that our proposed method manages to maintain scalability and robustness even in such scenarios and moreover, further highlights the benefits of dual-arm rearrangement.
 

### 2020-12-17 biography.tex
Updates from Overleaf

% \begin{wrapfigure}{l}{0.2\textwidth}
%   \begin{center}
%   \vspace{-0.02in}
%     \includegraphics[width=0.19\textwidth]{figures/biography/rahul_shome.jpeg}
%   \hspace{-0.02in}
%   \vspace{-0.02in}
%   \end{center}
% \end{wrapfigure}
% \noindent\textbf{Rahul Shome} is pursuing his Ph.D. in Computer
% Science at Rutgers University, and working with Prof. Kostas Bekris at
% the PRACSYS Lab. His research interests include multi-robot motion
% planning, manipulation planning, and problems in rearrangement task
% planning.  
% \\

% \begin{wrapfigure}{l}{0.2\textwidth}
%   \begin{center}
%   \vspace{-0.02in}
%     \includegraphics[width=0.19\textwidth]{figures/biography/kiril_solovey.PNG}
%   \hspace{-0.02in}
%   \vspace{-0.02in}
%   \end{center}
% \end{wrapfigure}
% \noindent\textbf{Kiril Solovey} is a Postdoctoral Scholar at the Autonomous Systems Lab, Department of Aeronautics and Astronautics, Stanford University, hosted by Prof. Marco Pavone. His research focuses on algorithmic aspects of robotics. He is particularly interested in the design and analysis of techniques for robot motion planning, multi-robot systems, and autonomous mobility-on-demand. He is supported by the Fulbright Scholars Program. Prior to Stanford, He was a Ph.D. student at Tel Aviv University working with Prof. Dan Halperin in the Computational Geometry Lab. He was supported by the Clore Israel Foundation.\\

% \begin{wrapfigure}{l}{0.2\textwidth}
%   \begin{center}
%   \vspace{-0.02in}
%     \includegraphics[width=0.19\textwidth]{figures/biography/yu-eps-converted-to.pdf}
%   \hspace{-0.02in}
%   \vspace{-0.02in}
%   \end{center}
% \end{wrapfigure}
% \noindent\textbf{Jingjin Yu} is an Assistant Professor in the Department of Computer Science at Rutgers, the State University of New Jersey. He received his B.S. degree from the University of Science and Technology of China in 1998. He holds M.S. degrees in Chemistry (Univ. Chicago, 2000), Mathematics (Univ. Illinois at Chicago, 2001), and Computer Science (Univ. Illinois at Urbana-Champaign, 2010). He obtained his Ph.D. degree in Electrical and Computer Engineering from the University of Illinois at Urbana-Champaign in 2013, where he briefly stayed as a postdoctoral researcher. He was a postdoctoral researcher at the Massachusetts Institute of Technology from 2013 to 2015 with a joint appointment at Boston University from 2013 to 2014. He is broadly interested in the areas of robotics and control, focusing on issues related to computational complexity and the design of efficient algorithms with provable guarantees. He is a Siebel Scholar and a recipient of the NSF CAREER Award.\\ 
% \\ \\ \\ \\ \\ \\ \\

% \begin{wrapfigure}{l}{0.2\textwidth}
%   \begin{center}
%   \vspace{-0.02in}
%   \noindent \includegraphics[width=0.19\textwidth]{figures/biography/kostas_bekris.jpg}
%   \hspace{-0.02in}
%   \vspace{-0.02in}
%   \end{center}
% \end{wrapfigure}
% \noindent\textbf{Kostas Bekris} is an Associate Professor in the
% Computer Science department of Rutgers, the State University of New
% Jersey. He received his MS and PhD degrees in Computer Science from
% Rice University in 2004 and 2008 respectively. He was an Assistant
% Professor at the Department of Computer Science and Engineering at the
% University of Nevada, Reno from 2008 to 2012. He is the recipient of a
% NASA Early Career Faculty award and his research has been supported by
% NSF, NASA, DHS and the DoD. His research interests include planning
% and coordination of robots, especially for systems with many degrees
% of freedom and significant dynamics, as well as applications to
% robotic manipulation, planetary exploration, cyber-physical systems
% and physically-realistic virtual agents. \\

% \begin{wrapfigure}{l}{0.2\textwidth}
%   \begin{center}
%   \vspace{-0.02in}
%     \includegraphics[width=0.19\textwidth]{figures/biography/Danny.jpg}
%   \hspace{-0.02in}
%   \vspace{-0.02in}
%   \end{center}
% \end{wrapfigure}
% \noindent\textbf{Dan Halperin} received his Ph.D. in Computer Science from Tel Aviv
% University. He then spent three years at the Computer Science
% Robotics Laboratory at Stanford University. In 1996 he joined the
% School of Computer Science at Tel Aviv University, where he is
% currently a full professor. Halperin's main field of research is
% Computational Geometry and its Applications. A major focus of his
% work has been in research and development of robust geometric
% software, principally as part of the CGAL project and library. The
% application areas he is interested in include robotics, automated
% manufacturing, algorithmic motion planning and 3D printing.
% http://acg.cs.tau.ac.il/danhalperin\\

%\begin{figure}[h]

%\begin{wrapfigure}{l}{0.25\textwidth}
%\begin{center}
%\includegraphics[width=0.24\textwidth]{figures/biography/rahul_shome.jpeg}
%\end{center}
%\end{wrapfigure} \par 
\vspace{0.3in}
\parpic{\includegraphics[width=0.2\textwidth]{figures/biography/rahul_shome.jpeg}}
\noindent {\bf Rahul Shome} is pursuing his Ph.D. in Computer
Science at Rutgers University. He has been working with Prof. Kostas Bekris at
the PRACSYS Lab. His research interests include multi-robot motion
planning, manipulation planning, warehouse automation, and problems in rearrangement task planning.

\vspace{0.2in}
%\begin{wrapfigure}{l}{0.2\textwidth}
%  \centering
  % \vspace{-0.02in}
%    \includegraphics[width=0.19\textwidth]{figures/biography/kiril_solovey.PNG}
  % \hspace{-0.02in}
  % \vspace{-0.02in}
%\end{wrapfigure}

\parpic{\includegraphics[width=0.2\textwidth]{figures/biography/kiril_solovey.PNG}}
\noindent {\bf Kiril Solovey} is a Postdoctoral Scholar at the Autonomous Systems Lab, Department of Aeronautics and Astronautics, Stanford University, hosted by Prof. Marco Pavone. His research focuses on algorithmic aspects of robotics. He is particularly interested in the design and analysis of techniques for robot motion planning, multi-robot systems, and autonomous mobility-on-demand. He is supported by the Fulbright Scholars Program. Prior to Stanford, He was a Ph.D. student at Tel Aviv University working with Prof. Dan Halperin in the Computational Geometry Lab. He was supported by the Clore Israel Foundation.

\vspace{0.2in}

\parpic{\includegraphics[width=0.2\textwidth]{figures/biography/yu-eps-converted-to.pdf}}
\noindent {\bf Jingjin Yu} is an Assistant Professor in the Department of Computer Science at Rutgers, the State University of New Jersey. He received his B.S. degree from the University of Science and Technology of China in 1998. He holds M.S. degrees in Chemistry (Univ. Chicago, 2000), Mathematics (Univ. Illinois at Chicago, 2001), and Computer Science (Univ. Illinois at Urbana-Champaign, 2010). He obtained his Ph.D. degree in Electrical and Computer Engineering from the University of Illinois at Urbana-Champaign in 2013, where he briefly stayed as a postdoctoral researcher. He was a postdoctoral researcher at the Massachusetts Institute of Technology from 2013 to 2015 with a joint appointment at Boston University from 2013 to 2014. He is broadly interested in the areas of robotics and control, focusing on issues related to computational complexity and the design of efficient algorithms with provable guarantees. He is a Siebel Scholar and a recipient of the NSF CAREER Award.

\vspace{0.2in}

\parpic{\includegraphics[width=0.2\textwidth]{figures/biography/kostas_bekris.jpg}}
\noindent {\bf Kostas Bekris} is an Associate Professor in the
Computer Science department of Rutgers University. He received his MS and PhD degrees in Computer Science from Rice University in 2004 and 2008 respectively. He was an Assistant
Professor at the Department of Computer Science and Engineering at the
University of Nevada, Reno from 2008 to 2012. He is the recipient of a
NASA Early Career Faculty award and his research has been supported by
NSF, NASA, DHS and the DoD. His research interests include planning
and coordination of robots, especially for systems with many degrees
of freedom and significant dynamics, as well as applications to
robot manipulation, planetary exploration, cyber-physical systems
and physically-realistic virtual agents.

\vspace{0.2in}
\parpic{\includegraphics[width=0.2\textwidth]{figures/biography/Danny.jpg}}
\noindent {\bf Dan Halperin} received his Ph.D. in Computer Science from Tel Aviv University. He then spent three years at the Computer Science
Robotics Laboratory at Stanford University. In 1996 he joined the
School of Computer Science at Tel Aviv University, where he is
currently a full professor. Halperin's main field of research is
Computational Geometry and its Applications. A major focus of his
work has been in research and development of robust geometric
software, principally as part of the CGAL project and library. The
application areas he is interested in include robotics, automated
manufacturing, algorithmic motion planning and 3D printing.
http://acg.cs.tau.ac.il/danhalperin\\

### 2020-12-18 response.tex
changes

% \documentclass{llncs}

\documentclass[journal]{IEEEtran}
%\usepackage{makeidx}  % allows for indexgeneration

\usepackage{amsmath,amsfonts,amssymb,mathrsfs}
\usepackage{graphicx}
\usepackage{psfrag,graphicx,epsfig,epsf}
\usepackage[ruled,linesnumbered, noend]{algorithm2e}
\usepackage{fancyhdr}
\usepackage{subfigure}
\usepackage{mathtools}
\usepackage{url}
\usepackage{color}
\usepackage{verbatim}
\usepackage{xspace}
\usepackage{amsmath}

\usepackage{wrapfig}

\usepackage{picins}

\DeclareMathOperator*{\argmin}{arg\,min}

\newcommand\permu[2][^n]{\prescript{#1\mkern-2.5mu}{}P_{#2}}
\newcommand\combi[2][^n]{\prescript{#1\mkern-0.5mu}{}C_{#2}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%% Theorems        %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\usepackage{amsthm}
%\newtheorem{theorem}{Theorem}
%\newtheorem{definition}[theorem]{Definition}
%\newtheorem{proposition}[theorem]{Proposition}
%\newtheorem{corollary}[theorem]{Corollary}
%\newtheorem{axiom}[theorem]{Axiom}
%\newtheorem{lemma}[theorem]{Lemma}
%\newtheorem{problem}{Problem}
%\newtheorem{prob}[theorem]{Problem}
%\newtheorem{conjecture}[theorem]{Conjecture}
%\newtheorem{obj}[theorem]{Objective}
%\newtheorem{prop}[theorem]{Property}
%\newtheorem{schedule}[theorem]{Schedule}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%% Figure resizing          %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% The macros are useful when we need to change the document textwidth.

%%This would resize everything within it to \textwidth
%\def\resizeall{\resizebox{\textwidth}{!}}
%
%%This would make a box around the item and center it 
%\def\resizetotextwidth{\makebox[\textwidth]}

\begin{document}

	\title{Fast, High-Quality Two-Arm Rearrangement in Synchronous, Monotone Tabletop Setups: Response}
	%\titlerunning{Fast Methods for Synchronized Tabletop Dual-Arm Rearragement}
	\author{Rahul Shome \and Kiril Solovey \and Jingjin Yu \and Kostas Bekris \and Dan Halperin}
	%\authorrunning{Shome et al.}
	% \institute{$^1$Rutgers University, NJ, USA and $^2$Tel Aviv University, Israel}

	\onecolumn

	\maketitle
	\input{notation}

	The authors would like to thank the reviewers for the helpful comments. This copy of the manuscript includes all the significant changes in the draft highlighted in blue to make it easier to track against the suggested edits. The authors also appreciate the efforts undertaken by the guest editors in their careful consideration of the reviewers' suggestions and their overall recommendation. We hope the changes are sufficient.
	In this response document the specific review points are quoted inline and our responses explained and highlighted.

	\newenvironment{partt}{\ttfamily}{\par}
	\newcommand{\edits}[1]{{\color{blue}#1}}

	\medskip

	\begin{partt}{ T-ASE-2019-525

			Lead Guest Editor
			Comments to the Author:
			Reviewer \#1 is very positive about the paper, and has no changes requested.  
		}
	\end{partt}

	\edits{The authors have addressed all the granular suggestions from Reviewer 1.}

	\begin{partt}
		Reviewer \#2 raises several criticisms.  The first relates to terminology. In particular, the reviewer feels that this paper’s use of "dual-arm rearrangement" implies cooperative manipulation by the two arms, rather than two arms working essentially independently once their tasks have been scheduled. This is a minor issue, but the Guest Editors encourage you to clarify, perhaps even by modifying the title of the paper, that this is not a paper about dual-arm cooperative manipulation. (Alternatively, if this terminology is in current use, you could provide a citation or two to the seminal papers in which definitions are given.)  
	\end{partt}
	\edits{The title and references to dual-arm rearrangement have been updated to two-arm rearrangement. Text has also been added to the introduction to clarify that we address object rearrangement problems using two robotic arms. In order to avoid giving the impression of cooperative manipulation the authors include the explicit reference to object rearrangement, the discussions of related literature, and problem formulation tying only single objects to each arm at a time. The authors appreciate the raising of this concern so that readers do not get any misleading impression from the text. Hopefully this is sufficient to avoid confusion about the problem domain. }

	\begin{partt}
		The second relates to the three assumptions posited in Section III. To address these concerns, the revised manuscript should justify the assumptions (e.g., by  explaining how/why the do not significantly compromise the efficacy and scope of your method, or by showing/explaining why these assumptions are generally satisfied in practice), or the authors should carefully discuss the implications should these assumptions not be met in practice (see also Reviewer \#3's comments).
	\end{partt}

	\edits{In addition to an existing paragraph that was previously a note on the assumptions, an additional discussion on the scope and limitations derived from the problem definition has been added.}

	\begin{partt}
		The remaining criticisms raised in this review relate to clarity, and the Guest Editors encourage you to take these seriously when revising your manuscript.
	\end{partt}

	\edits{The authors have added clarifying text wherever the reviewers have raised doubts or concerns.}

	\begin{partt}
		Reviewer \#3 raises two concerns: lack of adequate discussion of the limitations of the method, and the experimental setup. For the former, there is some overlap with the concerns of Reviewer \#2. A thorough, careful discussion of these issues is essential for your revised manuscript. 
	\end{partt}
	\edits{In addition to the discussion on the scope and limitations of our problem formulation, specific points raised by Reviewer 3 have also been addressed and pointed out inline with the review.}

	\begin{partt}
		For the latter concern, Reviewer \#3 questions the value of using a random assignment strategy as the base case, and proposes alternatives that could give more meaningful comparisons. The Guest Editors encourage the authors to investigate these, since the overhead for doing so should be minimal.
	\end{partt}
	\edits{A note about heuristic strategies has been added in the evaluation section. The argument there is that the regions of common reachability which are a focus of the benchmarks (even for the placement region for the reachability benchmark), random problem instances will not admit a clear workspace partitioning. The results indicate that committing to a single choice of object-to-arm assignments hedges the solution feasibility to the coordinated motion planning over that specific sequence of assignments and causes a drop in success rates. In the work we have proposed a lazy variant that repeatedly evaluates alternative solutions till a feasible one is found. This leads to a drastic improvement in success rates, especially for the Kuka arms. A deterministic hand-crafter heuristic will not be amenable to this framework. As such we choose to focus on methods with theoretical optimality bounds, and a naive random baseline.}

	\medskip
	\medskip

	\begin{partt}
		Reviewer's comments to author:

		Reviewer: 1

		Comments to the Authors

		Please comment on Major Contribution of the Paper, Organization and Style, Technical Accuracy, Presentation and Adequacy of Citations (List possible additions if needed).
		The paper proposes a method for arrangement of objects on a tabletop environment using 2 manipulator arms and argue its benefit over use of a single arm. The objective of the method is to focus on the underlying combinatorial aspect of the problem.The proposed method is subdivided into two sub-problem : one to find an optimal assignment of object to the arms and then to optimize the transit cost. The authors also provide a MILP formulation of the problem. The experiments show that the proposed method is better than MILP, random splitting (for assignment) and exhaustive search with respect to succes ratio, path length travelled and computation time.

		The paper is well written and clearly states the added contribution of this version over the conference paper (ref. 2). Most of the added contribution is in additional experiments and added details in the bounding cost proof. However, following are some areas of improvements:-

	\end{partt}
	\edits{ 
		The authors would like to thank the reviewer for the kind words.
	}
	\begin{partt}	
		- Note about the synchronicity assumption needs to be expanded with respect to reachabilty: The problem formulation assumes a balanced or nearly balanced distribution of the objects to two arms which enforces that atleast half of the objects are reachable by each arm for the proofs in Sec VII.
	\end{partt}
	\edits{ 
		This can be handled by NOACT assignments and was mentioned in the text. For clarity another note has been added to evaluation about the use of NOACT object arm assignments to deal with unbalanced cases. 
	}
	\begin{partt}

		- More insight required for the statements in Sec VII :
		-- "Clearly, the per robot additional (makespan or distance) cost is bounded by some function f(k,r)c\_t" in Theorem 8 proof : What is the nature of the f(k,r)? Is it based on the bound on the perimeter of the bounded region in ref 49?
	\end{partt}
	\edits{ 
		The reviewer is correct in this observation. It indeed follows from previous work [49] and for the disk robot case depend on the perimeter.
	}
	\begin{partt}
		-- Why is the statement about (n+1)\^2 potential line segment intersection is added in the proof of Corollary 9? 2n potential collision can be accounted by 4 potential collision for each pair and as there are n/2 pairs hence 2n potential collision.
	\end{partt}
	\edits{ 
		The extraneous statement has been removed for clarity.
	}
	\begin{partt}

		- Details about the experimental setup is required such as : size of the workspace with respect to the size of the objects and the start and goal locations (atleast for one instance) in both the domains (a labelled figure will be useful). 
	\end{partt}
	\edits{ 
		The dimensions of the Kuka workspace has been added to the evaluation section.
	}
	\begin{partt}

		- It will be interesting to show how the proposed system handles unbalanced number of objects in experiments. Unbalanced not just in odd number of objects but also with respect to unbalance in number with respect to reachability (experiments in Sec. VIII D).
	\end{partt}
	\edits{ 
		NOACT object assignments have been mentioned in Section III, VI, and as a note in evaluation to address such scenarios. This requires no change in our algorithm.
	}
	\begin{partt}

		- Also addition of static obstacles or experiments inspired by industrial setups (where the target locations are in a box or tightly spaced) will be interesting.
	\end{partt}
	\edits{ 
		This indeed poses interesting future domains and realistic grasping and cluttered motivating scenarios have included in the discussion.
	}
	\begin{partt}

		- Please label or index the subfigures in the multifigures as a, b, c ... or 1, 2, 3 instead of top , bottom, etc. If considering top, bottom indexing please state it next to the sub-figures and not just in the main caption.
	\end{partt}
	\edits{ 
		For compactness the authors have chosen to keep the arrangement of the plots unchanged for now. 
	}
	\begin{partt}

		- Section III "Every rearrangement ..." should be "every rearrangement ..." as it is in the middle of the sentence.
	\end{partt}
	\edits{ 
		Done.
	}
	\begin{partt}

		- Section III paragraph "Note on Assumptions" there is a trailing spaces before the sentence  "Objects do not need ..."
	\end{partt}
	\edits{ 
		Done.
	}
	\begin{partt}

		- Missing authors in reference 37
	\end{partt}
	\edits{ 
		This was caused by the bib style for repeated author lists.
	}

	\begin{partt}
		Reviewer: 2

		Comments to the Authors

		Please comment on Major Contribution of the Paper, Organization and Style, Technical Accuracy, Presentation and Adequacy of Citations (List possible additions if needed).
		The manuscript addresses the problem of rearranging objects in a tabletop scenario using two agents. Among the multiple challenges involved in such scenario, the focus of the manuscript is on the assignment and scheduling of objects-to-agents actions. This frustrates the first impression given by the title where it is expected a two-arm co-operative solution to the problem.
	\end{partt}
	\edits{ 
		The author appreciates the reviewer's feedback. The authors have clarified sections of the manuscript to alleviate some of the miscommunication that led to most of the criticisms laid by the reviewer. The authors feel that the changes will be enough to avoid the same with an interested reader.  The work does not solely deal with object assignment and scheduling and an explicit not pointing out the same has been added to the introduction.
	}

	\begin{partt}
		Indeed, this is one major drawback of the work which should be addressed at first. Robotics, particularly, co-operative manipulation literature, refers to dual-arm synchronous motion as the action of two arms moving in synchrony to achieve a given common manipulation task with/without a shared load, e.g., moving an object, manipulating a steering-wheel, a broom, etc. The scenario addressed in the manuscript refers to simultaneous/parallel asynchronous manipulation in a shared and semi-structured environment.  
	\end{partt}
	\edits{ 
		In order to avoid this confusion references to dual-arm rearrangement have been changed to two-arm rearrangement, and the text clarified.
	}

	\begin{partt}  
		Another important point to be addressed and improved is the large set of assumptions taken. For instance, assumption 1. monotonicity does simplify the problem, yet it limits the range of existing solutions and if one is to take a realistic cluttered scenario, one object is very likely to be placed within Agoal.  Similarly, Assumption 3 is a very strong assumption, when using general serial-kinematic manipulators. Assuming that transfers will not influence future motions, that is, their costs do not depend on the order in which objects are moved, may not be realistic, especially in the envisioned cluttered scenario. Since this is one of the main assumptions required for assessing the costs in the resulting graph, it would be better if the authors focused on the scheduling of delta robots.
		Finally, since the focus of the work is mostly on scheduling and assignment with constrained conditions, there is no reason not to make the solution as generic as possible, e.g., including multi-agents should not be a challenge.  
	\end{partt}
	\edits{ 
		A discussion of the scope and limitations of the assumptions has been added. The authors disagree with the reviewer's concerns about scheduling and assignment since the current method deals with planned solutions that need to avoid collisions between robot geometries and obstacles.
	}

	\begin{partt}

		With regard to the presentation, the manuscript is lengthy and hard to follow.
		In the Introduction Section, both observations are fairly too generic and should not be taken as observations since it is not true that, for instance, a k-arm solution cannot be worse than an optimal single-arm solution. First due to the lack of definition of optimality to this point, second by the lack of assumptions where this scenario is true. Take the trajectory cost, for example, if we assume possible collisions due to the initial pose of one arm, even if such arm stays static, the second arm will have to modify its trajectory accordingly. Naturally, this is just a specific example, but it should serve as a point to avoid generalizations.  
	\end{partt}
	\edits{ 
		A note has been added about the availability of sufficient space to admit k arms. There was already text explaining how other arms move out of the workspace containing the rearrangement problem for an analogous single-arm solution.
	}

	\begin{partt}
		In addition, the following remarks should also be addressed:
		* The objects pose belong to the set SE(2), which is more precise than a subset SE(3);
	\end{partt}
	\edits{ 
		The authors have maintained the SE(3) notation because that was used for all the benchmarks to compute and reason about grasps. Even the simple picker benchmarks modeled delta robots that existed in a 3D workspace.
	}

	\begin{partt}
		* In the subset R\^d, the value of d is never defined;
	\end{partt}
	\edits{ 
		This has been clarified as the dimension of the Euclidean space.
	}

	\begin{partt}
		* In the transfers and moves definition, the variable o\_i\^k is presented for the first time to refer to the object i within the robot k. Yet, the dual-arm path takes \\pi\_i\^1 and \\pi\_i\^2 as input which naturally refers to the manipulation of two distinguish objects, yet since \\pi\_i\^1 and \\pi\_i\^2 have the same subindex, it implicitly implies the same object o\_i being manipulated by both robots. In Eq. 3, on the other hand, it is presented the o\_j. The lack of consistency makes it harder to follow the manuscript. In Eq. 3, the length \\ell is also presented for the first time. And, it is not clear how it connects to i,j;
	\end{partt}
	\edits{ 
		A footnote to better explain the indices has been added.
	}

	\begin{partt}
		* The set of optimization costs and constraints in pg. 5 should not be defined using letters. Really, there is no reason to refer to Eqs. Letters and not follow the standard approach with numbers (and perhaps, subequations if needed);
	\end{partt}
	\edits{ 
		The authors see this as a self-contained set of MILP constraints and choose to distinguish the same.
	}

	\begin{partt}
		* Lemma 1 appears as a reference in pg. 5 without being defined.  Then, we have Lemma 4 without 2 and 3.
	\end{partt}
	\edits{ 
		The authors thank the reviewer for the careful read-through. This was an error in the theorem counter on our part. This has been fixed.
	}

	\begin{partt}
		* Figs. 7 and 8 need further discussion and description.  For instance, what is the horizontal bar in the computation time? Why milp performs so badly in terms of computation time the picker (worst than random) and better in the Kuka lazy example?  
	\end{partt}
	\edits{ 
		The authors believe the reviewer is referring to the lazy behavior. This is explained in the evaluation as an effect of increased infeasibility failures for random.
	}

	\begin{partt}
		* It would be interesting to compare the computational time from the proposed parallel/simultaneous solution compared to the smoothing strategy (compares the results in Fig. 8 with Fig. 9 in terms of trajectory and, most important, time complexity).
	\end{partt}
	\edits{ 
		The timings are mentioned within the text.
	}

	\begin{partt}
		* Finally, during most of the manuscript, it was also not clear how collision avoidance was addressed.  This should be better clarified in the problem definition.
	\end{partt}
	\edits{ 
		The subsection on Integration with Motion Planning, and the lazy algorithm's calls to the motion planner discuss the module that is burdened with motion planning and collision checking. 
	}

	\begin{partt}

		Overall the manuscript presents an interesting solution for the scheduling problem of multi(two)-agents. There are contributions to the area, but the text is rather lengthy and focused on a two-arm manipulation problem which is not addressed or important to the problem posed in the manuscript definition. In my opinion, the manuscript can be considerably improved taking care to better describe the problem and the strengths of the proposed solution, yet it is not sufficient contribution for a T-ASE publication.  
	\end{partt}
	\edits{ 
		The authors hope the changes are sufficient to address the reviewer's concerns.
	}

	\begin{partt}
		Reviewer: 3

		Comments to the Authors

		Please comment on Major Contribution of the Paper, Organization and Style, Technical Accuracy, Presentation and Adequacy of Citations (List possible additions if needed).
		Summary:

		This work develops a planner for rearranging objects in the plane using two manipulator arms.  Each arm works independently and simultaneously (e.g., no collaborative object placements).  Their algorithm optimizes first the cost of object transfers (making object assignments to each manipulator arm) and then the cost of manipulator movements between one object’s goal and another object’s start (reducing manipulator travel time).  They show improved performance over a single manipulator, over random object-manipulator assignments, and over a mix-integer solution.  This manuscript is an extended version of their WAFR publication.

		Recommendation:
		This work tackles an important problem that is becoming increasingly relevant as automation increases.  Specifically this addresses the automated packing problem where manipulator arms are used to rearrange and pack objects.  They first concentrate on the planar application where all objects start/goals lie in the plane and no objects are occluded/overlapping any other.  They assume an overhead grasping configuration for the robot arms.  The manuscript is well-written, clearly describing their work and experimental results.  With respect to their WAFR publication, they provide more detail in the method explanation, additional theoretical analysis, and some results with smoothing.
	\end{partt}
	\edits{ 
		The authors appreciate the reviewer's feedback. 
	}

	\begin{partt}

		There are a few items that need improvement:

		- Discussion on limitations - The authors describe the limiting assumptions made (planar, non-overlapping, completely graspable and transferable by single arm, empty workspace other than objects to rearrange, etc).  However, they should discuss more explicitly the situations where this approach will not (yet) work.  For example, they assume a planar environment and test in open workspaces which is not applicable to many packing scenarios that must stack items, pack filling, and navigate around box/container walls.  They also assume each manipulator can grasp and maneuver every object on its own.  This limits the size and shape of objects grasped without allowing for collaborative maneuvers.  Finally, they assume objects are only moved once, but certain scenarios are not solvable under these conditions (e.g., puzzle/tunnel setups where objects block each others start/goals).  This should be made explicit in the text.
	\end{partt}
	\edits{ 
		The concern about the discussion about the problem domain and limitations has been explicitly within a broader note on our assumptions. The reviewers' observations are all correct.
	}

	\begin{partt}

		- Experimental setup - The authors compare their method to randomly assigning objects to arms, but this approach will always yield poor results.  Instead, they should compare to something more reasonable such as splitting objects based on start proximity.  For example, they can divide the workspace into two halves along the plane that splits the manipulator bases.  This would yield much more reasonable results to compare against and be just as easy to compute as a random assignment.  The results would be more compelling if they varied the object size and geometry as often items to be packed are not identical (and nearly the size of the end effector so their collision status beyond the manipulator is not significant).

	\end{partt}
	\edits{ 
		A note about heuristics has been added in the evaluation to address this concern. Because of the benefits in feasibility obtained from repeated invocations within our proposed lazy framework, a deterministic hand-crafted heuristic has been avoided here. The authors do recognize that this is an important focus for practitioners and can form motivation for learning more effective ways to incorporate such heuristics about the coordinated problem into task planning. Richer classes of object geometries have been included as motivated future investigation domains in the discussion. 
	}

\end{document}

### 2020-12-18 00_abstract.tex
Updates from Overleaf
changes

@@
 efficiency but introduces new computational challenges. This paper
-studies the structure of dual-arm rearrangement for synchronous,
+studies the problem structure of \revisions{object rearrangement using two arms in} synchronous,
 monotone tabletop setups and develops an optimal mixed integer model. It then
@@
 arms and indicate that synchronous execution, in which the two arms perform together either transfers or moves, introduces only a small
-overhead.  Experiments support these points and show that the
+overhead.  Experiments support these claims and show that the
 scalable method can quickly compute solutions close to the optimal for

### 2020-12-18 01_introduction.tex
changes

@@
 setups \cite{193}.
-The proliferation of robot arms, however, including dual-arm setups, implies that industrial settings can utilize multiple robots in the same workspace (Fig~\ref{fig:two_arms}).
-This work explores a) the benefits of coordinated dual-arm rearrangement versus single-arm, b) the combinatorial challenges involved and c) computationally efficient, high-quality and scalable methods.
+The proliferation of robot arms, however, including \dual-arm setups, implies that industrial settings can utilize multiple robots in the same workspace (Fig~\ref{fig:two_arms}).
+This work explores a) the benefits and trade-offs of \revisions{using two arms for solving object rearrangement instead of a} single-arm, b) the combinatorial challenges involved and c) computationally efficient, high-quality and scalable methods.
 
@@
 
-A major motivation for this work is that the coordinated use of multiple arms can
-result in significant improvements in efficiency. This arises from the following argument.
+A major motivation for this work is that the coordinated use of multiple arms \revisions{to move multiple objects at the same time} can
+result in significant improvements in efficiency \revisions{of object rearrangement solutions}. This arises from the following argument.
 
@@
 % 	\vspace{-0.1in}
-	\caption{Example of dual-arm setups that can utilize
+	\caption{\Dual-arm setups that can utilize
 	algorithms proposed in this work.}
@@
 let one of the arms carry out the best single arm solution while the 
-other remains outside the workspace. More generally:
+other remains outside the workspace. \revisions{This means whenever there is enough available space for $k$ arms, it can be said:}
 
@@
 The above observations motivate the development of scalable algorithmic
-tools for such dual-arm rearrangement instances. This work considers
+tools for such \dual-arm rearrangement instances. This work considers
 certain relaxations to achieve this objective. In particular,
@@
 
+\revisions{It should be noted here that the solutions presented in this paper go beyond purely reasoning about task allocation and scheduling of objects to robots.
+The \dual-arm object rearrangement solution needs to consider geometric interactions and collisions between robots and obstacles through coordinated motion planning.
+Information about these real-world interactions need to be considered to yield solutions that are ultimately valid and collision-free.}
+
 The first contribution is the study of the combinatorial structure of
-synchronous, monotone dual-arm rearrangement. Then, a mixed integer linear programming (\milp) model is
+synchronous, monotone \dual-arm rearrangement. Then, a mixed integer linear programming (\milp) model is
 proposed that achieves optimal coordinated solutions in this domain.
-The proposed efficient algorithm {\tt Tour\_Over\_Matching} (\algo) significantly improves in scalability. \algo\ first optimizes the
+The proposed efficient algorithm {\tt Tour Over Matching} (\algo) significantly improves in scalability. \algo\ first optimizes the
 cost of object transfers and assigns objects to the two arms by
@@
 Specifically, the result describing the asymptotic cost bound for asynchronous operation has been extended to the $k$-arm case.
-Additionally, a more detailed proof is provided for the asymptotic cost bound estimate in the case of synchronized dual-arm operation.
+Additionally, a more detailed proof is provided for the asymptotic cost bound estimate in the case of synchronized \dual-arm operation.
 % 	\item New data (Section \ref{sec:smoothing}) is provided that study the effect of post-processing solutions so as to minimize delays introduced due to the synchronization assumption. 

### 2020-12-18 02_background.tex
changes

@@
 %\end{itemize}
-The current work dealing with dual-arm object rearrangement touches upon the challenging intersection of a variety of rich bodies of prior work.
+The current work dealing with \dual-arm object rearrangement touches upon the challenging intersection of a variety of rich bodies of prior work.
 It is closely related to multi-robot planning and coordination where a challenge is the high dimensionality of the configuration space.
@@
 %\textbf{The Traveling Salesman Problem}:
-In this work we leverage a connection between dual-arm rearrangement and two combinatorial problems: (1) optimal matching~\cite{edmonds1965maximum} and (2) TSP.
+In this work we leverage a connection between \dual-arm rearrangement and two combinatorial problems: (1) optimal matching~\cite{edmonds1965maximum} and (2) TSP.
 On the surface the problem seems closely related to multi-agent TSP.
@@
 Single-arm rearrangement solutions will also not be effective in this setting.
-The current work tries to bridge this gap and provide insights regarding the structure of dual-arm rearrangement.
+The current work tries to bridge this gap and provide insights regarding the structure of \dual-arm rearrangement.
 Under assumptions that enable this study, an efficient solution emerges for this problem.

### 2020-12-18 03_problem.tex
changes

@@
 Consider a planar surface and a set of $n$ rigid objects $ \objectset=\{ \object_1, \object_2 \cdots \object_n\}$  which can rest on the surface in stable poses $p_i \in \Pspace_i \subset SE(3)$.
-The arrangement space $ \Aspace = \Pspace_1 \times \Pspace_2 \ldots \times \Pspace_n $ is the Cartesian product of all $\Pspace_i$, where Every rearrangement $\arrangement \in \Aspace$ is an $n$-tuple $(\pose_1, \ldots, \pose_n)$.
+The arrangement space $ \Aspace = \Pspace_1 \times \Pspace_2 \ldots \times \Pspace_n $ is the Cartesian product of all $\Pspace_i$, where every rearrangement $\arrangement \in \Aspace$ is an $n$-tuple $(\pose_1, \ldots, \pose_n)$.
 In valid arrangements $ \Afree \subset \Aspace$, the objects are pairwise disjoint.
@@
 \end{figure}
-Two robot arms $\arm^1$ and $\arm^2$ can 
+Two robot arms \footnote{We shall use superscripts to denote arms, and subscripts to index into some sequence or data-structure dependent on context, unless stated otherwise.} $\arm^1$ and $\arm^2$ can
 % pick, raise above the surface and place the objects. 
@@
 % THE OLD SENTENCE$\cfree^k$ is the set of collision-free configurations for arm $ \arm^k $, where $ q^k \in \cfree^k %\subset \reals^d $ (while ignoring possible collisions with  objects or the other arm).
-$\cfree^k$ is the set of collision-free configurations for arm $\arm^k$ (while ignoring possible collisions with  objects or the other arm), and is assumed here to be a subset of $\reals^d $.
+$\cfree^k$ is the set of collision-free configurations for arm $\arm^k$ (while ignoring possible collisions with  objects or the other arm), and is assumed here to be a subset of \revisions{$d$-dimensional} $\reals^d $.
 A path for $\arm^k$ is denoted as $ \pi^k : [0,1] \rightarrow \cfree^k$ and includes picking and placing actions throughout the entire rearrangement process.
@@
 % \vspace{-.1in}
-{\definition [Optimal Dual-arm Rearrangement] Given arms $\arm^1$, $\arm^2$ and objects $\objectset$ to be moved from initial arrangement $ \ainit \in \Afree$ to target arrangement $ \atarget \in \Afree $, the optimal dual-arm rearrangement problem asks for a dual-arm path $D^* \in \mathcal{D}$, which optimizes a cost function, and solution paths belong to the valid configuration space.
-
-% \vspace{-.15in} 
-% \begin{equation}
-%  D^* =  (\pi^{*1}, \pi^{*2}) \ |\ \arrangement(\ainit, D^*) = \atarget \textrm{ and } \pi^{*i} \in \cfree^i(\pi^{*j}) \vspace{-.05in}
-% \label{eq:dualarm_constraint}
-% \end{equation}
-%  and optimizes a cost function: $D^* = \underset{ \forall D \in \mathcal{D}}{ \mathtt{argmin} } \ \cost(D).$}
-
-% \begin{align*}
-%  D^* =  (\pi^{*1}, \pi^{*2}) = \underset{ \forall D \in \mathcal{D}}{ \mathtt{argmin} }\ \cost(D) \numberthis\label{eq:dualarm_constraint} \\ 
-%  \ \textrm{such that} \ \arrangement(\ainit, D^*) = \atarget \textrm{ and,}\\ \pi^{*1} \in \cfree^1(\pi^{*2}), \pi^{*2} \in \cfree^2(\pi^{*1})  
-% \end{align*}
-%  and optimizes a cost function: $D^* =  .$}
-\vspace{-0.1in}
+{\definition [Optimal \Dual-arm Rearrangement] Given arms $\arm^1$, $\arm^2$ and objects $\objectset$ to be moved from initial arrangement $ \ainit \in \Afree$ to target arrangement $ \atarget \in \Afree $, the optimal dual-arm rearrangement problem asks for a dual-arm path $D^* \in \mathcal{D}$, which optimizes a cost function, and solution paths belong to the valid configuration space.
 \begin{align*}
@@
 \commentadd{
-\noindent \textbf{Note on Assumptions:} This work restricts the study to a class of monotone problems that relate to a range of industrial packing and stowing applications.
+\subsection{Discussion on Assumptions} This work restricts the study to a class of monotone problems that relate to a range of industrial packing and stowing applications.
 The monotonicity assumption is often used in manageable variants of well-studied problems~\cite{Wilson:1994fk,Halperin:2000uq}.
-A monotone solution also implies that every object's start and target is reachable by at least one arm.
-\cameraready{
-Objects do not need to be in the commonly reachable workspace as long as the problem is monotone and solvable.
+A monotone solution also implies that every object's start and target is reachable by at least one arm.\cameraready{Objects do not need to be in the commonly reachable workspace as long as the problem is monotone and solvable.
 Section~\ref{sec:integration} discusses a {\tt NO\_ACT} task that can deal with unbalanced object assignments between two arms.
@@
 }
+
+\revisions{
+	\textit{Scope and Limitations:} A variety of automation applications like packing, stowing, or sorting involve different singulated objects arriving at designated source regions, involving their rearrangement to a disjoint target region or container.
+Such automation applications also create semi-structured workspaces that guarantee that all objects of interest are easily graspable (top-down for planar surfaces).
+This class of problems is monotone since the source and target poses are disjoint, and \textit{no transfer will require an intermediate location}.
+In this case object non-interactivity essentially implies that the workspace is well-behaved enough to allow feasible single-arm motion plans between top-down reachable poses of the object.
+The current work addresses what we need to do go beyond single arm setups to effectively deploy two arms to speed up such an operation, and theoretically motivates the same.
+
+	The assumptions on the domain laid out in this work serve to identify the class of problems where our theoretical bounds will be close to the attained performance.
+\textit{The lazy variant proposed in this work is assured to iterate over all possible orderings of object-to-arm assignments, and take into account planning feasibility of the same.
+As such it is guaranteed to discover a solution as long as the \dual-arm rearrangement problem is monotone.} Admittedly, in domains where these assumptions are pathologically violated the theoretical and practical gains highlighted in this work will be compromised.
+The proposed method has limiting applicability to some interesting domains where objects are occluded, overlap, or lie in unstructured piles.
+Any non-monotonicity, i.e.
+problems that necessitate using an intermediate location, cannot be addressed by the current pipeline.
+These include puzzle-like or highly cluttered scenarios.
+}

### 2020-12-18 04_baseline.tex
changes

@@
 Prior work has applied these techniques for solving m-TSP \cite{rathinam2006matroid,friggstad2013multiple} and pickup-and-delivery problems \cite{coltin2014multi,savelsbergh1995general}, but viewed these problems in a decoupled manner.
-This work outlines an \milp formulation for the synchronized dual-arm rearrangement problem that reasons about coordination costs arising from arm interactions in a shared workspace.
+This work outlines an \milp formulation for the synchronized \dual-arm rearrangement problem that reasons about coordination costs arising from arm interactions in a shared workspace.
 

### 2020-12-18 05_approximation.tex
changes

@@
 \subsection{Importance of Transfers} In order to draw some insight, consider again the tabletop setup with a general cost measure of $c_t$ per unit distance.
-Lemma~\ref{l:k-arm-lower-bound} suggests that under certain conditions, there 
+Observation~\ref{l:k-arm-lower-bound} suggests that under certain conditions, there 
 may not be a meaningful bound on the performance ratio between a $k$-arm 
@@
 %\vspace{-0.2in}
-	\caption{ \tase{ \textit{(Top-left)} A dual-arm rearrangement problem.
+	\caption{ \tase{ \textit{(Top-left)} A \dual-arm rearrangement problem.
 \textit{(Top-middle)} Directed edges between objects represents the assignment of arms to object \textit{transfers}.
@@
 Since $ \graph $ is a complete graph (shown in Fig~\ref{fig:edge_matching}(top-right)) where every edge corresponds to every possible valid $ \coma $, by construction $ \scomaset \subset \edges$.
-A candidate solution of a monotone dual-arm rearrangement problem must transfer every object exactly once.
+A candidate solution of a monotone \dual-arm rearrangement problem must transfer every object exactly once.
 In terms of the graph, this means that in the subset of edges $ \scomaset $ every vertex appears in only one edge.
@@
 \lemma [Tour]
-Any complete tour $ \tour $ over the graph $ \tspgraph $, corresponds to a sequence of object-to-arm assignments $ \scoma_\tour $ and is a candidate solution to the synchronous dual-arm rearrangement problem.
+Any complete tour $ \tour $ over the graph $ \tspgraph $, corresponds to a sequence of object-to-arm assignments $ \scoma_\tour $ and is a candidate solution to the synchronous \dual-arm rearrangement problem.
 }

### 2020-12-18 07_cost_bounds.tex
changes

@@
 with, an arm may travel a path formed by $n + 1$ straight line 
-segments. Therefore, there are up to $(n + 1)^2$ intersections between the 
-two end-effector trajectories where potential collisions may happen.
-Nevertheless, since we can have at most four intersections for the transfers and transits associated with a pair of objects (one for each arm), there are at most $2n$ potential collisions to handle.
+segments. 
+\commentdel{Therefore, there are up to $(n + 1)^2$ intersections between the 
+two end-effector trajectories where potential collisions may happen. Nevertheless,} 
+Since we can have at most four intersections for the transfers and transits associated with a pair of objects (one for each arm), there are at most $2n$ potential collisions to handle.
 For each intersection, let one

### 2020-12-18 08_evaluation.tex
changes

@@
 
+\revisions{Note that we choose to focus on balanced problem instances where at least half of the objects are reachable to one of the robots.
+Unbalanced instances can be dealt with using {\tt NO\_ACT} object-to-arm assignments that requires no dual-arm coordination, while the proposed method remains unchanged.}
+
 \subsection{Simple Picker}
@@
 The objects are placed in the common reachable part of both arms' workspace, and only one top-down grasping configuration is allowed for each object pose.
+\revisions{For the Kuka arms top-down reachability exists in an annular region between 40-70cm from the base of each robot.
+The robots were placed 1.1m apart.
+Experiments were performed on the largest rectangle that fitted within the intersection of the annular reachability regions.}
+
 Here (Fig~\ref{fig:kuka}) a larger number of motion plans tend to fail, so the single shot variants show artifacts of the randomness of \drrtstar in their success rates. 
@@
 Expectedly, the naive random split tends to erroneously assign unreachable objects to arms.
-The data reported for the lazy variants, shows that our proposed method manages to maintain scalability and robustness even in such scenarios and moreover, further highlights the benefits of dual-arm rearrangement.
+The data reported for the lazy variants, shows that our proposed method manages to maintain scalability and robustness even in such scenarios and moreover, further highlights the benefits of \dual-arm rearrangement.
 
 }
+
+\revisions{\textit{Note on Heuristic Strategies: } 
+	%Alternative simplified strategies exist for this problem domain.
+A significant complexity in the studied problem arises from the coordination of the arms, especially for general manipulators.
+Decoupled motion planning here with coordination of single-arm solutions is typically faster but loses guarantees of completeness.
+%	For the assignment of objects to arms fast heuristics can be designed to allocate the objects based some partitioning of the workspace.
+The focus of the current work is however on problems where the arms have to move and coordinate in common regions where such a partition might not exist, and decoupled solutions might not work.
+	 It is possible that instead of the random baseline, some other heuristic might be used to allocate the objects to arms, like the proximity of objects to arms or some workspace partitioning.
+Such a deterministic, decoupled heuristic will make it faster to compute object-arm assignments than the proposed reasoning, but trade off the optimality bounds posited in this work.
+Given the object-to-arm assignments feasibility of the solution ultimately depends on coordinated motion planning.
+It should be noted that committing to a single choice of object assignments seriously affects success rates (especially in the Kuka benchmark).
+The success is only increased using our proposed lazy approach which takes into account such infeasibility and keeps reattempting other alternatives.
+A deterministic heuristic however will not offer alternative object-arm assignments and thus is incompatible with the improvements obtained from lazy evaluation.
+As such we leave the learning and incorporation of appropriate heuristics in this domain as future work and a motivation for practitioners.}

### 2020-12-18 09_discussion.tex
Updates from Overleaf
changes

@@
-The current work demonstrates the underlying structure of synchronized dual-arm rearrangement and proposes an \milp formulation, as well as a scalable algorithm \algo that provides fast, high quality solutions.
+The current work demonstrates the underlying structure of synchronized \dual-arm rearrangement and proposes an \milp formulation, as well as a scalable algorithm \algo that provides fast, high quality solutions.
 Existing efficient solvers for reductions of the dual-arm problem made \algo effective.
+
 \cameraready
 {
-Future work will attempt to explore the $k-$arm case.
+Work beyond the methods presented in this paper has explored the $k-$arm case.
 The matching sub-problem ceases to have effective solvers for $k>2$, and heuristics might need to be considered for feasible solutions.
-Regrasp reasoning can extend this work to non-monotone problem instances.
-The incorporation of manipulation and grasp reasoning can apply such solvers to more cluttered environments.
+Effective approximate or lazy solutions to the $k-$arm case can also prove to be power heuristics to the general multi-arm task planning~\cite{shome2019multiarm} challenge.
+Regrasp reasoning and the use of intermediate locations can extend this work to non-monotone problem instances.
+The incorporation of manipulation and grasp reasoning with \revisions{real-world object geometries} can also extend such solvers to more cluttered environments.
+This work serves as a stepping stone in building towards these rich problem domains.
 }

### 2020-12-18 biography.tex
changes

@@
 \parpic{\includegraphics[width=0.2\textwidth]{figures/biography/rahul_shome.jpeg}}
-\noindent {\bf Rahul Shome} is pursuing his Ph.D. in Computer
-Science at Rutgers University. He has been working with Prof. Kostas Bekris at
-the PRACSYS Lab. His research interests include multi-robot motion
-planning, manipulation planning, warehouse automation, and problems in rearrangement task planning.
+\noindent {\bf Rahul Shome} is a Postdoctoral Research Associate at Kavraki Lab, Rice University, working with Prof.
+Lydia Kavraki.
+He attained his Ph.D.
+in Computer Science from Rutgers University where he worked with Prof.
+Kostas Bekris at the PRACSYS Lab.
+His research interests include motion
+planning, manipulation, and task-and-motion planning with a special focus on practical real-world robotic solutions with strong theoretical guarantees.
 

### 2020-12-21 03_problem.tex
Updates from Overleaf

@@
 % THE OLD SENTENCE$\cfree^k$ is the set of collision-free configurations for arm $ \arm^k $, where $ q^k \in \cfree^k %\subset \reals^d $ (while ignoring possible collisions with  objects or the other arm).
-$\cfree^k$ is the set of collision-free configurations for arm $\arm^k$ (while ignoring possible collisions with  objects or the other arm), and is assumed here to be a subset of \revisions{$d$-dimensional} $\reals^d $.
+$\cfree^k$ is the set of collision-free configurations for arm $\arm^k$ (while ignoring possible collisions with  objects or the other arm), and is assumed here to be a subset of \revisions{$d$-dimensional} Euclidean space $\reals^d $.
 A path for $\arm^k$ is denoted as $ \pi^k : [0,1] \rightarrow \cfree^k$ and includes picking and placing actions throughout the entire rearrangement process.
@@
 \revisions{
-	\textit{Scope and Limitations:} A variety of automation applications like packing, stowing, or sorting involve different singulated objects arriving at designated source regions, involving their rearrangement to a disjoint target region or container.
+	\textit{Scope and Limitations:} A variety of automation applications like packing, stowing, or sorting involve different singulated objects arriving at designated source regions, and require their rearrangement to a disjoint target region or container.
 Such automation applications also create semi-structured workspaces that guarantee that all objects of interest are easily graspable (top-down for planar surfaces).
@@
 In this case object non-interactivity essentially implies that the workspace is well-behaved enough to allow feasible single-arm motion plans between top-down reachable poses of the object.
-The current work addresses what we need to do go beyond single arm setups to effectively deploy two arms to speed up such an operation, and theoretically motivates the same.
+	%The current work addresses what we need to do go beyond single arm setups to effectively deploy two arms to speed up such an operation, and theoretically motivates the same. 
+	 The current work addresses what we need to do in order to go beyond single arm setups and in particular in order to effectively deploy two arms to speed up such tasks.
+Our work also theoretically motivates the use of two arms over a single arm in monotone object rearrangement.
 
@@
 The proposed method has limiting applicability to some interesting domains where objects are occluded, overlap, or lie in unstructured piles.
-Any non-monotonicity, i.e.
-problems that necessitate using an intermediate location, cannot be addressed by the current pipeline.
+Any non-monotone problems, i.e., problems that necessitate using an intermediate location, cannot be addressed by the current pipeline.
 These include puzzle-like or highly cluttered scenarios.

### 2020-12-21 08_evaluation.tex
Updates from Overleaf

@@
 \revisions{Note that we choose to focus on balanced problem instances where at least half of the objects are reachable to one of the robots.
-Unbalanced instances can be dealt with using {\tt NO\_ACT} object-to-arm assignments that requires no dual-arm coordination, while the proposed method remains unchanged.}
+Unbalanced instances can be dealt with using {\tt NO\_ACT} object-to-arm assignments that require no dual-arm coordination, while the proposed method remains unchanged.}
 
@@
 It should be noted that committing to a single choice of object assignments seriously affects success rates (especially in the Kuka benchmark).
-The success is only increased using our proposed lazy approach which takes into account such infeasibility and keeps reattempting other alternatives.
+The success is only increased using our proposed lazy approach, which takes into account such infeasibility and keeps reattempting other alternatives.
 A deterministic heuristic however will not offer alternative object-arm assignments and thus is incompatible with the improvements obtained from lazy evaluation.

### 2020-12-21 09_discussion.tex
Updates from Overleaf

@@
 {
-Work beyond the methods presented in this paper has explored the $k-$arm case.
+Work beyond the methods presented in this paper has explored the $k$-arm case.
 The matching sub-problem ceases to have effective solvers for $k>2$, and heuristics might need to be considered for feasible solutions.
-Effective approximate or lazy solutions to the $k-$arm case can also prove to be power heuristics to the general multi-arm task planning~\cite{shome2019multiarm} challenge.
+Effective approximate or lazy solutions to the $k$-arm case can also prove to be power heuristics to the general multi-arm task planning~\cite{shome2019multiarm} challenge.
 Regrasp reasoning and the use of intermediate locations can extend this work to non-monotone problem instances.

### 2021-01-25 biography.tex
Updates from Overleaf

@@
 \parpic{\includegraphics[width=0.2\textwidth]{figures/biography/kiril_solovey.PNG}}
-\noindent {\bf Kiril Solovey} is a Postdoctoral Scholar at the Autonomous Systems Lab, Department of Aeronautics and Astronautics, Stanford University, hosted by Prof.
-Marco Pavone.
-His research focuses on algorithmic aspects of robotics.
-He is particularly interested in the design and analysis of techniques for robot motion planning, multi-robot systems, and autonomous mobility-on-demand.
-He is supported by the Fulbright Scholars Program.
-Prior to Stanford, He was a Ph.D.
-student at Tel Aviv University working with Prof.
-Dan Halperin in the Computational Geometry Lab.
-He was supported by the Clore Israel Foundation.
+\noindent {\bf Kiril Solovey} is a Postdoctoral Scholar at the Autonomous Systems Lab, Department of Aeronautics and Astronautics, Stanford University.
+He received his Ph.D.
+in Computer Science from Tel Aviv University, Israel.
+His work focuses on multi-robot systems and their applications to smart mobility, with an emphasis on the design of effective control and decision-making mechanisms.
+He is the recipient of the Clore Scholars Award, Fulbright Postdoctoral Fellowship, and several best paper awards and nominations.
 
